### 2014-05-12 Paper/paper.tex
new file:   2D_Gauss.py 	new file:   GaussFit.py 	new file:   Gauss_Fitting/CASA_gaussians.txt 	new file:   Gauss_Fitting/CASA_gaussians_lower.txt 	new file:   Gauss_Fitting/CASA_gaussians_upper.txt 	new file:   Gauss_Fitting/Final_Fit_Results.txt 	new file:   Gauss_Fitting/Fit_Latex_Table.tex 	new file:   Gauss_Fitting/Flux_Table.py 	new file:   Gauss_Fitting/Make_Estimates.py 	new file:   Gauss_Fitting/SERPS_Gauss_Fit.py 	new file:   Gauss_Fitting/SERPS_lower.S1-gaussest.txt 	new file:   Gauss_Fitting/SERPS_lower.S10-gaussest.txt 	new file:   Gauss_Fitting/SERPS_lower.S11-gaussest.txt 	new f

%% Document Class
\documentclass[iop]{aastex}

%% Document Preamble
% Packages
\usepackage{indentfirst}		% Used to fix non indent of 1st paragraph
\usepackage{fancyhdr}		% Used to make custom footer / headers
\usepackage{fixltx2e}		% Used fix Latex Corrections
\usepackage{graphicx}		% To import figures into text
\usepackage{natbib}			% Bibliography
\usepackage{amsmath}		% Equation Package
\usepackage{textcomp}		% For symbols
\usepackage{amssymb}		% More symbols
\usepackage{booktabs}		% For tables
\usepackage{lscape}		% For Sideways Tables

%% Begin Document
\begin{document}
\title{Centimeter Continuum Emission From Young Stellar Objects in the Serpens South Protocluster}
%\title{Radio Properties of Protostars in the Serpens South Star Forming Region}

%% Abstract
\begin{abstract}
The Serpens South protostellar cluster is a site of active star formation located in the Aquila Rift, with an abundance of embedded protostars at its core. Radio observations of centimeter emission from the region allow for the classifications of young protostars that are still heavily shrouded, and have proven to be an essential tool in the characterization of young stellar objects. We report the detection of centimeter wavelength ($\lambda=4.135$ cm and $\lambda=6.311$ cm) continuum emission from previously known and unidentified young stellar objects in the core of the Serpens South protostellar cluster. We use the Jansky Very Large Array (VLA) to give a detailed account of the radio properties of the young stellar objects, as well as characterize the evolutionary stage and luminosity source of young stellar objects in Serpens South in conjunction with infrared mappings of the region. We report the detection of centimeter sources lining up with more diffuse sources in micrometer wavelengths, verifying the presence of compact cores. This is the first mapping of centimeter continuum emission in this region at a spatial resolution of $<$ 5 arcseconds.

\end{abstract}

%% Begin Paper %%

%% Introduction
\section{Introduction}

Radio observations of protostars have long been used as a tool to infer the presence of protostars deeply embedded in the clouds of dust and gas that are their progenitors \citep{Anglada95}.

\begin{landscape}
\begin{deluxetable}{lccccccccccc}
\tablewidth{0pc}
\tabletypesize{\scriptsize}
\tablecolumns{12}
\tablecaption{Caption...\label{Properties of 2D Gaussian Fits}}
\tablehead{
\colhead{Source Name} & \colhead{Int. Flux} & \colhead{Int. Flux Err} & \colhead{Peak Flux} & \colhead{RA} & \colhead{RA Err} & \colhead{DEC} & \colhead{DEC Err} & \colhead{Bmaj} & \colhead{Bmin} & \colhead{Pos. Angle} & \colhead{RMS} \\
 \colhead{} & \colhead{(mJy)} & \colhead{(mJy)} & \colhead{(mJy)} & \colhead{(J2000)} & \colhead{(arcsec)} & \colhead{(J2000)} & \colhead{(arcsec)} & \colhead{(arcsec)} & \colhead{(arcsec)} & \colhead{(degrees)} & \colhead{(mJy)}  }
\startdata
lower.S1 & 0.06486 & 0.02438 & 0.06500 & -82.44 & 0.8961 & -2.024 & 0.7340 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S2 & 0.5987 & 0.02511 & 0.6000 & -82.46 & 0.09998 & -2.009 & 0.08190 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S3 & 0.04091 & 0.02534 & 0.04100 & -82.47 & 1.476 & -2.013 & 1.209 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S4 & 0.1197 & 0.01196 & 0.1200 & -82.48 & 0.2380 & -2.010 & 0.1950 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S5 & 0.07284 & 0.01367 & 0.07300 & -82.49 & 0.4473 & -2.013 & 0.3664 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S6 & 0.9978 & 0.02082 & 1.000 & -82.49 & 0.04973 & -2.014 & 0.04074 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S7 & 0.05687 & 0.02516 & 0.05700 & -82.47 & 1.054 & -2.025 & 0.8638 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S8 & 0.04290 & 0.02563 & 0.04300 & -82.48 & 0.0003964 & -2.029 & 0.0003247 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S9 & 0.000 & 0.000 & 0.04000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
lower.S10 & 0.000 & 0.000 & 0.1100 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
lower.S11 & 0.1497 & 0.1033 & 0.1500 & -82.49 & 1.646 & -2.042 & 1.348 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S12 & 0.1497 & 0.01350 & 0.1500 & -82.49 & 0.2150 & -2.043 & 0.1762 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S13 & 0.4290 & 0.02459 & 0.4300 & -82.49 & 0.1366 & -2.046 & 0.1119 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S14 & 0.000 & 0.000 & 0.03600 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
lower.S15 & 0.1696 & 0.01368 & 0.1700 & -82.49 & 0.1923 & -2.052 & 0.1575 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S16 & 0.000 & 0.000 & 0.1700 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
lower.S17 & 0.03792 & 0.02311 & 0.03800 & -82.48 & 1.453 & -2.054 & 1.190 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S18 & 0.000 & 0.000 & 0.05000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
lower.S19 & 0.1197 & 0.01004 & 0.1200 & -82.49 & 0.1998 & -2.062 & 0.1637 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S20 & 0.05887 & 0.01186 & 0.05900 & -82.50 & 0.4802 & -2.067 & 0.3933 & 4.820 & 3.850 & 13.40 & 0.03806\\
lower.S21 & 0.1497 & 0.02503 & 0.1500 & -82.46 & 0.3986 & -2.069 & 0.3265 & 4.820 & 3.850 & 13.40 & 0.03806\\
upper.S1 & 0.09969 & 0.01901 & 0.1000 & -82.44 & 0.2973 & -2.024 & 0.2436 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S2 & 0.5483 & 0.01932 & 0.5500 & -82.46 & 0.05494 & -2.009 & 0.04502 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S3 & 0.02592 & 0.01936 & 0.02600 & -82.47 & 1.164 & -2.013 & 0.9542 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S4 & 0.05084 & 0.008597 & 0.05100 & -82.48 & 0.2636 & -2.010 & 0.2160 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S5 & 0.04985 & 0.008045 & 0.05000 & -82.49 & 0.2516 & -2.013 & 0.2062 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S6 & 0.3988 & 0.01086 & 0.4000 & -82.49 & 0.04245 & -2.014 & 0.03479 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S7 & 0.04486 & 0.01182 & 0.04500 & -82.47 & 0.4107 & -2.025 & 0.3365 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S8 & 0.04785 & 0.01226 & 0.04800 & -82.48 & 0.3994 & -2.029 & 0.3273 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S9 & 0.02592 & 0.007830 & 0.02600 & -82.49 & 0.4709 & -2.033 & 0.3859 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S10 & 0.05284 & 0.04357 & 0.05300 & -82.49 & 1.285 & -2.040 & 1.053 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S11 & 0.05284 & 0.03196 & 0.05300 & -82.49 & 0.9428 & -2.042 & 0.7726 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S12 & 0.05284 & 0.008033 & 0.05300 & -82.49 & 0.2370 & -2.043 & 0.1942 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S13 & 0.04486 & 0.01037 & 0.04500 & -82.49 & 0.3603 & -2.046 & 0.2952 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S14 & 0.000 & 0.000 & 0.03900 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
upper.S15 & 0.1894 & 0.01814 & 0.1900 & -82.49 & 0.1493 & -2.052 & 0.1223 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S16 & 0.1894 & 0.01372 & 0.1900 & -82.48 & 0.1129 & -2.053 & 0.09251 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S17 & 0.03888 & 0.01403 & 0.03900 & -82.48 & 0.5624 & -2.054 & 0.4609 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S18 & 0.05084 & 0.009118 & 0.05100 & -82.49 & 0.2796 & -2.057 & 0.2291 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S19 & 0.1196 & 0.007314 & 0.1200 & -82.49 & 0.09530 & -2.062 & 0.07810 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S20 & 0.02592 & 0.009043 & 0.02600 & -82.50 & 0.5438 & -2.067 & 0.4457 & 3.150 & 2.520 & 12.70 & 0.03004\\
upper.S21 & 0.09969 & 0.01154 & 0.1000 & -82.46 & 0.1804 & -2.069 & 0.1478 & 3.150 & 2.520 & 12.70 & 0.03004\\
\enddata
\end{deluxetable}
\end{landscape}

-- Present problem

-- Previous studies

-- Importance of field

-- Basic specs on data

-- Outline of paper

%Perhaps talk generally about protostars, classifications, problems, unique opportunities for use of radio astronomy?

%Introduction of the discovery of Serpens South by Gutermuth 2008. Basic properties of the region and current thoughts on age, distance, evolution, filamentary accretion flows, and also the basic properties of protostars seen in the radio. Why radio is interesting for protostars and what it may tell us, previous uses of radio emission to determine properties.

\section{Observed Region}
-- History of region

-- Other studies of region, and current thoughts on dynamics and evolution of region

-- Other studies of region in radio and other wavelengths

-- Overview of telescope used in the study

\section{Observations \& Data Reduction}
-- Data reduction processes, RFI problems, antennas, etc..

-- RMS values, cleaning steps

-- Acknowledgment of artifacts and bugs in images

-- Resolution of beam

-- Possible errors in aperture synthesis technique

%We used the Jansky Very Large Array (VLA) to image radio continuum emission coming from the Serpens South cluster, taken on July 2nd, 2013. We focused on RA xxxxx DEC xxxxxx, and were sensitive to an area of xxx square degrees. The array was in the C configuration during the observation, which is the second smallest configuration with a maximum baseline length of 3.4 km. We imaged the cluster in the C band, which spans 4238.0 MHz -- 7762.0 MHz. We broke this bandwidth up into two subbands, the first ranging from 4238.00 MHz -- 5262.00 MHz with the middle at $\lambda=6.311$ cm, and the second ranging from 6738.00 MHz -- 7762.00 MHz with the middle at $\lambda=4.135$ cm.

\section{Sources}
-- Note on sources, how they were chosen

\section{Results \& Analysis}

\section{Discussion}

\section{Conclusions}

%% Bibliography %%
\bibliographystyle{apj}		
\bibliography{references}{}

%% End Document
\end{document}

### 2014-05-12 2D_Gauss.py

@@ -1,0 +1,68 @@
+#### Serpens South 2D Gaussian Fit ####
+## Nicholas S. Kern
+## nkern@umich.edu
+
+### Import Modules
+import numpy as np
+import matplotlib.pyplot as mp
+import scipy.optimize
+import astropy.io.fits as fits
+from mpl_toolkits.mplot3d import Axes3D
+from GaussFit import gaussian, moments, fitgaussian
+
+### Flags
+
+
+
+### Program
+
+## Load Data
+# Load FITS
+HDU1 = fits.open('SERPS_2.upper.mask.deeper2.briggs.fits')
+SS_4cm = HDU1[0].data[0][0]
+
+## Load Approximate Source Locations
+# Load SS_Targets_pxl.csv
+Y,X,ID = np.loadtxt('SS_Targets_pxl.csv',delimiter=',',unpack=True)
+ID = np.array(ID,int)
+sort = np.argsort(ID)
+X,Y,ID = X[sort],Y[sort],ID[sort]
+
+## Cut regions
+X_sub = X-5
+X_add = X+5
+Y_sub = Y-5
+Y_add = Y+5
+SS_4cm_sources = []
+for i in range(len(ID)):
+	SS_4cm_sources.append(SS_4cm[X_sub[i]:X_add[i],Y_sub[i]:Y_add[i]])
+
+SS_4cm_sources = np.array(SS_4cm_sources)
+
+## Find Maximum Value per Source
+max_val = np.array(map(np.max,SS_4cm_sources))
+
+## Fit 2D Gaussian
+PARAMS = []
+for i in range(len(ID)):
+	PARAMS.append(fitgaussian(SS_4cm_sources[i]))
+
+PARAMS=np.array(PARAMS)
+
+## Integrate FWHM
+# 2D Gaussian Functionalform
+# f = A*np.exp(-( (x-mu_x)**2/(2*sig_x**2) + (y-mu_y)**2/(2*sig_y**2) ))
+def f(x,y,A,mu_x,mu_y,sig_x,sig_y):
+	return A*np.exp(-( (x-mu_x)**2/(2*sig_x**2) + (y-mu_y)**2/(2*sig_y**2) ))
+
+
+
+
+## Plot
+i = 5
+mp.matshow(SS_4cm_sources[5])
+X,Y = np.meshgrid(range(10),range(10))
+CS = mp.contour(f(X,Y,*PARAMS[5]))
+mp.show()
+
+

### 2014-05-12 Gauss_Fitting/Flux_Table.py

@@ -1,0 +1,75 @@
+'''
+This script takes data and writes a Latex Table.
+It is dependent on Table.py and sigfig.py
+'''
+import numpy as np
+import Table
+
+Source_Num = 21
+
+# Turn into Latex Table (need Table.py and sigfig.py in working directory)
+print '...Loading Data'
+
+# Load and Configure Necessary Data for Table
+sourcename = np.loadtxt('Final_Fit_Results.txt',dtype=str,usecols=(0,),unpack=True)
+sourcenames = np.array(map(lambda x:x[6:],sourcename))
+flux,flux_err,ra,dec,ra_err,dec_err,bmaj,bmin,pos_angle,rms=np.loadtxt('Final_Fit_Results.txt',usecols=(1,2,3,4,5,6,7,8,9,10),unpack=True)
+peak_flux = []
+j = 0
+for i in np.concatenate([np.arange(1,Source_Num+1),np.arange(1,Source_Num+1)]):
+	j += 1
+	if j < 22:
+		peak_flux.append(np.loadtxt('SERPS_lower.S'+str(i)+'-gaussest.txt',delimiter=',',usecols=(0,)))
+	elif j > 21:
+		peak_flux.append(np.loadtxt('SERPS_upper.S'+str(i)+'-gaussest.txt',delimiter=',',usecols=(0,)))
+peak_flux = np.array(peak_flux)
+
+# Convert flux values to mJy
+flux *= 1e3
+flux_err *= 1e3
+peak_flux *= 1e3
+rms *= 1e3
+
+# Convert RA and DEC to J2000
+ra = 360 + ra 
+ra_frac = ra/360. * 24
+ra_h = np.array(np.floor(ra_frac),int)
+ra_m = np.array(np.floor((ra_frac - ra_h)*60),int)
+ra_s = np.around(((ra_frac - ra_h)*60 - ra_m)*60,1)
+ra_s = np.array(map(lambda x:"%02g" % (x,), ra_s))
+ra_sexig = np.array([a+':'+b+':'+c for a,b,c in zip(np.array(ra_h,str),np.array(ra_m,str),np.array(ra_s,str))])
+
+dec_deg = np.ceil(dec)
+dec_m = np.array(np.floor((dec_deg-dec)*60),int)
+dec_s = np.around( ((dec_deg-dec)*60 - dec_m)*60,1)
+dec_deg = np.array(map(lambda x: "%03d" % (x), dec_deg))
+dec_m = np.array(map(lambda x:"%02d" % (x), dec_m))
[…]

### 2014-05-12 Gauss_Fitting/Make_Estimates.py

@@ -1,0 +1,55 @@
+"""
+This code interactively takes in data to write out estimates files needed by SERPS_Gauss_Fit.py
+"""
+import numpy as np
+
+# Define Constants
+Source_Num = 21		# Number of Sources in Field of View, see SS_Targets.reg
+Image_Num = 2		# Number of Images with same sources
+
+sources = []
+source_id=np.array(np.arange(1,Source_Num+1),str)
+for p in range(Source_Num*Image_Num):
+	if p < 21:
+		sources.append('SERPS_lower.S'+source_id[p])	
+	else:
+		sources.append('SERPS_upper.S'+source_id[p-21])
+
+sources = np.array(sources)
+
+for i in np.arange(0,Source_Num*Image_Num):
+	file = open(sources[i]+'-gaussest.txt','r')
+	cont = False
+	while cont == False:
+		print ''
+		print 'Working on Source:',sources[i]
+		print '-'*25
+		flux = raw_input('Flux density of center pixel? (Jy) : ')
+		x = raw_input('X pixel coordinate of center pixel? : ')
+		y = raw_input('Y pixel coordinate of center pixel? : ')
+		major_axis = '3.15arcsec' #raw_input('Major axis of beam? (#.##arcsec) : ')
+		minor_axis = '2.52arcsec' #raw_input('Minor axis of beam? (#.##arcsec) : ')
+		position_angle = '12.7deg' #raw_input('Position angle of beam? (###.#deg) : ')
+		print 'Given Values:'
+		print 'flux =',flux
+		print 'x =',x
+		print 'y =',y
+		print 'major_axis =',major_axis
+		print 'minor_axis =',minor_axis
+		print 'position_angle =',position_angle
+		read = raw_input('Is this correct? (y/n) : ')
+		if read == 'y':
+			cont = True
+		else:
+			print 'Try again...'	
+
+	print '...Writing Data for Source:',sources[i]
+	file.write(str(flux)+','+str(x)+','+str(y)+','+str(major_axis)+','+str(minor_axis)+','+str(position_angle)+'\n')
+	file.close()
+
+
+
+
+
+
+

### 2014-05-12 Gauss_Fitting/SERPS_Gauss_Fit.py

@@ -1,0 +1,236 @@
+"""
+ - This code takes the two SERPS.**.fits files and uses imfit-sources.py to fit 
+Gaussians to sources in the images.
+
+ - To be run within CASA: execfile('SERPS_Gauss_Fit.py')
+
+ - Dependent on readcol.py
+	http://code.google.com/p/agpy/source/browse/trunk/agpy/readcol.py
+
+May, 2014
+"""
+
+### Import Modules ###
+print '...Loading Modules'
+print '-'*30
+import numpy as np
+import matplotlib.pyplot as mp
+from readcol import *
+import os, sys
+
+
+### Define Flags ###
+
+
+### Functions ###
+def extractcomponents(sourcename=None,componentlist=None,comp=None,rms=None):
+	print comp
+	#outputfilefits = open(sourcename+'-fitresults.txt','w')
+	#outputfileseps = open(sourcename+'-separations.txt','w')
+	cl.open(componentlist)
+	separations=np.zeros(comp, dtype=float)
+	e_separations=np.zeros(comp, dtype=float)
+	rakeep=np.zeros(comp, dtype=float)
+	deckeep=np.zeros(comp, dtype=float)
+	e_rakeep=np.zeros(comp, dtype=float)
+	e_deckeep=np.zeros(comp, dtype=float)
+
+	for j in range(comp):
+		fit=cl.getcomponent(j)
+		flux = fit['flux']['value']
+		e_flux = fit['flux']['error']
+		print flux[0]
+		ra = fit['shape']['direction']['m0']['value']*180.0/3.14159265
+		dec = fit['shape']['direction']['m1']['value']*180.0/3.14159265
+		e_ra = fit['shape']['direction']['error']['latitude']['value']
+		e_dec = fit['shape']['direction']['error']['longitude']['value']
+		bmaj = fit['shape']['majoraxis']['value']*60.0     
+		bmin = fit['shape']['minoraxis']['value']*60.0       
+		pa =   fit['shape']['positionangle']['value']
+		print ra,dec,e_ra,e_dec,bmaj,bmin
+		line = str(sourcename[:])+" "+str(flux[0])+" "+str(e_flux[0])+ " " +str(ra)+" "+str(dec)+" "+str(e_ra)+" "+str(e_dec)+" " +str(bmaj)+" "+str(bmin)+" "+str(pa)+" "+str(rms)+"\n"
+		rakeep[j]=ra
[…]

### 2014-05-12 Gauss_Fitting/Table.py

@@ -1,0 +1,207 @@
+'''
+Table.py
+
+A module/class for creating LaTeX deluxetable's.  In a nutshell, you create
+a table instance, add columns, set options, then call the pring method.'''
+
+import numpy
+import sigfig
+import os,string,re,sys
+import types
+
+float_types = [types.FloatType, numpy.float16, numpy.float32, numpy.float64,
+      numpy.float128]
+
+class Table:
+
+   def __init__(self, numcols, justs=None, fontsize=None, rotate=False, 
+         tablewidth=None, tablenum=None, caption=None, label=None):
+
+      self.numcols = numcols
+      self.justs = justs
+      if self.justs is None:
+         self.justs = ['c' for i in range(numcols)]
+      else:
+         self.justs = list(justs)
+         if len(self.justs) != numcols:
+            raise ValueError, "Error, justs must have %d elements" % (numcols)
+      for just in self.justs:
+         if just not in ['c','r','l']:
+            raise ValueError, "Error, invalid character for just: %s" % just
+      self.fontsize = fontsize
+      self.rotate = rotate
+      self.tablewidth = tablewidth
+      self.tablenum = None
+      self.caption = caption
+      self.label = label
+      self.col_justs = []
+      self.headers = []
+      self.header_ids = []
+      # self.data is a list of data.  Each element of the list corresponds
+      #  to a separate "secton" of the table, headed by self.data_labels
+      # Each element of data should be a list of self.numcols items.
+      self.data = []
+      self.data_labels = []
+      self.data_label_types = []
+      self.sigfigs = []
+      self.nrows = []
+
+   def add_header_row(self, headers, header2=None, cols=None):
+      '''Add a header row to the table.  [headers] should be a list of the
+      strings that will be in the header.  [cols], if specified, should be a 
+      list of column indexes.  If [cols] is None, it is assummed the headers
+      are in order and there are no multicolumns.  If cols is specified, you
+      can indicate the the ith header spans several columns by setting the
+      ith value of cols to a 2-tuple of first and last columns for the span.'''
+      
+      if cols is None:
+         if len(headers) != self.numcols:
+            raise ValueError, "Error, headers must be a list of length %d" %\
+                  self.numcols
+         self.headers.append(headers)
+         self.header_ids.append(range(self.numcols))
+         if header2 != None:
[…]

### 2014-05-12 SERPS_SED.py

@@ -1,0 +1,165 @@
+"""
+This code takes the gaussian fitted data and derives the Spectral Index of the sources with fits
+
+May, 2014
+"""
+
+### Import Modules ###
+import numpy as np
+import matplotlib.pyplot as mp
+import scipy.stats as stats
+
+### Flags, Constants ###
+lower_freq	= 4750.00		# MHz
+upper_freq	= 7250.00		# MHz
+lower_passband	= [4238.00,5262.00]	# MHz
+upper_passband	= [6738.00,7762.00]	# MHz
+Source_Num	= 21
+Image_Num	= 2
+c		= 2.9979e8		# m/s
+
+
+### Program ###
+
+# Load Data, arrays with 0.0000 are nulls
+data = np.loadtxt('Gauss_Fitting/Final_Fit_Results.txt',usecols=(1,2,3,4,5,6,7,8,9,10))
+sources = np.loadtxt('Gauss_Fitting/Final_Fit_Results.txt',usecols=(0,),dtype=str)
+
+lower_data = data[0:21]
+lower_sources = sources[0:21]
+upper_data = data[21:]
+upper_sources = sources[21:]
+
+# data arrays have 2nd axis metadata of:
+# flux,flux_e,ra,dec,ra_e,dec_e,bmaj,bmin,pa,rms
+
+# Find sources with fit in both upper and lower
+fitted = np.array([0,1,2,3,4,5,6,7,10,11,12,14,16,18,19,20])	# Indicies
+
+# Load Gutermuth Cross Match data
+RA_VLA,Dec_VLA,jmag,hmag,kmag,i1mag,i2mag,i3mag,i4mag,m24mag,p70mag = np.loadtxt('vla_serps_merger_gutermuth_try1.csv',delimiter=',',unpack=True)
+# -100 are nulls
+# jhk mags are 2mass near infrared 
+# i1,i2,i3,i4 are IRAC on Spitzer
+# m24 is MIPS 24 micron on Spitzer 
+# p70 is PACS 70 micron on Herschel
+
+# Write ds9 region file for RA and DEC coordinates
+output = open('Gutermuth_CrossMatch.reg','w')
+output.write('# Region file format: DS9 version 4.1\n')
[…]

### 2014-12-02 2D_Gauss.py
deleted:    2D_Gauss.py 	new file:   IRAM_sources.txt 	new file:   Lower_Peak_Fluxes_try2.csv 	new file:   MSX_Catalogue.tsv 	new file:   Make_Figs.py 	new file:   Shirley07Data/3.6cmFout.dat 	new file:   Shirley07Data/3.6cmcont.dat 	new file:   Shirley07Data/6cmcont.dat 	new file:   Shirley07Data/cmcontinuum.xls 	deleted:    cross.reg 	deleted:    ds9.reg

@@ -1,68 +1,0 @@
-#### Serpens South 2D Gaussian Fit ####
-## Nicholas S. Kern
-## nkern@umich.edu
-
-### Import Modules
-import numpy as np
-import matplotlib.pyplot as mp
-import scipy.optimize
-import astropy.io.fits as fits
-from mpl_toolkits.mplot3d import Axes3D
-from GaussFit import gaussian, moments, fitgaussian
-
-### Flags
-
-
-
-### Program
-
-## Load Data
-# Load FITS
-HDU1 = fits.open('SERPS_2.upper.mask.deeper2.briggs.fits')
-SS_4cm = HDU1[0].data[0][0]
-
-## Load Approximate Source Locations
-# Load SS_Targets_pxl.csv
-Y,X,ID = np.loadtxt('SS_Targets_pxl.csv',delimiter=',',unpack=True)
-ID = np.array(ID,int)
-sort = np.argsort(ID)
-X,Y,ID = X[sort],Y[sort],ID[sort]
-
-## Cut regions
-X_sub = X-5
-X_add = X+5
-Y_sub = Y-5
-Y_add = Y+5
-SS_4cm_sources = []
-for i in range(len(ID)):
-	SS_4cm_sources.append(SS_4cm[X_sub[i]:X_add[i],Y_sub[i]:Y_add[i]])
-
-SS_4cm_sources = np.array(SS_4cm_sources)
-
-## Find Maximum Value per Source
-max_val = np.array(map(np.max,SS_4cm_sources))
-
-## Fit 2D Gaussian
-PARAMS = []
-for i in range(len(ID)):
-	PARAMS.append(fitgaussian(SS_4cm_sources[i]))
-
-PARAMS=np.array(PARAMS)
-
-## Integrate FWHM
-# 2D Gaussian Functionalform
-# f = A*np.exp(-( (x-mu_x)**2/(2*sig_x**2) + (y-mu_y)**2/(2*sig_y**2) ))
-def f(x,y,A,mu_x,mu_y,sig_x,sig_y):
-	return A*np.exp(-( (x-mu_x)**2/(2*sig_x**2) + (y-mu_y)**2/(2*sig_y**2) ))
-
-
-
-
-## Plot
-i = 5
-mp.matshow(SS_4cm_sources[5])
-X,Y = np.meshgrid(range(10),range(10))
-CS = mp.contour(f(X,Y,*PARAMS[5]))
-mp.show()
-
-

### 2014-12-02 Make_Figs.py

@@ -1,0 +1,266 @@
+## Make Paper Figures
+import numpy as np
+import matplotlib.pyplot as mp
+import astropy.io.fits as fits
+from astropy.wcs import WCS
+from wcsaxes import WCSAxes
+from astropy import units as u
+import DictEZ as dez
+import aplpy
+from PIL import Image
+import matplotlib
+from astropy import coordinates as coord
+from astropy import units as u
+
+## Flags
+savefig = False
+
+plot1 = False
+plot2 = False
+plot3 = True
+
+
+def sexig_to_deg(ra,dec):
+	length = len(ra)
+	ra_deg = []
+	dec_deg = []
+	for i in range(length):
+		_ra_deg = np.float(ra[i][0:2])*360./24. + np.float(ra[i][3:5])*360./24./60. + np.float(ra[i][6:10])*360./24./60./60.
+		_dec_deg = (np.float(dec[i][1:3]) + np.float(dec[i][4:6])/60. + np.float(dec[i][7:11])/3600.)*np.float(dec[i][0]+'1')
+		ra_deg.append(_ra_deg)
+		dec_deg.append(_dec_deg)
+	ra_deg = np.array(ra_deg)
+	dec_deg = np.array(dec_deg)
+	return ra_deg,dec_deg
+
+def get_zorder(layers):
+	''' Gets zorder of a aplpy figure given dictionary *layers* (fig._layers) '''
+	zorder_values = {}
+	zorder_paths = {}
+	for a in layers:
+		try:
+			zorder = layers[a].get_zorder()
+			path = layers[a]
+		except AttributeError:
+			try:
+				zorder = layers[a].collections[0].get_zorder()
+				path = layers[a].collections[0]
+			except AttributeError:
+				try:
+					zorder = layers[a].artistlist[0].get_zorder()
+					path = layers[a].artistlist[0]	
+				except:
+					print "Couldn't get zorder for layer:",a
+					zorder = np.nan
+					paths = np.nan
+		zorder_values[a] = zorder
+		zorder_paths[a] = path
+	return zorder_values, zorder_paths
+
+### Herschel map w/ Spitzer sources and VLA primary beam
+if plot1 == True:
+	# Load and Configure Images
[…]

### 2014-12-02 GaussFit.py
deleted:    GaussFit.py 	deleted:    Gauss_Fitting/CASA_gaussians.txt 	deleted:    Gauss_Fitting/CASA_gaussians_lower.txt 	deleted:    Gauss_Fitting/CASA_gaussians_upper.txt 	deleted:    Gauss_Fitting/Final_Fit_Results.txt 	deleted:    Gauss_Fitting/Fit_Latex_Table.tex 	deleted:    Gauss_Fitting/Flux_Table.py 	deleted:    Gauss_Fitting/Make_Estimates.py 	deleted:    Gauss_Fitting/SERPS_Gauss_Fit.py 	deleted:    Gauss_Fitting/SERPS_lower.S1-gaussest.txt 	deleted:    Gauss_Fitting/SERPS_lower.S10-gaussest.txt 	deleted:    Gauss_Fitting/SERPS_lower.S11-gaussest.txt 	deleted:    Gauss_Fitting/SERP

@@ -1,33 +1,0 @@
-from numpy import *
-from scipy import optimize
-
-def gaussian(height, center_x, center_y, width_x, width_y):
-    """Returns a gaussian function with the given parameters"""
-    width_x = float(width_x)
-    width_y = float(width_y)
-    return lambda x,y: height*exp(
-                -(((center_x-x)/width_x)**2+((center_y-y)/width_y)**2)/2)
-
-def moments(data):
-    """Returns (height, x, y, width_x, width_y)
-    the gaussian parameters of a 2D distribution by calculating its
-    moments """
-    total = data.sum()
-    X, Y = indices(data.shape)
-    x = (X*data).sum()/total
-    y = (Y*data).sum()/total
-    col = data[:, int(y)]
-    width_x = sqrt(abs((arange(col.size)-y)**2*col).sum()/col.sum())
-    row = data[int(x), :]
-    width_y = sqrt(abs((arange(row.size)-x)**2*row).sum()/row.sum())
-    height = data.max()
-    return height, x, y, width_x, width_y
-
-def fitgaussian(data):
-    """Returns (height, x, y, width_x, width_y)
-    the gaussian parameters of a 2D distribution found by a fit"""
-    params = moments(data)
-    errorfunction = lambda p: ravel(gaussian(*p)(*indices(data.shape)) -
-                                 data)
-    p, success = optimize.leastsq(errorfunction, params)
-    return p

### 2014-12-02 Gauss_Fitting/Flux_Table.py

@@ -1,75 +1,0 @@
-'''
-This script takes data and writes a Latex Table.
-It is dependent on Table.py and sigfig.py
-'''
-import numpy as np
-import Table
-
-Source_Num = 21
-
-# Turn into Latex Table (need Table.py and sigfig.py in working directory)
-print '...Loading Data'
-
-# Load and Configure Necessary Data for Table
-sourcename = np.loadtxt('Final_Fit_Results.txt',dtype=str,usecols=(0,),unpack=True)
-sourcenames = np.array(map(lambda x:x[6:],sourcename))
-flux,flux_err,ra,dec,ra_err,dec_err,bmaj,bmin,pos_angle,rms=np.loadtxt('Final_Fit_Results.txt',usecols=(1,2,3,4,5,6,7,8,9,10),unpack=True)
-peak_flux = []
-j = 0
-for i in np.concatenate([np.arange(1,Source_Num+1),np.arange(1,Source_Num+1)]):
-	j += 1
-	if j < 22:
-		peak_flux.append(np.loadtxt('SERPS_lower.S'+str(i)+'-gaussest.txt',delimiter=',',usecols=(0,)))
-	elif j > 21:
-		peak_flux.append(np.loadtxt('SERPS_upper.S'+str(i)+'-gaussest.txt',delimiter=',',usecols=(0,)))
-peak_flux = np.array(peak_flux)
-
-# Convert flux values to mJy
-flux *= 1e3
-flux_err *= 1e3
-peak_flux *= 1e3
-rms *= 1e3
-
-# Convert RA and DEC to J2000
-ra = 360 + ra 
-ra_frac = ra/360. * 24
-ra_h = np.array(np.floor(ra_frac),int)
-ra_m = np.array(np.floor((ra_frac - ra_h)*60),int)
-ra_s = np.around(((ra_frac - ra_h)*60 - ra_m)*60,1)
-ra_s = np.array(map(lambda x:"%02g" % (x,), ra_s))
-ra_sexig = np.array([a+':'+b+':'+c for a,b,c in zip(np.array(ra_h,str),np.array(ra_m,str),np.array(ra_s,str))])
-
-dec_deg = np.ceil(dec)
-dec_m = np.array(np.floor((dec_deg-dec)*60),int)
-dec_s = np.around( ((dec_deg-dec)*60 - dec_m)*60,1)
-dec_deg = np.array(map(lambda x: "%03d" % (x), dec_deg))
-dec_m = np.array(map(lambda x:"%02d" % (x), dec_m))
[…]

### 2014-12-02 Gauss_Fitting/Make_Estimates.py

@@ -1,55 +1,0 @@
-"""
-This code interactively takes in data to write out estimates files needed by SERPS_Gauss_Fit.py
-"""
-import numpy as np
-
-# Define Constants
-Source_Num = 21		# Number of Sources in Field of View, see SS_Targets.reg
-Image_Num = 2		# Number of Images with same sources
-
-sources = []
-source_id=np.array(np.arange(1,Source_Num+1),str)
-for p in range(Source_Num*Image_Num):
-	if p < 21:
-		sources.append('SERPS_lower.S'+source_id[p])	
-	else:
-		sources.append('SERPS_upper.S'+source_id[p-21])
-
-sources = np.array(sources)
-
-for i in np.arange(0,Source_Num*Image_Num):
-	file = open(sources[i]+'-gaussest.txt','r')
-	cont = False
-	while cont == False:
-		print ''
-		print 'Working on Source:',sources[i]
-		print '-'*25
-		flux = raw_input('Flux density of center pixel? (Jy) : ')
-		x = raw_input('X pixel coordinate of center pixel? : ')
-		y = raw_input('Y pixel coordinate of center pixel? : ')
-		major_axis = '3.15arcsec' #raw_input('Major axis of beam? (#.##arcsec) : ')
-		minor_axis = '2.52arcsec' #raw_input('Minor axis of beam? (#.##arcsec) : ')
-		position_angle = '12.7deg' #raw_input('Position angle of beam? (###.#deg) : ')
-		print 'Given Values:'
-		print 'flux =',flux
-		print 'x =',x
-		print 'y =',y
-		print 'major_axis =',major_axis
-		print 'minor_axis =',minor_axis
-		print 'position_angle =',position_angle
-		read = raw_input('Is this correct? (y/n) : ')
-		if read == 'y':
-			cont = True
-		else:
-			print 'Try again...'	
-
-	print '...Writing Data for Source:',sources[i]
-	file.write(str(flux)+','+str(x)+','+str(y)+','+str(major_axis)+','+str(minor_axis)+','+str(position_angle)+'\n')
-	file.close()
-
-
-
-
-
-
-

### 2014-12-02 Gauss_Fitting/SERPS_Gauss_Fit.py

@@ -1,236 +1,0 @@
-"""
- - This code takes the two SERPS.**.fits files and uses imfit-sources.py to fit 
-Gaussians to sources in the images.
-
- - To be run within CASA: execfile('SERPS_Gauss_Fit.py')
-
- - Dependent on readcol.py
-	http://code.google.com/p/agpy/source/browse/trunk/agpy/readcol.py
-
-May, 2014
-"""
-
-### Import Modules ###
-print '...Loading Modules'
-print '-'*30
-import numpy as np
-import matplotlib.pyplot as mp
-from readcol import *
-import os, sys
-
-
-### Define Flags ###
-
-
-### Functions ###
-def extractcomponents(sourcename=None,componentlist=None,comp=None,rms=None):
-	print comp
-	#outputfilefits = open(sourcename+'-fitresults.txt','w')
-	#outputfileseps = open(sourcename+'-separations.txt','w')
-	cl.open(componentlist)
-	separations=np.zeros(comp, dtype=float)
-	e_separations=np.zeros(comp, dtype=float)
-	rakeep=np.zeros(comp, dtype=float)
-	deckeep=np.zeros(comp, dtype=float)
-	e_rakeep=np.zeros(comp, dtype=float)
-	e_deckeep=np.zeros(comp, dtype=float)
-
-	for j in range(comp):
-		fit=cl.getcomponent(j)
-		flux = fit['flux']['value']
-		e_flux = fit['flux']['error']
-		print flux[0]
-		ra = fit['shape']['direction']['m0']['value']*180.0/3.14159265
-		dec = fit['shape']['direction']['m1']['value']*180.0/3.14159265
-		e_ra = fit['shape']['direction']['error']['latitude']['value']
-		e_dec = fit['shape']['direction']['error']['longitude']['value']
-		bmaj = fit['shape']['majoraxis']['value']*60.0     
-		bmin = fit['shape']['minoraxis']['value']*60.0       
-		pa =   fit['shape']['positionangle']['value']
-		print ra,dec,e_ra,e_dec,bmaj,bmin
-		line = str(sourcename[:])+" "+str(flux[0])+" "+str(e_flux[0])+ " " +str(ra)+" "+str(dec)+" "+str(e_ra)+" "+str(e_dec)+" " +str(bmaj)+" "+str(bmin)+" "+str(pa)+" "+str(rms)+"\n"
-		rakeep[j]=ra
[…]

### 2014-12-02 Gauss_Fitting/Table.py

@@ -1,207 +1,0 @@
-'''
-Table.py
-
-A module/class for creating LaTeX deluxetable's.  In a nutshell, you create
-a table instance, add columns, set options, then call the pring method.'''
-
-import numpy
-import sigfig
-import os,string,re,sys
-import types
-
-float_types = [types.FloatType, numpy.float16, numpy.float32, numpy.float64,
-      numpy.float128]
-
-class Table:
-
-   def __init__(self, numcols, justs=None, fontsize=None, rotate=False, 
-         tablewidth=None, tablenum=None, caption=None, label=None):
-
-      self.numcols = numcols
-      self.justs = justs
-      if self.justs is None:
-         self.justs = ['c' for i in range(numcols)]
-      else:
-         self.justs = list(justs)
-         if len(self.justs) != numcols:
-            raise ValueError, "Error, justs must have %d elements" % (numcols)
-      for just in self.justs:
-         if just not in ['c','r','l']:
-            raise ValueError, "Error, invalid character for just: %s" % just
-      self.fontsize = fontsize
-      self.rotate = rotate
-      self.tablewidth = tablewidth
-      self.tablenum = None
-      self.caption = caption
-      self.label = label
-      self.col_justs = []
-      self.headers = []
-      self.header_ids = []
-      # self.data is a list of data.  Each element of the list corresponds
-      #  to a separate "secton" of the table, headed by self.data_labels
-      # Each element of data should be a list of self.numcols items.
-      self.data = []
-      self.data_labels = []
-      self.data_label_types = []
-      self.sigfigs = []
-      self.nrows = []
-
-   def add_header_row(self, headers, header2=None, cols=None):
-      '''Add a header row to the table.  [headers] should be a list of the
-      strings that will be in the header.  [cols], if specified, should be a 
-      list of column indexes.  If [cols] is None, it is assummed the headers
-      are in order and there are no multicolumns.  If cols is specified, you
-      can indicate the the ith header spans several columns by setting the
-      ith value of cols to a 2-tuple of first and last columns for the span.'''
-      
-      if cols is None:
-         if len(headers) != self.numcols:
-            raise ValueError, "Error, headers must be a list of length %d" %\
-                  self.numcols
-         self.headers.append(headers)
-         self.header_ids.append(range(self.numcols))
-         if header2 != None:
[…]

### 2014-12-02 Gauss_Fitting/imfit-sources.py

@@ -1,127 +1,0 @@
-from readcol import *
-import numpy as np
-
-
-
-def extractcomponents(sourcename=None,componentlist=None,comp=None,rms=None):
-   print comp
-  # outputfilefits = open(sourcename+'-fitresults.txt','w')
-   #outputfileseps = open(sourcename+'-separations.txt','w')
-   cl.open(componentlist)
-   separations=np.zeros(comp, dtype=float)
-   e_separations=np.zeros(comp, dtype=float)
-   rakeep=np.zeros(comp, dtype=float)
-   deckeep=np.zeros(comp, dtype=float)
-   e_rakeep=np.zeros(comp, dtype=float)
-   e_deckeep=np.zeros(comp, dtype=float)
-
-   for j in range(comp):
-      fit=cl.getcomponent(j)
-      flux = fit['flux']['value']
-      e_flux = fit['flux']['error']
-      print flux[0]
-      ra = fit['shape']['direction']['m0']['value']*180.0/3.14159265
-      dec = fit['shape']['direction']['m1']['value']*180.0/3.14159265
-      e_ra = fit['shape']['direction']['error']['latitude']['value']
-      e_dec = fit['shape']['direction']['error']['longitude']['value']
-      bmaj = fit['shape']['majoraxis']['value']*60.0     
-      bmin = fit['shape']['minoraxis']['value']*60.0       
-      pa =   fit['shape']['positionangle']['value']
-      print ra,dec,e_ra,e_dec,bmaj,bmin
-      line = str(sourcename[:])+" "+str(flux[0])+" "+str(e_flux[0])+ " " +str(ra)+" "+str(dec)+" "+str(e_ra)+" "+str(e_dec)+" " +str(bmaj)+" "+str(bmin)+" "+str(pa)+" "+str(rms)+"\n"
-      rakeep[j]=ra
-      deckeep[j]=dec
-      e_rakeep[j]=e_ra
-      e_deckeep[j]=e_dec
-      outputfilefits.writelines(line)
-   print range(comp)
-   iter=0
-   for j in range(comp):
-      for k in range(comp):
-         print e_rakeep[j], e_deckeep[j],e_rakeep[k], e_deckeep[k]
-         if j != k and k > j:
-            print iter
-            dra=rakeep[j]* 3600.0-rakeep[k]* 3600.0
-            ddec=deckeep[j]* 3600.0-deckeep[k]* 3600.0
-
[…]

### 2014-12-02 Make_Figs.py

@@ -1,266 +1,0 @@
-## Make Paper Figures
-import numpy as np
-import matplotlib.pyplot as mp
-import astropy.io.fits as fits
-from astropy.wcs import WCS
-from wcsaxes import WCSAxes
-from astropy import units as u
-import DictEZ as dez
-import aplpy
-from PIL import Image
-import matplotlib
-from astropy import coordinates as coord
-from astropy import units as u
-
-## Flags
-savefig = False
-
-plot1 = False
-plot2 = False
-plot3 = True
-
-
-def sexig_to_deg(ra,dec):
-	length = len(ra)
-	ra_deg = []
-	dec_deg = []
-	for i in range(length):
-		_ra_deg = np.float(ra[i][0:2])*360./24. + np.float(ra[i][3:5])*360./24./60. + np.float(ra[i][6:10])*360./24./60./60.
-		_dec_deg = (np.float(dec[i][1:3]) + np.float(dec[i][4:6])/60. + np.float(dec[i][7:11])/3600.)*np.float(dec[i][0]+'1')
-		ra_deg.append(_ra_deg)
-		dec_deg.append(_dec_deg)
-	ra_deg = np.array(ra_deg)
-	dec_deg = np.array(dec_deg)
-	return ra_deg,dec_deg
-
-def get_zorder(layers):
-	''' Gets zorder of a aplpy figure given dictionary *layers* (fig._layers) '''
-	zorder_values = {}
-	zorder_paths = {}
-	for a in layers:
-		try:
-			zorder = layers[a].get_zorder()
-			path = layers[a]
-		except AttributeError:
-			try:
-				zorder = layers[a].collections[0].get_zorder()
-				path = layers[a].collections[0]
-			except AttributeError:
-				try:
-					zorder = layers[a].artistlist[0].get_zorder()
-					path = layers[a].artistlist[0]	
-				except:
-					print "Couldn't get zorder for layer:",a
-					zorder = np.nan
-					paths = np.nan
-		zorder_values[a] = zorder
-		zorder_paths[a] = path
-	return zorder_values, zorder_paths
-
-### Herschel map w/ Spitzer sources and VLA primary beam
-if plot1 == True:
-	# Load and Configure Images
[…]

### 2014-12-02 SERPS_SED.py

@@ -1,165 +1,0 @@
-"""
-This code takes the gaussian fitted data and derives the Spectral Index of the sources with fits
-
-May, 2014
-"""
-
-### Import Modules ###
-import numpy as np
-import matplotlib.pyplot as mp
-import scipy.stats as stats
-
-### Flags, Constants ###
-lower_freq	= 4750.00		# MHz
-upper_freq	= 7250.00		# MHz
-lower_passband	= [4238.00,5262.00]	# MHz
-upper_passband	= [6738.00,7762.00]	# MHz
-Source_Num	= 21
-Image_Num	= 2
-c		= 2.9979e8		# m/s
-
-
-### Program ###
-
-# Load Data, arrays with 0.0000 are nulls
-data = np.loadtxt('Gauss_Fitting/Final_Fit_Results.txt',usecols=(1,2,3,4,5,6,7,8,9,10))
-sources = np.loadtxt('Gauss_Fitting/Final_Fit_Results.txt',usecols=(0,),dtype=str)
-
-lower_data = data[0:21]
-lower_sources = sources[0:21]
-upper_data = data[21:]
-upper_sources = sources[21:]
-
-# data arrays have 2nd axis metadata of:
-# flux,flux_e,ra,dec,ra_e,dec_e,bmaj,bmin,pa,rms
-
-# Find sources with fit in both upper and lower
-fitted = np.array([0,1,2,3,4,5,6,7,10,11,12,14,16,18,19,20])	# Indicies
-
-# Load Gutermuth Cross Match data
-RA_VLA,Dec_VLA,jmag,hmag,kmag,i1mag,i2mag,i3mag,i4mag,m24mag,p70mag = np.loadtxt('vla_serps_merger_gutermuth_try1.csv',delimiter=',',unpack=True)
-# -100 are nulls
-# jhk mags are 2mass near infrared 
-# i1,i2,i3,i4 are IRAC on Spitzer
-# m24 is MIPS 24 micron on Spitzer 
-# p70 is PACS 70 micron on Herschel
-
-# Write ds9 region file for RA and DEC coordinates
-output = open('Gutermuth_CrossMatch.reg','w')
-output.write('# Region file format: DS9 version 4.1\n')
[…]

### 2014-12-02 Gauss_Fitting/Flux_Table.py
new file:   AAS_2015/225th_AAS_Abstract.rtf 	new file:   Data/reduction_notes.txt 	new file:   Gauss_Fitting/Final_Fit_Results.txt 	new file:   Gauss_Fitting/Final_Fit_Results_old.txt 	new file:   Gauss_Fitting/Final_Fit_Results_try2.txt 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.dat 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.f0 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.f0i 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.info 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/ta

@@ -1,0 +1,115 @@
+'''
+This script takes data and prints out Latex Table strings to be copy-pasted into tablular float in master paper.tex file
+It is dependent on Table.py and sigfig.py
+'''
+import numpy as np
+import Table
+from wcsaxes import WCS
+import astropy.io.fits as fits
+
+SN = 18		# Source Number
+
+#################
+### Load Data ###
+#################
+print '...Loading Data'
+
+## Load flux data
+sourcenames = np.array(map(lambda x:"VLA "+x,np.array(np.arange(1,SN+1),str)))
+sources = np.loadtxt('Final_Fit_Results_try2.txt',usecols=(0,),dtype='str')
+flux,flux_err,ra,dec,ra_err,dec_err,bmaj,bmin,pos_angle,rms=np.loadtxt('Final_Fit_Results_try2.txt',usecols=(1,2,3,4,5,6,7,8,9,10),unpack=True)
+peak_flux = []
+j = 0
+for i in np.concatenate([np.arange(1,SN+1),np.arange(1,SN+1)]):
+	if j < SN+1:
+		peak_flux.append(np.loadtxt('Fit_Files/SERPS_lower_try2.S'+str(i)+'-gaussest_new.txt',delimiter=',',usecols=(0,)))
+	elif j > SN:
+		peak_flux.append(np.loadtxt('Fit_Files/SERPS_upper_try2.S'+str(i)+'-gaussest_new.txt',delimiter=',',usecols=(0,)))
+peak_flux = np.array(peak_flux)
+print "Using Peak Fluxes from IMFIT's 2D Gaussian Estimates"
+
+# Put flux data into micro jansky
+flux *= 1e6
+flux_err *= 1e6
+rms *= 1e6
+
+# Configure Flux Data
+lower_flux,upper_flux = flux[0:SN],flux[SN:]
+lower_flux_err,upper_flux_err = flux_err[0:SN],flux_err[SN:]
+lower_peak_flux,upper_peak_flux = peak_flux[0:SN],peak_flux[SN:]
+lower_peak_flux_err, upper_peak_flux_err = 11.1e-5, 8.5e-6
+lower_ra,upper_ra = ra[0:SN],ra[SN:]
+lower_dec,upper_dec = dec[0:SN],dec[SN:]
+lower_ra_err,upper_ra_err = ra_err[0:SN],ra_err[SN:]
[…]

### 2014-12-02 Gauss_Fitting/Make_Estimates.py

@@ -1,0 +1,55 @@
+"""
+This code interactively takes in data to write out estimates files needed by SERPS_Gauss_Fit.py
+"""
+import numpy as np
+
+# Define Constants
+Source_Num = 18		# Number of Sources in Field of View, see SS_Targets.reg
+Image_Num = 2		# Number of Images with same sources
+
+sources = []
+source_id=np.array(np.arange(1,Source_Num+1),str)
+for p in range(Source_Num*Image_Num):
+	if p < Source_Num:
+		sources.append('SERPS_lower_try2.S'+source_id[p])	
+	else:
+		sources.append('SERPS_upper_try2.S'+source_id[p-Source_Num])
+
+sources = np.array(sources)
+
+for i in np.arange(0,Source_Num*Image_Num):
+	file = open(sources[i]+'-gaussest.txt','w')
+	cont = False
+	while cont == False:
+		print ''
+		print 'Working on Source:',sources[i]
+		print '-'*25
+		flux = raw_input('Flux density of center pixel? (Jy) : ')
+		x = raw_input('X pixel coordinate of center pixel? : ')
+		y = raw_input('Y pixel coordinate of center pixel? : ')
+		major_axis = raw_input('Major axis of beam? (#.##arcsec) : ')
+		minor_axis = raw_input('Minor axis of beam? (#.##arcsec) : ')
+		position_angle = raw_input('Position angle of beam? (###.#deg) : ')
+		print 'Given Values:'
+		print 'flux =',flux
+		print 'x =',x
+		print 'y =',y
+		print 'major_axis =',major_axis
+		print 'minor_axis =',minor_axis
+		print 'position_angle =',position_angle
+		read = raw_input('Is this correct? (y/n) : ')
+		if read == 'y':
+			cont = True
+		else:
+			print 'Try again...'	
+
+	print '...Writing Data for Source:',sources[i]
+	file.write(str(flux)+','+str(x)+','+str(y)+','+str(major_axis)+','+str(minor_axis)+','+str(position_angle)+'\n')
+	file.close()
+
+
+
+
+
+
+

### 2014-12-02 Gauss_Fitting/SERPS_Gauss_Fit.py

@@ -1,0 +1,248 @@
+"""
+ - This code takes the two SERPS.**.fits files and uses imfit-sources.py to fit 
+Gaussians to sources in the images.
+
+ - To be run within CASA: execfile('SERPS_Gauss_Fit.py')
+
+ - Dependent on readcol.py
+	http://code.google.com/p/agpy/source/browse/trunk/agpy/readcol.py
+
+May, 2014
+"""
+
+### Import Modules ###
+print '...Loading Modules'
+print '-'*30
+import numpy as np
+import matplotlib.pyplot as mp
+from readcol import *
+import os, sys
+
+
+### Define Flags ###
+
+
+### Functions ###
+def extractcomponents(sourcename=None,componentlist=None,comp=None,rms=None):
+	print comp
+	#outputfilefits = open(sourcename+'-fitresults.txt','w')
+	#outputfileseps = open(sourcename+'-separations.txt','w')
+	cl.open(componentlist)
+	separations=np.zeros(comp, dtype=float)
+	e_separations=np.zeros(comp, dtype=float)
+	rakeep=np.zeros(comp, dtype=float)
+	deckeep=np.zeros(comp, dtype=float)
+	e_rakeep=np.zeros(comp, dtype=float)
+	e_deckeep=np.zeros(comp, dtype=float)
+
+	for j in range(comp):
+		fit=cl.getcomponent(j)
+		flux = fit['flux']['value']
+		e_flux = fit['flux']['error']
+		print flux[0]
+		ra = fit['shape']['direction']['m0']['value']*180.0/3.14159265
+		dec = fit['shape']['direction']['m1']['value']*180.0/3.14159265
+		e_ra = fit['shape']['direction']['error']['latitude']['value']
+		e_dec = fit['shape']['direction']['error']['longitude']['value']
+		bmaj = fit['shape']['majoraxis']['value']*60.0     
+		bmin = fit['shape']['minoraxis']['value']*60.0       
+		pa =   fit['shape']['positionangle']['value']
+		print ra,dec,e_ra,e_dec,bmaj,bmin
+		line = str(sourcename[:])+" "+str(flux[0])+" "+str(e_flux[0])+ " " +str(ra)+" "+str(dec)+" "+str(e_ra)+" "+str(e_dec)+" " +str(bmaj)+" "+str(bmin)+" "+str(pa)+" "+str(rms)+"\n"
+		rakeep[j]=ra
+		deckeep[j]=dec
[…]

### 2014-12-02 Make_Figs.py

@@ -1,0 +1,333 @@
+## Make Paper Figures
+import numpy as np
+import matplotlib.pyplot as mp
+import astropy.io.fits as fits
+from astropy.wcs import WCS
+from wcsaxes import WCSAxes
+from astropy import units as u
+import DictEZ as dez
+import aplpy
+from PIL import Image
+import matplotlib
+from astropy import coordinates as coord
+from astropy import units as u
+from matplotlib.widgets import Slider
+
+
+## Flags
+savefig = False
+
+plot1 = False
+plot2 = True
+plot3 = False
+
+
+def sexig_to_deg(ra,dec):
+	length = len(ra)
+	ra_deg = []
+	dec_deg = []
+	for i in range(length):
+		_ra_deg = np.float(ra[i][0:2])*360./24. + np.float(ra[i][3:5])*360./24./60. + np.float(ra[i][6:10])*360./24./60./60.
+		_dec_deg = (np.float(dec[i][1:3]) + np.float(dec[i][4:6])/60. + np.float(dec[i][7:11])/3600.)*np.float(dec[i][0]+'1')
+		ra_deg.append(_ra_deg)
+		dec_deg.append(_dec_deg)
+	ra_deg = np.array(ra_deg)
+	dec_deg = np.array(dec_deg)
+	return ra_deg,dec_deg
+
+def get_zorder(layers):
+	''' Gets zorder of a aplpy figure given dictionary *layers* (fig._layers) '''
+	zorder_values = {}
+	zorder_paths = {}
+	for a in layers:
+		try:
+			zorder = layers[a].get_zorder()
+			path = layers[a]
+		except AttributeError:
+			try:
+				zorder = layers[a].collections[0].get_zorder()
+				path = layers[a].collections[0]
+			except AttributeError:
+				try:
+					zorder = layers[a].artistlist[0].get_zorder()
+					path = layers[a].artistlist[0]	
+				except:
+					print "Couldn't get zorder for layer:",a
+					zorder = np.nan
+					paths = np.nan
+		zorder_values[a] = zorder
+		zorder_paths[a] = path
+	return zorder_values, zorder_paths
+
+### Herschel map w/ Spitzer sources and VLA primary beam
+if plot1 == True:
[…]

### 2014-12-02 git_add.sh

@@ -1,0 +1,79 @@
+git add IRAM_sources.txt
+git add Lower_Peak_Fluxes.csv
+git add Lower_Peak_Fluxes_try2.csv
+git add MSX_Catalogue.tsv
+git add Make_Figs.py
+git add NVSS_Catalogue.tsv
+git add Observers_Log.pdf
+git add RMS_Catalogue.tsv
+git add Rodriguez10_IR_Sources.fit
+git add Rodriguez10_IR_Sources.reg
+git add Rodriguez10_VLA_Sources.fit
+git add Rodriguez10_VLA_Sources.reg
+git add Rodriguez10_VLA_Sources_ICRS.reg
+git add SERPS_SED.py
+git add SS_Final_Sources.crtf
+git add SS_Final_Sources.reg
+git add SS_Final_Sources.txt
+git add SS_Final_Sources_deg.reg
+git add SS_Final_Sources_lowerbriggs05pxl.reg
+git add SS_Final_Sources_upperbriggs05pxl.reg
+git add SS_Labels.txt
+git add SS_Targets.reg
+git add SS_Targets_ICRS.reg
+git add SS_Targets_ICRS.txt
+git add SS_Targets_pxl.reg
+git add SerpSouthGutermuth.reg
+git add Shirley07Data/
+git add Upper_Peak_Fluxes.csv
+git add Upper_Peak_Fluxes_try2.csv
+git add fluxscale_output.txt
+git add git_add.sh
+git add gutermuth2008_serps_ysos1.crtf
+git add gutermuth2008_serps_ysos1.reg
+git add gutermuth2008_serps_ysos1.txt
+git add notes_serpsouth_reduction.txt
+git add serps_yso1.reg
+git add vla_serps_merger_gutermuth_try1.csv
+
+git add AAS_2015/225th_AAS_Abstract.rtf
+
+git add Data/reduction_notes.txt
+
+git add Gauss_Fitting/Final_Fit_Results.txt
+git add Gauss_Fitting/Final_Fit_Results_old.txt
+git add Gauss_Fitting/Final_Fit_Results_try2.txt
+git add Gauss_Fitting/Fit_Latex_Table.tex
+git add Gauss_Fitting/Flux_Table.py
+git add Gauss_Fitting/
+git add Gauss_Fitting/
+git add Gauss_Fitting/
+git add Gauss_Fitting/
+git add Gauss_Fitting/Make_Estimates.py
[…]

### 2014-12-02 Gauss_Fitting/Flux_Table.py
deleted:    AAS_2015/225th_AAS_Abstract.rtf 	deleted:    Data/reduction_notes.txt 	deleted:    Gauss_Fitting/Final_Fit_Results.txt 	deleted:    Gauss_Fitting/Final_Fit_Results_old.txt 	deleted:    Gauss_Fitting/Final_Fit_Results_try2.txt 	deleted:    Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.dat 	deleted:    Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.f0 	deleted:    Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.f0i 	deleted:    Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/table.info 	deleted:    Gauss_Fitting/Fit_Files/SERPS_lower.S1-fitcomps.cl/ta

@@ -1,115 +1,0 @@
-'''
-This script takes data and prints out Latex Table strings to be copy-pasted into tablular float in master paper.tex file
-It is dependent on Table.py and sigfig.py
-'''
-import numpy as np
-import Table
-from wcsaxes import WCS
-import astropy.io.fits as fits
-
-SN = 18		# Source Number
-
-#################
-### Load Data ###
-#################
-print '...Loading Data'
-
-## Load flux data
-sourcenames = np.array(map(lambda x:"VLA "+x,np.array(np.arange(1,SN+1),str)))
-sources = np.loadtxt('Final_Fit_Results_try2.txt',usecols=(0,),dtype='str')
-flux,flux_err,ra,dec,ra_err,dec_err,bmaj,bmin,pos_angle,rms=np.loadtxt('Final_Fit_Results_try2.txt',usecols=(1,2,3,4,5,6,7,8,9,10),unpack=True)
-peak_flux = []
-j = 0
-for i in np.concatenate([np.arange(1,SN+1),np.arange(1,SN+1)]):
-	if j < SN+1:
-		peak_flux.append(np.loadtxt('Fit_Files/SERPS_lower_try2.S'+str(i)+'-gaussest_new.txt',delimiter=',',usecols=(0,)))
-	elif j > SN:
-		peak_flux.append(np.loadtxt('Fit_Files/SERPS_upper_try2.S'+str(i)+'-gaussest_new.txt',delimiter=',',usecols=(0,)))
-peak_flux = np.array(peak_flux)
-print "Using Peak Fluxes from IMFIT's 2D Gaussian Estimates"
-
-# Put flux data into micro jansky
-flux *= 1e6
-flux_err *= 1e6
-rms *= 1e6
-
-# Configure Flux Data
-lower_flux,upper_flux = flux[0:SN],flux[SN:]
-lower_flux_err,upper_flux_err = flux_err[0:SN],flux_err[SN:]
-lower_peak_flux,upper_peak_flux = peak_flux[0:SN],peak_flux[SN:]
-lower_peak_flux_err, upper_peak_flux_err = 11.1e-5, 8.5e-6
-lower_ra,upper_ra = ra[0:SN],ra[SN:]
-lower_dec,upper_dec = dec[0:SN],dec[SN:]
-lower_ra_err,upper_ra_err = ra_err[0:SN],ra_err[SN:]
[…]

### 2014-12-02 Gauss_Fitting/Make_Estimates.py

@@ -1,55 +1,0 @@
-"""
-This code interactively takes in data to write out estimates files needed by SERPS_Gauss_Fit.py
-"""
-import numpy as np
-
-# Define Constants
-Source_Num = 18		# Number of Sources in Field of View, see SS_Targets.reg
-Image_Num = 2		# Number of Images with same sources
-
-sources = []
-source_id=np.array(np.arange(1,Source_Num+1),str)
-for p in range(Source_Num*Image_Num):
-	if p < Source_Num:
-		sources.append('SERPS_lower_try2.S'+source_id[p])	
-	else:
-		sources.append('SERPS_upper_try2.S'+source_id[p-Source_Num])
-
-sources = np.array(sources)
-
-for i in np.arange(0,Source_Num*Image_Num):
-	file = open(sources[i]+'-gaussest.txt','w')
-	cont = False
-	while cont == False:
-		print ''
-		print 'Working on Source:',sources[i]
-		print '-'*25
-		flux = raw_input('Flux density of center pixel? (Jy) : ')
-		x = raw_input('X pixel coordinate of center pixel? : ')
-		y = raw_input('Y pixel coordinate of center pixel? : ')
-		major_axis = raw_input('Major axis of beam? (#.##arcsec) : ')
-		minor_axis = raw_input('Minor axis of beam? (#.##arcsec) : ')
-		position_angle = raw_input('Position angle of beam? (###.#deg) : ')
-		print 'Given Values:'
-		print 'flux =',flux
-		print 'x =',x
-		print 'y =',y
-		print 'major_axis =',major_axis
-		print 'minor_axis =',minor_axis
-		print 'position_angle =',position_angle
-		read = raw_input('Is this correct? (y/n) : ')
-		if read == 'y':
-			cont = True
-		else:
-			print 'Try again...'	
-
-	print '...Writing Data for Source:',sources[i]
-	file.write(str(flux)+','+str(x)+','+str(y)+','+str(major_axis)+','+str(minor_axis)+','+str(position_angle)+'\n')
-	file.close()
-
-
-
-
-
-
-

### 2014-12-02 Gauss_Fitting/SERPS_Gauss_Fit.py

@@ -1,248 +1,0 @@
-"""
- - This code takes the two SERPS.**.fits files and uses imfit-sources.py to fit 
-Gaussians to sources in the images.
-
- - To be run within CASA: execfile('SERPS_Gauss_Fit.py')
-
- - Dependent on readcol.py
-	http://code.google.com/p/agpy/source/browse/trunk/agpy/readcol.py
-
-May, 2014
-"""
-
-### Import Modules ###
-print '...Loading Modules'
-print '-'*30
-import numpy as np
-import matplotlib.pyplot as mp
-from readcol import *
-import os, sys
-
-
-### Define Flags ###
-
-
-### Functions ###
-def extractcomponents(sourcename=None,componentlist=None,comp=None,rms=None):
-	print comp
-	#outputfilefits = open(sourcename+'-fitresults.txt','w')
-	#outputfileseps = open(sourcename+'-separations.txt','w')
-	cl.open(componentlist)
-	separations=np.zeros(comp, dtype=float)
-	e_separations=np.zeros(comp, dtype=float)
-	rakeep=np.zeros(comp, dtype=float)
-	deckeep=np.zeros(comp, dtype=float)
-	e_rakeep=np.zeros(comp, dtype=float)
-	e_deckeep=np.zeros(comp, dtype=float)
-
-	for j in range(comp):
-		fit=cl.getcomponent(j)
-		flux = fit['flux']['value']
-		e_flux = fit['flux']['error']
-		print flux[0]
-		ra = fit['shape']['direction']['m0']['value']*180.0/3.14159265
-		dec = fit['shape']['direction']['m1']['value']*180.0/3.14159265
-		e_ra = fit['shape']['direction']['error']['latitude']['value']
-		e_dec = fit['shape']['direction']['error']['longitude']['value']
-		bmaj = fit['shape']['majoraxis']['value']*60.0     
-		bmin = fit['shape']['minoraxis']['value']*60.0       
-		pa =   fit['shape']['positionangle']['value']
-		print ra,dec,e_ra,e_dec,bmaj,bmin
-		line = str(sourcename[:])+" "+str(flux[0])+" "+str(e_flux[0])+ " " +str(ra)+" "+str(dec)+" "+str(e_ra)+" "+str(e_dec)+" " +str(bmaj)+" "+str(bmin)+" "+str(pa)+" "+str(rms)+"\n"
-		rakeep[j]=ra
-		deckeep[j]=dec
[…]

### 2014-12-02 Make_Figs.py

@@ -1,333 +1,0 @@
-## Make Paper Figures
-import numpy as np
-import matplotlib.pyplot as mp
-import astropy.io.fits as fits
-from astropy.wcs import WCS
-from wcsaxes import WCSAxes
-from astropy import units as u
-import DictEZ as dez
-import aplpy
-from PIL import Image
-import matplotlib
-from astropy import coordinates as coord
-from astropy import units as u
-from matplotlib.widgets import Slider
-
-
-## Flags
-savefig = False
-
-plot1 = False
-plot2 = True
-plot3 = False
-
-
-def sexig_to_deg(ra,dec):
-	length = len(ra)
-	ra_deg = []
-	dec_deg = []
-	for i in range(length):
-		_ra_deg = np.float(ra[i][0:2])*360./24. + np.float(ra[i][3:5])*360./24./60. + np.float(ra[i][6:10])*360./24./60./60.
-		_dec_deg = (np.float(dec[i][1:3]) + np.float(dec[i][4:6])/60. + np.float(dec[i][7:11])/3600.)*np.float(dec[i][0]+'1')
-		ra_deg.append(_ra_deg)
-		dec_deg.append(_dec_deg)
-	ra_deg = np.array(ra_deg)
-	dec_deg = np.array(dec_deg)
-	return ra_deg,dec_deg
-
-def get_zorder(layers):
-	''' Gets zorder of a aplpy figure given dictionary *layers* (fig._layers) '''
-	zorder_values = {}
-	zorder_paths = {}
-	for a in layers:
-		try:
-			zorder = layers[a].get_zorder()
-			path = layers[a]
-		except AttributeError:
-			try:
-				zorder = layers[a].collections[0].get_zorder()
-				path = layers[a].collections[0]
-			except AttributeError:
-				try:
-					zorder = layers[a].artistlist[0].get_zorder()
-					path = layers[a].artistlist[0]	
-				except:
-					print "Couldn't get zorder for layer:",a
-					zorder = np.nan
-					paths = np.nan
-		zorder_values[a] = zorder
-		zorder_paths[a] = path
-	return zorder_values, zorder_paths
-
-### Herschel map w/ Spitzer sources and VLA primary beam
-if plot1 == True:
[…]

### 2014-12-02 SERPS_SED.py

@@ -1,441 +1,0 @@
-"""
-This code takes the gaussian fitted data and derives the Spectral Index of the sources with fits
-Also does other stuffs...
-
-December, 2014
-nkern@umich.edu
-"""
-
-### Import Modules ###
-print '...importing modules'
-import numpy as np
-import matplotlib.pyplot as mp
-import scipy.stats as stats
-import numpy.ma as ma
-from mpl_toolkits.axes_grid1 import AxesGrid
-
-print '...done importing'
-
-### Flags, Constants ###
-lower_freq	= 4750.00		# MHz
-upper_freq	= 7250.00		# MHz
-lower_passband	= [4238.00,5262.00]	# MHz
-upper_passband	= [6738.00,7762.00]	# MHz
-Source_Num	= 18
-Image_Num	= 2
-c		= 2.9979e8		# m/s
-
-### Program ###
-
-
-###############################################################################
-########################### Load Data #########################################
-###############################################################################
-
-print '...loading Gutermuth Cross Match Data'
-## Load Gutermuth Cross Match data
-RA_VLA,Dec_VLA,jmag,hmag,kmag,i1mag,i2mag,i3mag,i4mag,m24mag,p70mag = np.loadtxt('vla_serps_merger_gutermuth_try1.csv',delimiter=',',unpack=True)
-# -100 are nulls
-# jhk mags are 2mass near infrared 
-# i1,i2,i3,i4 are IRAC on Spitzer
-# m24 is MIPS 24 micron on Spitzer 
-# p70 is PACS 70 micron on Herschel
-
-# Write ds9 region file for RA and DEC coordinates
-#output = open('Gutermuth_CrossMatch.reg','w')
-#output.write('# Region file format: DS9 version 4.1\n')
-#output.write('global color=magenta dashlist=8 3 width=1 font="helvetica 10 normal roman" select=1 highlite=1 dash=0 fixed=0 edit=1 move=1 delete=1 include=1 source=1\n')
-#output.write('fk5\n')
-#for i in range(len(RA_VLA)):
-#	output.write('point('+str(RA_VLA[i])+','+str(Dec_VLA[i])+') # point=x text={'+str(i+1)+'}\n')
-
-#output.close()
-
[…]

### 2014-12-02 git_add.sh

@@ -1,79 +1,0 @@
-git add IRAM_sources.txt
-git add Lower_Peak_Fluxes.csv
-git add Lower_Peak_Fluxes_try2.csv
-git add MSX_Catalogue.tsv
-git add Make_Figs.py
-git add NVSS_Catalogue.tsv
-git add Observers_Log.pdf
-git add RMS_Catalogue.tsv
-git add Rodriguez10_IR_Sources.fit
-git add Rodriguez10_IR_Sources.reg
-git add Rodriguez10_VLA_Sources.fit
-git add Rodriguez10_VLA_Sources.reg
-git add Rodriguez10_VLA_Sources_ICRS.reg
-git add SERPS_SED.py
-git add SS_Final_Sources.crtf
-git add SS_Final_Sources.reg
-git add SS_Final_Sources.txt
-git add SS_Final_Sources_deg.reg
-git add SS_Final_Sources_lowerbriggs05pxl.reg
-git add SS_Final_Sources_upperbriggs05pxl.reg
-git add SS_Labels.txt
-git add SS_Targets.reg
-git add SS_Targets_ICRS.reg
-git add SS_Targets_ICRS.txt
-git add SS_Targets_pxl.reg
-git add SerpSouthGutermuth.reg
-git add Shirley07Data/
-git add Upper_Peak_Fluxes.csv
-git add Upper_Peak_Fluxes_try2.csv
-git add fluxscale_output.txt
-git add git_add.sh
-git add gutermuth2008_serps_ysos1.crtf
-git add gutermuth2008_serps_ysos1.reg
-git add gutermuth2008_serps_ysos1.txt
-git add notes_serpsouth_reduction.txt
-git add serps_yso1.reg
-git add vla_serps_merger_gutermuth_try1.csv
-
-git add AAS_2015/225th_AAS_Abstract.rtf
-
-git add Data/reduction_notes.txt
-
-git add Gauss_Fitting/Final_Fit_Results.txt
-git add Gauss_Fitting/Final_Fit_Results_old.txt
-git add Gauss_Fitting/Final_Fit_Results_try2.txt
-git add Gauss_Fitting/Fit_Latex_Table.tex
-git add Gauss_Fitting/Flux_Table.py
-git add Gauss_Fitting/
-git add Gauss_Fitting/
-git add Gauss_Fitting/
-git add Gauss_Fitting/
-git add Gauss_Fitting/Make_Estimates.py
[…]

### 2014-12-02 Paper/paper.tex
new file:   AAS_2015/225th_AAS_Abstract.rtf 	new file:   Data/reduction_notes.txt 	new file:   Gauss_Fitting/Final_Fit_Results.txt 	new file:   Gauss_Fitting/Final_Fit_Results_old.txt 	new file:   Gauss_Fitting/Final_Fit_Results_try2.txt 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S1-gaussest.txt 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S10-gaussest.txt 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S11-gaussest.txt 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S12-gaussest.txt 	new file:   Gauss_Fitting/Fit_Files/SERPS_lower.S13-gaussest.txt 	new file:   Gauss_Fitting/Fit_Fi

@@
 %% Document Class
-\documentclass[iop]{aastex}
+\documentclass[apj]{emulateapj}
 
@@
 % Packages
-\usepackage{indentfirst}		% Used to fix non indent of 1st paragraph
-\usepackage{fancyhdr}		% Used to make custom footer / headers
-\usepackage{fixltx2e}		% Used fix Latex Corrections
-\usepackage{graphicx}		% To import figures into text
+\usepackage{graphicx}	% Graphics
 \usepackage{natbib}		% Bibliography
-\usepackage{amsmath}		% Equation Package
-\usepackage{textcomp}		% For symbols
+\usepackage{amsmath}	% Equations
+\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}		% References
+\renewcommand*{\backref}[1]{[#1]}	
+\usepackage[all]{hypcap}	% Workaround for hyperref
+\usepackage{cleveref}		% Better than autoref
+\usepackage{indentfirst}	
+\usepackage{fancyhdr}	% Header and Footer
 \usepackage{amssymb}	% More symbols
-\usepackage{booktabs}		% For tables
-\usepackage{lscape}		% For Sideways Tables
+%\usepackage{stfloats}		% For Figures on bottom of page
 
@@
 \begin{document}
-\title{Centimeter Continuum Emission From Young Stellar Objects in the Serpens South Protocluster}
-%\title{Radio Properties of Protostars in the Serpens South Star Forming Region}
+%\submitted{Submitted: \today}
+\title{Radio Properties of Protostars in the Serpens South Protocluster}
+\author{Authors}
 
-%% Abstract
+%% Abstract %%
 \begin{abstract}
-The Serpens South protostellar cluster is a site of active star formation located in the Aquila Rift, with an abundance of embedded protostars at its core.
-Radio observations of centimeter emission from the region allow for the classifications of young protostars that are still heavily shrouded, and have proven to be an essential tool in the characterization of young stellar objects.
-We report the detection of centimeter wavelength ($\lambda=4.135$ cm and $\lambda=6.311$ cm) continuum emission from previously known and unidentified young stellar objects in the core of the Serpens South protostellar cluster.
-We use the Jansky Very Large Array (VLA) to give a detailed account of the radio properties of the young stellar objects, as well as characterize the evolutionary stage and luminosity source of young stellar objects in Serpens South in conjunction with infrared mappings of the region.
-We report the detection of centimeter sources lining up with more diffuse sources in micrometer wavelengths, verifying the presence of compact cores.
-This is the first mapping of centimeter continuum emission in this region at a spatial resolution of $<$ 5 arcseconds.
+
+We present 4.14 and 6.31 centimeter continuum observations of the Serpens South protocluster with the Karl G.
+Jansky Very Large Array in its C configuration.
+Our focus is a 4' x 4' area around the central filament ($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0).
+We detect roughly 18 sources, 10 of which are probably protostellar in nature.
+We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region.
+We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously labeled starless cores.
+We compare our radio sources to the known centimeter vs.
+bolometric luminosity relationship.
+With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more radio protostars.
 
@@
 
+\maketitle
+\newpage
+
 %% Begin Paper %%
 
+%($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0)
 %% Introduction
 \section{Introduction}
+\label{sec:introduction}
 
-Radio observations of protostars have long been used as a tool to infer the presence of protostars deeply embedded in the clouds of dust and gas that are their progenitors \citep{Anglada95}.
+	Serpens South is a young stellar cluster that is apart of the broader Aquila Rift extinction feature.
+It lies south of the Serpens Main cloud, and is just West of the bright W40 HII region.
+Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars, suggesting it is in a very early phase of cluster formation.
+Since its discovery, it has become the center of a wide range of scholarship.
+This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}.
+X-ray studies of Serpens South have yet to be published.
+To-date, only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al.
+in prep), meaning that there has yet to be a radio study of Serpens South since the VLA upgraded its facilities 2012.
+Beyond this study, further radio studies of Serpens South will be important in understanding the star formation process across the electromagnetic spectrum.
 
-\begin{landscape}
-\begin{deluxetable}{lccccccccccc}
-\tablewidth{0pc}
-\tabletypesize{\scriptsize}
-\tablecolumns{12}
-\tablecaption{Caption...\label{Properties of 2D Gaussian Fits}}
-\tablehead{
-\colhead{Source Name} & \colhead{Int.
-Flux} & \colhead{Int.
-Flux Err} & \colhead{Peak Flux} & \colhead{RA} & \colhead{RA Err} & \colhead{DEC} & \colhead{DEC Err} & \colhead{Bmaj} & \colhead{Bmin} & \colhead{Pos.
-Angle} & \colhead{RMS} \\
- \colhead{} & \colhead{(mJy)} & \colhead{(mJy)} & \colhead{(mJy)} & \colhead{(J2000)} & \colhead{(arcsec)} & \colhead{(J2000)} & \colhead{(arcsec)} & \colhead{(arcsec)} & \colhead{(arcsec)} & \colhead{(degrees)} & \colhead{(mJy)}  }
-\startdata
-lower.S1 & 0.06486 & 0.02438 & 0.06500 & -82.44 & 0.8961 & -2.024 & 0.7340 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S2 & 0.5987 & 0.02511 & 0.6000 & -82.46 & 0.09998 & -2.009 & 0.08190 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S3 & 0.04091 & 0.02534 & 0.04100 & -82.47 & 1.476 & -2.013 & 1.209 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S4 & 0.1197 & 0.01196 & 0.1200 & -82.48 & 0.2380 & -2.010 & 0.1950 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S5 & 0.07284 & 0.01367 & 0.07300 & -82.49 & 0.4473 & -2.013 & 0.3664 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S6 & 0.9978 & 0.02082 & 1.000 & -82.49 & 0.04973 & -2.014 & 0.04074 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S7 & 0.05687 & 0.02516 & 0.05700 & -82.47 & 1.054 & -2.025 & 0.8638 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S8 & 0.04290 & 0.02563 & 0.04300 & -82.48 & 0.0003964 & -2.029 & 0.0003247 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S9 & 0.000 & 0.000 & 0.04000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
-lower.S10 & 0.000 & 0.000 & 0.1100 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
-lower.S11 & 0.1497 & 0.1033 & 0.1500 & -82.49 & 1.646 & -2.042 & 1.348 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S12 & 0.1497 & 0.01350 & 0.1500 & -82.49 & 0.2150 & -2.043 & 0.1762 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S13 & 0.4290 & 0.02459 & 0.4300 & -82.49 & 0.1366 & -2.046 & 0.1119 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S14 & 0.000 & 0.000 & 0.03600 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
-lower.S15 & 0.1696 & 0.01368 & 0.1700 & -82.49 & 0.1923 & -2.052 & 0.1575 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S16 & 0.000 & 0.000 & 0.1700 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
-lower.S17 & 0.03792 & 0.02311 & 0.03800 & -82.48 & 1.453 & -2.054 & 1.190 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S18 & 0.000 & 0.000 & 0.05000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
-lower.S19 & 0.1197 & 0.01004 & 0.1200 & -82.49 & 0.1998 & -2.062 & 0.1637 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S20 & 0.05887 & 0.01186 & 0.05900 & -82.50 & 0.4802 & -2.067 & 0.3933 & 4.820 & 3.850 & 13.40 & 0.03806\\
-lower.S21 & 0.1497 & 0.02503 & 0.1500 & -82.46 & 0.3986 & -2.069 & 0.3265 & 4.820 & 3.850 & 13.40 & 0.03806\\
-upper.S1 & 0.09969 & 0.01901 & 0.1000 & -82.44 & 0.2973 & -2.024 & 0.2436 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S2 & 0.5483 & 0.01932 & 0.5500 & -82.46 & 0.05494 & -2.009 & 0.04502 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S3 & 0.02592 & 0.01936 & 0.02600 & -82.47 & 1.164 & -2.013 & 0.9542 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S4 & 0.05084 & 0.008597 & 0.05100 & -82.48 & 0.2636 & -2.010 & 0.2160 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S5 & 0.04985 & 0.008045 & 0.05000 & -82.49 & 0.2516 & -2.013 & 0.2062 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S6 & 0.3988 & 0.01086 & 0.4000 & -82.49 & 0.04245 & -2.014 & 0.03479 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S7 & 0.04486 & 0.01182 & 0.04500 & -82.47 & 0.4107 & -2.025 & 0.3365 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S8 & 0.04785 & 0.01226 & 0.04800 & -82.48 & 0.3994 & -2.029 & 0.3273 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S9 & 0.02592 & 0.007830 & 0.02600 & -82.49 & 0.4709 & -2.033 & 0.3859 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S10 & 0.05284 & 0.04357 & 0.05300 & -82.49 & 1.285 & -2.040 & 1.053 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S11 & 0.05284 & 0.03196 & 0.05300 & -82.49 & 0.9428 & -2.042 & 0.7726 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S12 & 0.05284 & 0.008033 & 0.05300 & -82.49 & 0.2370 & -2.043 & 0.1942 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S13 & 0.04486 & 0.01037 & 0.04500 & -82.49 & 0.3603 & -2.046 & 0.2952 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S14 & 0.000 & 0.000 & 0.03900 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000 & 0.000\\
-upper.S15 & 0.1894 & 0.01814 & 0.1900 & -82.49 & 0.1493 & -2.052 & 0.1223 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S16 & 0.1894 & 0.01372 & 0.1900 & -82.48 & 0.1129 & -2.053 & 0.09251 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S17 & 0.03888 & 0.01403 & 0.03900 & -82.48 & 0.5624 & -2.054 & 0.4609 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S18 & 0.05084 & 0.009118 & 0.05100 & -82.49 & 0.2796 & -2.057 & 0.2291 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S19 & 0.1196 & 0.007314 & 0.1200 & -82.49 & 0.09530 & -2.062 & 0.07810 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S20 & 0.02592 & 0.009043 & 0.02600 & -82.50 & 0.5438 & -2.067 & 0.4457 & 3.150 & 2.520 & 12.70 & 0.03004\\
-upper.S21 & 0.09969 & 0.01154 & 0.1000 & -82.46 & 0.1804 & -2.069 & 0.1478 & 3.150 & 2.520 & 12.70 & 0.03004\\
-\enddata
-\end{deluxetable}
-\end{landscape}
+	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.][]{Curiel89, Anglada98, Reipurth99, Eiroa05, Shirley07, Rodriguez10}.
+Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star.
+Theory and observations have best explained protostellar radio emission as having two components: thermal and non-thermal.
+Thermal radio emission is generally assumed to be free-free emission created from an HII region.
+High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not.
+HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar.
+Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.
 
--- Present problem
+%	  Centimeter continuum emission is largely associated with free-free emission created from ionized regions within the dense envelope surrounding the star \citep{Anglada95}.
+High-mass protostars are strong enough to create this region from stellar winds, while low-mass protostars likely create these regions from compact, collimated thermal outflows, however photoionization and stellar winds from low-mass protostars may also help sustain HII regions around the protostar \citep{Scaife12}.
+Because radio observations probe deep into the stellar envelope, centimeter observations of this nature have been a proven tool in the detection of outflow sources \citep{Rodriguez97} and in the exploration of the physical dynamics of the youngest protostellar objects \citep{Anglada98,Shirley07}.
+In this respect, centimeter observations of protostars are a crucial asset in our understanding of regions of active star formation.
 
--- Previous studies
+\subsection{Distance to Serpens South}
+\label{subsec:distance to serpens south}
 
--- Importance of field
+The distances to Serpens South, W40 and the Serpens Main cloud are not agreed upon in the literature.
+When Serpens South was discovered in 2008, a distance of 260 pc $\pm$ 37 pc was adopted based on evidence that its LSR velocities matched LSR velocities of the Serpens Main cloud, which was then thought to be a part of the larger Aquila Rift extinction feature whose distance was estimated at 260 pc by \citet{Straizys03}.
+However, VLBA parallax measurements done in 2010 have established the distance to the Serpens Main cloud as 429 $\pm$ 2 pc \citep{Dzib11}, meaning that Serpens Main is distinct from the the Aquila Rift if the latter is to have a distance of 260 pc.
 
--- Basic specs on data
-
--- Outline of paper
+\citet{Gutermuth08} also argued that Serpens South lies in front of W40, claiming that it is seen in absorption against emission from W40.
+Therefore, we know Serpens Main is at 429 pc, and we know that Serpens South lies in front of W40.
+What we don't know are the absolute distances to both W40 or Serpens South.
+If we are to follow the initial LSR velocity analysis by \citet{Gutermuth08}, we would equate Serpens South to Serpens Main and say Serpens South lies at approximately 429 pc, while W40 lies further away.
+Indeed, recent radio and x-ray studies adopt a distance of 600 pc to W40, although they admit the distance is poorly constrained \citep{Kuhn10, Rodriguez10}.
+Here, we adopt a distance of 429 pc for Serpens South, although we comment on how a 260 pc distance estimate would change our analysis.
 
@@
 
-\section{Observed Region}
--- History of region
+%% VLA Observations
+\section{Observations}
+\label{sec:observations}
 
--- Other studies of region, and current thoughts on dynamics and evolution of region
+%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
+\capstartfalse
+\begin{deluxetable}{cccc}
+\tabletypesize{\footnotesize}
+\tablecaption{EVLA Image Properties}
+\tablehead{
+	\multicolumn{1}{c}{Wavelength}			&
+	\multicolumn{1}{c}{Beam Size$^{a}$}		&
+	\multicolumn{1}{c}{Position Angle}			&
+	\multicolumn{1}{c}{Image RMS}					\\
+	\colhead{(cm)}							&
+	\colhead{(arcsec x arcsec)}					&
+	\colhead{(degrees)}							&
+	\colhead{($\mu$Jy beam$^{-1}$)}			}
+\startdata
+6.31	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
+4.14	&	3.2 x 2.5	&	12.7	&	8.5
+\enddata
+\tablenotetext{a}{Images deconvolved with robust (Briggs) weighting, \emph{robust}=0.5 \citep{Briggs95}.}
+\label{tab:image_pars}
+\end{deluxetable}
+\capstarttrue
+%%%%%%%%%%% End Table %%%%%%%%%%%%%%%
 
--- Other studies of region in radio and other wavelengths
+We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration.
+The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband.
+We focused on a 3.5 arcsec x 3.5 arcsec region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$.
+Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation.
 
--- Overview of telescope used in the study
+We manually flagged, calibrated and imaged our data with standard procedures using Common Astronomy Software Applications (CASA) 4.1.0.
+We used J1331+305 (3C286) as a flux and bandpass calibrator, and J1804+0101 as a gain and phase calibrator ($S_{6.31\text{cm}}$ = 0.70 $\pm$ 0.02 Jy, $S_{4.14\text{cm}}$ = 0.66 $\pm$ 0.02 Jy).
+We deconvolved the Stokes $I$ images with the Cotton-Schwab algorithm \citep{Schwab84} using the CLEAN method \citep{Hogbom74,Clark80}.
+We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution with robust weighting, also known as Briggs weighting \citep{Briggs95}, with a \emph{robust} parameter set to 0.5.
+The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}.
+We also deconvolved the Stokes $V$ images, but did not find any significant signal.
 
-\section{Observations \& Data Reduction}
--- Data reduction processes, RFI problems, antennas, etc..
+Observing Serpens South at radio wavelengths is difficult because of the extended and bright HII region W40 directly to the East, which adds to over-resolved flux and increases the RMS noise level in our images.
+In addition, our short integration time--45 minutes on source--left us with a less than desirable UV coverage at long UV distances.
+Long UV distance coverage is particularly important because we are trying to resolve point source emission.
+Further EVLA studies of Serpens South would benefit from extended array configurations and longer integration times.
 
--- RMS values, cleaning steps
+%% Results & Analysis
+\section{Results}
+\label{sec:results}
 
--- Acknowledgment of artifacts and bugs in images
+\subsection{Radio Source Selection}
+In choosing our sources, we restrict ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength.
+We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing our Sextractor source extracted sample \citep{Bertin96}.
+We were left with a total of 18 radio sources.
+We then ran source extractions on these spatial positions over near and far infrared data from the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
+We used a 2 arcsecond maximum matching tolerance for these extractions.
+Apertures and adopted corrections are consistent with the HOPS survey \{What source should I cite?\}
 
--- Resolution of beam
+Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond.
+A total of ten out of our 18 sources have signs that indicate they are protostellar in nature.
+One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as Class 0 and starless.
+Here, we confirm compact radio emission with a rising spectral index indicative of mixed optically thin and thick free-free emission, which suggests the presence of a compact core.
 
--- Possible errors in aperture synthesis technique
+We can calculate the number of random background sources we would expect to find in our images.
+We use the formulation found in \citet{Shirley07}, who draw from radio studies done by \citet{Fomalont91}.
+The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by $N(>S) = 0.42\cdot(S/30\ \mu \text{Jy})^{-1.18}$ arcmin$^{-2}$.
+Therefore, the total number of sources with flux $S$ greater than 50 $\mu$Jy at 6 cm is 0.229 arcmin$^{-2}$.
+This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact star, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest.
+This agrees with our analysis, as we find roughly 8 sources that are likely background sources.
+
+\
+
+%Centered on Serpens South ($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0), we collected data in the VLA C band, using two spectral windows centered at 6.311 cm and 4.135 cm, each with a bandpass width of 1,024 MHz, with two polarization pairs.
+Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour long observation time.
+Flux density and bandpass calibrations were done using observations of quasar 3C 286.
+We obtained a total of 45 minutes of integration on source.
+%
+%The data were manually inspected for radio frequency interference (RFI), and we removed obvious RFI from our visibilities.
+The data were then reduced using standard reduction techniques in CASA 4.1.0.
+Artifacts and streaks in our final images are products of incomplete $u-v$ coverage of our point spread function, which was slightly enhanced because we did not receive data from 2 of the 27 antennas in the array during our observation, in addition to the bright HII region to the east of Serpens South, contributing extended source signal to our short baselines.
+%
+%The Stokes \emph{I} image was deconvolved multiple times with the CLEAN task \citep{Hogbom74, Clark80}, using natural, robust and uniform weighting, utilizing the Cotton-Schwab algorithm \citep{Schwab84}.
+We find that the best compromise between noise level and source resolution is achieved with robust weighting \citep{Briggs95}.
+The deconvolutions that produced the highest signal to noise ratios involved using masks around our protostellar sources.
+We cleaned our 6.3 and 4.1 cm maps down to a RMS noise level of 18$\mu$Jy and 8$\mu$Jy respectively.
+Table 1 outlines these observations.
+%
+%We used a circular CLEANing mask centered on the image phase center with a radial extent of $\sim$3 arcseconds, corresponding to 80\% of primary beam strength at the center.
+Our short integration time, $\sim$45 minutes, left us with a less than desirable point source function, and we therefore set `psfmode' to `hogbom' in the CLEANing process.
+%
+%Two particularly strong radio sources in the northern part of our field of view created psf artifacts that were visible in our dirty maps.
+In addition to this, and the fact that our protostellar sources are relatively weak, we could not readily distinguish between weak protostar emission and a weak compact artifact.
+Therefore, instead of masking around individual sources, we used a circular mask around 80\% of primary beam strength during the CLEANing process.
+We compared the final CLEANed image with our psf to check for remaining psf artifacts, and used Spitzer 3.6 $\mu$m maps to spatially confirm centimeter emission from known Spitzer protostars.
+For the case where compact emission of seemingly protostellar nature does not spatially match a Spitzer protostar, nor an obvious psf artifact, we use its measured radio spectral index and the calculated random probability that it is a background source to discern whether it is a newly detected protostar.
 
@@
 
-\section{Sources}
--- Note on sources, how they were chosen
+\begin{figure}[h!]
+\label{fig:serpsouth_fov}
+\centering
+\includegraphics[keepaspectratio=True,scale=.6]{figures/SerpSouth_FOV.eps}
+\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South.
+Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively.
+The green box indicates our region of interest with the EVLA.}}
+\end{figure}
 
-\section{Results \& Analysis}
+\begin{figure}[h!]
+\label{fig:serpsouth_fov_contour}
+\centering
+\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
+\caption{\small{ 
+}}
+\end{figure}
 
+\begin{figure}[h!]
+\label{fig:serpsouth_zoom_contour}
+\centering
+\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_zoom_contour.eps}
+\caption{\small{ 
+}}
+\end{figure}
+
+\begin{figure}[h!]
+\label{fig:serpsouth_zoom_color_contour}
+\centering
+\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_zoom_color_contour.eps}
+\caption{\small{ 
+}}
+\end{figure}
+
+%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
+\capstartfalse
+\begin{deluxetable*}{lccccccc}%cccc}
+\label{tab:radio_properties_table}
+\tabletypesize{\footnotesize}
+\tablecaption{Radio Properties of VLA Sources}
+\tablehead{
+	\multicolumn{1}{c}{Source}								&
+	\multicolumn{2}{c}{Position$^{a}$}							&
+	\multicolumn{1}{c}{$S_{6.3 \text{cm}}\ ^{b}$}				&
+	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}		&
+	\multicolumn{1}{c}{$S_{4.1 \text{cm}}$}					&
+	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}		&
+	\multicolumn{1}{c}{$\alpha_{\text{radio}}\ ^{c}$}				\\ [.25ex]		
+%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
+%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
+%	\multicolumn{1}{c}{Match?}						&
+%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
+	\cline{2-3}										\\ [-1.5ex]
+	\colhead{}										&
+	\colhead{RA}									&
+	\colhead{Dec.}									&
+	\colhead{($\mu$Jy)}								&
+	\colhead{($\mu$Jy beam$^{-1}$)}					&
+	\colhead{($\mu$Jy)}								&
+	\colhead{($\mu$Jy beam$^{-1}$)}					&
+	\colhead{}										
+%	\colhead{(L$_{\text{sun}}$)}						&
+%	\colhead{(L$_{\text{sun}}$)}						&
+%	\colhead{(MM/Hersc/Spitz)}						&
+%	\colhead{Stage}								
+	}
+\startdata
+
+6.31\dotfill		&	1.024	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
+
+4.14\dotfill		&	1.024	&	3.2 x 2.5	&	12.7	&	8.5
+
+\enddata
+\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
+\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
+\tablenotetext{c}{Spectral index of peak flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
+
+\end{deluxetable*}
+\capstarttrue
+%%%%%%%%%%% End Table %%%%%%%%%%%%%%%
+
+\subsection{VLA 1, 2, 3 and 4}
+\label{subsec:vla1_2_3_4}
+
+\subsection{VLA 6, 7 and 8}
+\label{subsec:vla6_7_8}
+
+\subsection{VLA 9 to 17}
+\label{subsec:vla9_to_17}
+
+\subsection{VLA 5 and 18}
+\label{subsec:vla18}
+
+%% Discussion
 \section{Discussion}
 
+\subsection{Protostars in the Central Filament}
+Spitzer observations revealed dozens of Class I and II protostars spatially correlated to the central filament \citep{Gutermuth08}.
+Herschel observations revealed colder clumps of dust corresponding to younger Class 0 protostars \citep{Bontemps10}, however, with their poor spatial resolution they cannot reasonably resolve individual compact cores.
+
+\subsection{$L_{\text{infrared}}$ and $L_{\text{bol}}$ Relationship}
+
+\subsection{The $S_{\text{radio}}$ and $L_{\text{bol}}$ Relationship}
+
+\subsection{Sources of Molecular Outflow}
+
+The Serpens South embedded cluster occupies a region in projected proximity to the larger Aquila Rift complex, the W40 HII region and the Serpens Main molecular cloud.
+The Aquila Rift, as previously noted, is a local complex of dark molecular clouds extending several degrees, encompassing the Serpens Main molecular cloud, Serpens South and the W40 HII region (see Figure 1), which are the three main regions of star formation in the direction of the Aquila Rift \citep{Eiroa08}.
+
+%% Conclusions
 \section{Conclusions}
@@
 
+\appendix
+{\large These are my edit notes for the paper.} \\[.25in]
+
+-- What does Rob say about SS distance?\\
+
+-- What paper should I quote for infrared source extraction photometry analysis?
+
 %% End Document

### 2014-12-02 Gauss_Fitting/imfit-sources.py

@@ -1,0 +1,127 @@
+from readcol import *
+import numpy as np
+
+
+
+def extractcomponents(sourcename=None,componentlist=None,comp=None,rms=None):
+   print comp
+  # outputfilefits = open(sourcename+'-fitresults.txt','w')
+   #outputfileseps = open(sourcename+'-separations.txt','w')
+   cl.open(componentlist)
+   separations=np.zeros(comp, dtype=float)
+   e_separations=np.zeros(comp, dtype=float)
+   rakeep=np.zeros(comp, dtype=float)
+   deckeep=np.zeros(comp, dtype=float)
+   e_rakeep=np.zeros(comp, dtype=float)
+   e_deckeep=np.zeros(comp, dtype=float)
+
+   for j in range(comp):
+      fit=cl.getcomponent(j)
+      flux = fit['flux']['value']
+      e_flux = fit['flux']['error']
+      print flux[0]
+      ra = fit['shape']['direction']['m0']['value']*180.0/3.14159265
+      dec = fit['shape']['direction']['m1']['value']*180.0/3.14159265
+      e_ra = fit['shape']['direction']['error']['latitude']['value']
+      e_dec = fit['shape']['direction']['error']['longitude']['value']
+      bmaj = fit['shape']['majoraxis']['value']*60.0     
+      bmin = fit['shape']['minoraxis']['value']*60.0       
+      pa =   fit['shape']['positionangle']['value']
+      print ra,dec,e_ra,e_dec,bmaj,bmin
+      line = str(sourcename[:])+" "+str(flux[0])+" "+str(e_flux[0])+ " " +str(ra)+" "+str(dec)+" "+str(e_ra)+" "+str(e_dec)+" " +str(bmaj)+" "+str(bmin)+" "+str(pa)+" "+str(rms)+"\n"
+      rakeep[j]=ra
+      deckeep[j]=dec
+      e_rakeep[j]=e_ra
+      e_deckeep[j]=e_dec
+      outputfilefits.writelines(line)
+   print range(comp)
+   iter=0
+   for j in range(comp):
+      for k in range(comp):
+         print e_rakeep[j], e_deckeep[j],e_rakeep[k], e_deckeep[k]
+         if j != k and k > j:
+            print iter
+            dra=rakeep[j]* 3600.0-rakeep[k]* 3600.0
+            ddec=deckeep[j]* 3600.0-deckeep[k]* 3600.0
+
[…]

### 2014-12-02 SERPS_SED.py

@@ -1,0 +1,441 @@
+"""
+This code takes the gaussian fitted data and derives the Spectral Index of the sources with fits
+Also does other stuffs...
+
+December, 2014
+nkern@umich.edu
+"""
+
+### Import Modules ###
+print '...importing modules'
+import numpy as np
+import matplotlib.pyplot as mp
+import scipy.stats as stats
+import numpy.ma as ma
+from mpl_toolkits.axes_grid1 import AxesGrid
+
+print '...done importing'
+
+### Flags, Constants ###
+lower_freq	= 4750.00		# MHz
+upper_freq	= 7250.00		# MHz
+lower_passband	= [4238.00,5262.00]	# MHz
+upper_passband	= [6738.00,7762.00]	# MHz
+Source_Num	= 18
+Image_Num	= 2
+c		= 2.9979e8		# m/s
+
+### Program ###
+
+
+###############################################################################
+########################### Load Data #########################################
+###############################################################################
+
+print '...loading Gutermuth Cross Match Data'
+## Load Gutermuth Cross Match data
+RA_VLA,Dec_VLA,jmag,hmag,kmag,i1mag,i2mag,i3mag,i4mag,m24mag,p70mag = np.loadtxt('vla_serps_merger_gutermuth_try1.csv',delimiter=',',unpack=True)
+# -100 are nulls
+# jhk mags are 2mass near infrared 
+# i1,i2,i3,i4 are IRAC on Spitzer
+# m24 is MIPS 24 micron on Spitzer 
+# p70 is PACS 70 micron on Herschel
+
+# Write ds9 region file for RA and DEC coordinates
+#output = open('Gutermuth_CrossMatch.reg','w')
+#output.write('# Region file format: DS9 version 4.1\n')
+#output.write('global color=magenta dashlist=8 3 width=1 font="helvetica 10 normal roman" select=1 highlite=1 dash=0 fixed=0 edit=1 move=1 delete=1 include=1 source=1\n')
+#output.write('fk5\n')
+#for i in range(len(RA_VLA)):
+#	output.write('point('+str(RA_VLA[i])+','+str(Dec_VLA[i])+') # point=x text={'+str(i+1)+'}\n')
+
+#output.close()
+
[…]

### 2014-12-02 git_add.sh

@@ -1,0 +1,75 @@
+git add IRAM_sources.txt
+git add Lower_Peak_Fluxes.csv
+git add Lower_Peak_Fluxes_try2.csv
+git add MSX_Catalogue.tsv
+git add Make_Figs.py
+git add NVSS_Catalogue.tsv
+git add Observers_Log.pdf
+git add RMS_Catalogue.tsv
+git add Rodriguez10_IR_Sources.fit
+git add Rodriguez10_IR_Sources.reg
+git add Rodriguez10_VLA_Sources.fit
+git add Rodriguez10_VLA_Sources.reg
+git add Rodriguez10_VLA_Sources_ICRS.reg
+git add SERPS_SED.py
+git add SS_Final_Sources.crtf
+git add SS_Final_Sources.reg
+git add SS_Final_Sources.txt
+git add SS_Final_Sources_deg.reg
+git add SS_Final_Sources_lowerbriggs05pxl.reg
+git add SS_Final_Sources_upperbriggs05pxl.reg
+git add SS_Labels.txt
+git add SS_Targets.reg
+git add SS_Targets_ICRS.reg
+git add SS_Targets_ICRS.txt
+git add SS_Targets_pxl.reg
+git add SerpSouthGutermuth.reg
+git add Shirley07Data/
+git add Upper_Peak_Fluxes.csv
+git add Upper_Peak_Fluxes_try2.csv
+git add fluxscale_output.txt
+git add git_add.sh
+git add gutermuth2008_serps_ysos1.crtf
+git add gutermuth2008_serps_ysos1.reg
+git add gutermuth2008_serps_ysos1.txt
+git add notes_serpsouth_reduction.txt
+git add serps_yso1.reg
+git add vla_serps_merger_gutermuth_try1.csv
+
+git add AAS_2015/225th_AAS_Abstract.rtf
+
+git add Data/reduction_notes.txt
+
+git add Gauss_Fitting/Final_Fit_Results.txt
+git add Gauss_Fitting/Final_Fit_Results_old.txt
+git add Gauss_Fitting/Final_Fit_Results_try2.txt
+git add Gauss_Fitting/Fit_Latex_Table.tex
+git add Gauss_Fitting/Flux_Table.py
+git add Gauss_Fitting/Make_Estimates.py
+git add Gauss_Fitting/SERPS_Gauss_Fit.py
+git add Gauss_Fitting/Table.py
+git add Gauss_Fitting/apj.bst
[…]

### 2014-12-02 git_add.sh
modified:   git_add.sh

@@ -55,6 +55,7 @@ git add Gauss_Fitting/sigfig.py
 git add Gauss_Fitting/Fit_Files/*.txt
 
 git add Paper/paper.tex
+git add Paper/paper.pdf
 git add Paper/references.bib
 git add Paper/apj.bst
 git add Paper/figures/SerpSouth_FOV-eps-converted-to.pdf

### 2014-12-12 Paper/paper.tex
modified:   IRAM_sources.txt 	modified:   Make_Figs.py 	new file:   Paper/deluxetable.sty 	new file:   Paper/emulateapj.cls 	modified:   Paper/figures/SerpSouth_fov_contour-eps-converted-to.pdf 	modified:   Paper/figures/SerpSouth_zoom_color_contour-eps-converted-to.pdf 	modified:   Paper/figures/SerpSouth_zoom_contour-eps-converted-to.pdf 	new file:   Paper/mn2e.cls 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib 	modified:   Rodriguez10_VLA_Sources.reg 	modified:   SERPS_SED.py 	modified:   git_add.sh

@@
 %\usepackage{stfloats}		% For Figures on bottom of page
+\usepackage{rotating}		% Rotated figures
 
@@
 %\submitted{Submitted: \today}
-\title{Radio Properties of Protostars in the Serpens South Protocluster}
+\title{Radio Sources in the Serpens South Protocluster}
 \author{Authors}
@@
 
-	Serpens South is a young stellar cluster that is apart of the broader Aquila Rift extinction feature.
+	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature.
 It lies south of the Serpens Main cloud, and is just West of the bright W40 HII region.
@@
 X-ray studies of Serpens South have yet to be published.
-To-date, only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al.
-in prep), meaning that there has yet to be a radio study of Serpens South since the VLA upgraded its facilities 2012.
+Presently only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al.
+in prep).
 Beyond this study, further radio studies of Serpens South will be important in understanding the star formation process across the electromagnetic spectrum.
 
-	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.][]{Curiel89, Anglada98, Reipurth99, Eiroa05, Shirley07, Rodriguez10}.
+	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}.
 Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star.
@@
 Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation.
+\autoref{fig:serpsouth_fov} shows Serpens South at 350 micron and outlines our field of view.
+
+\begin{figure}[h!]
+\label{fig:serpsouth_fov}
+\centering
+\includegraphics[keepaspectratio=True,scale=.55]{figures/SerpSouth_FOV.eps}
+\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South.
+Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively.
+The green box indicates our region of interest with the EVLA.}}
+\end{figure}
 
@@
 
+%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
+\capstartfalse
+\begin{deluxetable*}{lcccccccc}
+\label{tab:flux_table}
+\tabletypesize{\footnotesize}
+\tablecaption{Radio Properties of VLA Sources}
+\tablehead{
+	\multicolumn{1}{c}{Source}								&
+	\multicolumn{1}{c}{RA$^{a}$}								&
+	\multicolumn{1}{c}{Decl.$^{a}$}							&
+	\multicolumn{1}{c}{$S^{\text{int}}_{6.3 \text{cm}}\ ^{b}$}			&
+	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}				&
+	\multicolumn{1}{c}{$S^{\text{int}}_{4.1 \text{cm}}$}				&
+	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}				&
+	\multicolumn{1}{c}{$\alpha^{\text{int}}_{\text{radio}}$}				&
+	\multicolumn{1}{c}{$\alpha^{\text{peak}}_{\text{radio}}$}				\\ [.25ex]		
+%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
+%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
+%	\multicolumn{1}{c}{Match?}						&
+%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
+	\colhead{}										&
+	\colhead{(J2000)}								&
+	\colhead{(J2000)}								&
+	\colhead{($\mu$Jy)}								&
+	\colhead{($\mu$Jy beam$^{-1}$)}					&
+	\colhead{($\mu$Jy)}								&
+	\colhead{($\mu$Jy beam$^{-1}$)}					&
+	\colhead{}										&
+	\colhead{}										
+%	\colhead{(L$_{\text{sun}}$)}						&
+%	\colhead{(L$_{\text{sun}}$)}						&
+%	\colhead{(MM/Hersc/Spitz)}						&
+%	\colhead{Stage}								
+	}
+\startdata
+
+VLA\_1	&	18:30:09.68	&	-02:00:32.8	&	844 $\pm$ 8	&	794	&	749 $\pm$ 6	&	718	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02\\[1ex]
+
+VLA\_2	&	18:30:04.79	&	-02:00:34.1	&	87 $\pm$ 7	&	72	&	177 $\pm$ 7	&	138	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14\\[1ex]
+
+VLA\_3	&	18:30:02.55	&	-02:00:48.5	&	116 $\pm$ 10	&	87	&	140 $\pm$ 2	&	99	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15\\[1ex]
+
+VLA\_4	&	18:30:01.53	&	-02:00:51.6	&	946 $\pm$ 28	&	515	&	1663 $\pm$ 32	&	1178	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02\\[1ex]
+
+VLA\_5	&	18:30:14.79	&	-02:01:27.3	&	167 $\pm$ 10	&	173	&	106 $\pm$ 5	&	95	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13\\[1ex]
+
+VLA\_6	&	18:30:06.62	&	-02:01:28.9	&	33 $\pm$ 4	&	56	&	79 $\pm$ 7	&	61	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23\\[1ex]
+
+VLA\_7	&	18:30:05.81	&	-02:01:44.9	&	84 $\pm$ 7	&	63	&	48 $\pm$ 4	&	40	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31\\[1ex]
+
+VLA\_8	&	18:30:06.89	&	-02:02:11.5	&	50 $\pm$ 6	&	50	&	39 $\pm$ 3	&	46	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29\\[1ex]
+
+VLA\_9	&	18:30:02.80	&	-02:02:25.3	&	60 $\pm$ 1	&	44	&	66 $\pm$ 1	&	50	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29\\[1ex]
+
+VLA\_10	&	18:30:02.95	&	-02:02:32.2	&	260 $\pm$ 17	&	73	&	287 $\pm$ 6	&	119	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15\\[1ex]
+
+VLA\_11	&	18:30:03.36	&	-02:02:45.8	&	73 $\pm$ 4	&	58	&	38 $\pm$ 2	&	36	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34\\[1ex]
+
+VLA\_12	&	18:30:04.11	&	-02:03:02.1	&	79 $\pm$ 2	&	58	&	30 $\pm$ 2	&	24	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48\\[1ex]
+
+VLA\_13	&	18:30:03.54	&	-02:03:08.4	&	231 $\pm$ 3	&	227	&	186 $\pm$ 1	&	178	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07\\[1ex]
+
+VLA\_14	&	18:30:03.84	&	-02:03:12.2	&	83 $\pm$ 2	&	61	&	31 $\pm$ 0	&	37	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33\\[1ex]
+
+VLA\_15	&	18:30:04.60	&	-02:03:14.1	&	49 $\pm$ 4	&	51	&	68 $\pm$ 1	&	52	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27\\[1ex]
+
+VLA\_16	&	18:30:03.25	&	-02:03:26.6	&	55 $\pm$ 1	&	65	&	63 $\pm$ 2	&	58	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23\\[1ex]
+
+VLA\_17	&	18:30:01.32	&	-02:03:42.9	&	161 $\pm$ 4	&	167	&	146 $\pm$ 3	&	135	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1\\[1ex]
+
+VLA\_18	&	18:30:09.40	&	-02:04:08.8	&	167 $\pm$ 10	&	134	&	170 $\pm$ 3	&	182	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09
+
+\enddata
+\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
+\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
+\tablenotetext{c}{Spectral index of integrated flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
+\tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
+\tablenotetext{e}{}
+
+\end{deluxetable*}
+\capstarttrue
+%%%%%%%%%%% End Table %%%%%%%%%%%%%%%
+
 \subsection{Radio Source Selection}
+\label{sec:radio source selection}
+
 In choosing our sources, we restrict ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength.
-We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing our Sextractor source extracted sample \citep{Bertin96}.
+We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}.
 We were left with a total of 18 radio sources.
-We then ran source extractions on these spatial positions over near and far infrared data from the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
+We then ran source extractions on these spatial positions over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
 We used a 2 arcsecond maximum matching tolerance for these extractions.
-Apertures and adopted corrections are consistent with the HOPS survey \{What source should I cite?\}
+Apertures and adopted corrections are consistent with the HOPS survey.
+
+\begin{figure}[h!]
+\label{fig:serpsouth_fov_contour}
+\centering
+\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
+\caption{\small{Serpens South radio continuum at 6.3 cm, focused in on green box from \autoref{fig:serpsouth_fov}.
+Radio contours start at 4$\sigma$ and end at 50$\sigma$.
+The loose black contour is the same SPIRE 350 $\mu$m contour found in \autoref{fig:serpsouth_fov}.
+}}
+\end{figure}
+
+\begin{figure*}
+\epsscale{1.15}
+\plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
+\caption{{\bfseries Left}: Radio continuum of central filament at 6.3 cm, focused in on red box from \autoref{fig:serpsouth_fov_contour}.
+Blue and red crosses correspond to Class I and II protostars identified by Spitzer \citep{Gutermuth08}.
+Green crosses correspond to 1.2 mm dust peaks identified by IRAM \citep{Maury11}.
+{\bfseries Right}: Identical image as figure on the left, but the background color is PACS 70 $\mu$m image.}
+\end{figure*}
 
@@
 A total of ten out of our 18 sources have signs that indicate they are protostellar in nature.
-One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as Class 0 and starless.
+One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as starless.
 Here, we confirm compact radio emission with a rising spectral index indicative of mixed optically thin and thick free-free emission, which suggests the presence of a compact core.
@@
 
-\
+%\subsection{Spectral Indices}
+%\label{sec:spix}
+%A spectral index is the slope of the flux density in log space between two wavelengths. At radio wavelengths, the spectral index is defined as
+%
+%\begin{equation}
+%\label{eq:radio_spix}
+%\alpha_{\text{radio}} = \frac{\ln({S_{\lambda_{1}}/S_{\lambda_{2}})}}{\ln({\lambda_{2}/\lambda_{1}})}
+%\end{equation}
+%where $\lambda_{2} > \lambda_{1}$ \citep{Shirley07}.
+Note that we have defined $S_{\lambda}$ in terms of a flux density (e.g.
+Jansky) not a flux (e.g.
+$\lambda S_{\lambda}$ or $\nu S_{\nu}$).
+Theoretical studies have shown that
+%
 
-%Centered on Serpens South ($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0), we collected data in the VLA C band, using two spectral windows centered at 6.311 cm and 4.135 cm, each with a bandpass width of 1,024 MHz, with two polarization pairs.
-Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour long observation time.
-Flux density and bandpass calibrations were done using observations of quasar 3C 286.
-We obtained a total of 45 minutes of integration on source.
-%
-%The data were manually inspected for radio frequency interference (RFI), and we removed obvious RFI from our visibilities.
-The data were then reduced using standard reduction techniques in CASA 4.1.0.
-Artifacts and streaks in our final images are products of incomplete $u-v$ coverage of our point spread function, which was slightly enhanced because we did not receive data from 2 of the 27 antennas in the array during our observation, in addition to the bright HII region to the east of Serpens South, contributing extended source signal to our short baselines.
-%
-%The Stokes \emph{I} image was deconvolved multiple times with the CLEAN task \citep{Hogbom74, Clark80}, using natural, robust and uniform weighting, utilizing the Cotton-Schwab algorithm \citep{Schwab84}.
-We find that the best compromise between noise level and source resolution is achieved with robust weighting \citep{Briggs95}.
-The deconvolutions that produced the highest signal to noise ratios involved using masks around our protostellar sources.
-We cleaned our 6.3 and 4.1 cm maps down to a RMS noise level of 18$\mu$Jy and 8$\mu$Jy respectively.
-Table 1 outlines these observations.
-%
-%We used a circular CLEANing mask centered on the image phase center with a radial extent of $\sim$3 arcseconds, corresponding to 80\% of primary beam strength at the center.
-Our short integration time, $\sim$45 minutes, left us with a less than desirable point source function, and we therefore set `psfmode' to `hogbom' in the CLEANing process.
-%
-%Two particularly strong radio sources in the northern part of our field of view created psf artifacts that were visible in our dirty maps.
-In addition to this, and the fact that our protostellar sources are relatively weak, we could not readily distinguish between weak protostar emission and a weak compact artifact.
-Therefore, instead of masking around individual sources, we used a circular mask around 80\% of primary beam strength during the CLEANing process.
-We compared the final CLEANed image with our psf to check for remaining psf artifacts, and used Spitzer 3.6 $\mu$m maps to spatially confirm centimeter emission from known Spitzer protostars.
-For the case where compact emission of seemingly protostellar nature does not spatially match a Spitzer protostar, nor an obvious psf artifact, we use its measured radio spectral index and the calculated random probability that it is a background source to discern whether it is a newly detected protostar.
+\subsection{Radio Source Properties}
+\label{sec:radio source properties}
 
-%We used the Jansky Very Large Array (VLA) to image radio continuum emission coming from the Serpens South cluster, taken on July 2nd, 2013.
-We focused on RA xxxxx DEC xxxxxx, and were sensitive to an area of xxx square degrees.
-The array was in the C configuration during the observation, which is the second smallest configuration with a maximum baseline length of 3.4 km.
-We imaged the cluster in the C band, which spans 4238.0 MHz -- 7762.0 MHz.
-We broke this bandwidth up into two subbands, the first ranging from 4238.00 MHz -- 5262.00 MHz with the middle at $\lambda=6.311$ cm, and the second ranging from 6738.00 MHz -- 7762.00 MHz with the middle at $\lambda=4.135$ cm.
+\newcommand{\sourcenote}[1]{\textit{#1 ---}}
 
-\begin{figure}[h!]
-\label{fig:serpsouth_fov}
-\centering
-\includegraphics[keepaspectratio=True,scale=.6]{figures/SerpSouth_FOV.eps}
-\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South.
-Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively.
-The green box indicates our region of interest with the EVLA.}}
-\end{figure}
+\sourcenote{VLA 1 - 5}
+VLA 1 is relatively isolated from the cluster, has very strong radio emission and has no known protostellar matches in the infrared.
+These alone would suggest an extragalactic classification, however, it has a slightly rising radio spectral index of 0.28 indicative of optically thin free-free emission.
+While galaxies are capable of producing  free-free emission from large HII regions, non-thermal synchrotron emission with a steep negative spectral index generally dominates a galaxies' radio emission output.
+However, because VLA 1 does not spatially match any near or far infrared emission structures, we conclude it is extragalactic in nature.
 
-\begin{figure}[h!]
-\label{fig:serpsouth_fov_contour}
-\centering
-\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
-\caption{\small{ 
-}}
-\end{figure}
+Sources 2 through 4 seem to be extragalactic. They have no infrared or far-infrared matches and have steep negative radio spectral indices that suggests their emission is non-thermal synchrotron.
 
-\begin{figure}[h!]
-\label{fig:serpsouth_zoom_contour}
-\centering
-\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_zoom_contour.eps}
-\caption{\small{ 
-}}
-\end{figure}
-
-\begin{figure}[h!]
-\label{fig:serpsouth_zoom_color_contour}
-\centering
-\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_zoom_color_contour.eps}
-\caption{\small{ 
-}}
-\end{figure}
-
-%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
-\capstartfalse
-\begin{deluxetable*}{lccccccc}%cccc}
-\label{tab:radio_properties_table}
-\tabletypesize{\footnotesize}
-\tablecaption{Radio Properties of VLA Sources}
-\tablehead{
-	\multicolumn{1}{c}{Source}								&
-	\multicolumn{2}{c}{Position$^{a}$}							&
-	\multicolumn{1}{c}{$S_{6.3 \text{cm}}\ ^{b}$}				&
-	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}		&
-	\multicolumn{1}{c}{$S_{4.1 \text{cm}}$}					&
-	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}		&
-	\multicolumn{1}{c}{$\alpha_{\text{radio}}\ ^{c}$}				\\ [.25ex]		
-%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
-%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
-%	\multicolumn{1}{c}{Match?}						&
-%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
-	\cline{2-3}										\\ [-1.5ex]
-	\colhead{}										&
-	\colhead{RA}									&
-	\colhead{Dec.}									&
-	\colhead{($\mu$Jy)}								&
-	\colhead{($\mu$Jy beam$^{-1}$)}					&
-	\colhead{($\mu$Jy)}								&
-	\colhead{($\mu$Jy beam$^{-1}$)}					&
-	\colhead{}										
-%	\colhead{(L$_{\text{sun}}$)}						&
-%	\colhead{(L$_{\text{sun}}$)}						&
-%	\colhead{(MM/Hersc/Spitz)}						&
-%	\colhead{Stage}								
-	}
-\startdata
-
-6.31\dotfill		&	1.024	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]
-
-4.14\dotfill		&	1.024	&	3.2 x 2.5	&	12.7	&	8.5
-
-\enddata
-\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
-\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
-\tablenotetext{c}{Spectral index of peak flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
-
-\end{deluxetable*}
-\capstarttrue
-%%%%%%%%%%% End Table %%%%%%%%%%%%%%%
-
-\subsection{VLA 1, 2, 3 and 4}
-\label{subsec:vla1_2_3_4}
-
-\subsection{VLA 6, 7 and 8}
-\label{subsec:vla6_7_8}
-
-\subsection{VLA 9 to 17}
-\label{subsec:vla9_to_17}
-
-\subsection{VLA 5 and 18}
-\label{subsec:vla18}
+VLA 5 is isolated from the cluster and has no infrared or far-infrared matches, but has a strongly rising radio spectral index of 1.41 suggesting that it comes from optically thick free-free emission.
+Similar to VLA 1, we conclude that it is extragalactic.
 
@@
 \subsection{$L_{\text{infrared}}$ and $L_{\text{bol}}$ Relationship}
+
+The internal luminosity $L_{\text{int}}$ of a protostar is defined as the total luminosity from the protostar and its circumstellar disk if present.
+The bolometric luminosity of a source can then defined as $L_{\text{bol}}$ = $L_{\text{int}}$ + $L_{\text{ext}}$, where the external luminosity comes from the heated protostellar envelope.
+It is estimated that $L_{\text{ext}}$ contributes to $L_{\text{bol}}$ on the order of 0.1 $L_{\odot}$ \citet{Dunham08} developed a scaling law relating an embedded protostar's 70 $\mu$m flux to its internal luminosity $L_{\text{int}}$.
 
@@
 
--- What paper should I quote for infrared source extraction photometry analysis?
+-- What paper should I quote for infrared source extraction photometry analysis?\\
+
+-- Do we have to worry about vibrational dust emission in our 4.1 cm data?\\
 

### 2014-12-12 Make_Figs.py

@@ -18,8 +18,8 @@ from matplotlib.widgets import Slider
 savefig = False
 
 plot1 = False
-plot2 = True
-plot3 = False
+plot2 = False
+plot3 = True
 
 
 def sexig_to_deg(ra,dec):
@@ -224,7 +224,6 @@ if plot2 == True:
 	else: 
 		fig.recenter(277.525,-2.038,width=0.082,height=0.082)
 
-
 	if savefig == True:
 		fig.save('Paper/figures/SerpSouth_zoom_contour.eps',adjust_bbox='tight')
 
@@ -315,7 +314,6 @@ if plot3 == True:
 	else: 
 		fig.recenter(277.525,-2.038,width=0.082,height=0.082)
 
-	savefig=False
 	if savefig == True:
 		fig.save('Paper/figures/SerpSouth_zoom_color_contour.eps',adjust_bbox='tight')
 

### 2014-12-12 SERPS_SED.py

@@ -127,7 +127,7 @@ mag_rel_errs = np.array([0.15]*9)
 zeroflux_rel_errs = np.array([jmag_zero_err,hmag_zero_err,kmag_zero_err,i1mag_zero_err,i2mag_zero_err,i3mag_zero_err,i4mag_zero_err,m24mag_zero_err,p70mag_zero_err])/np.array([jmag_zero,hmag_zero,kmag_zero,i1mag_zero,i2mag_zero,i3mag_zero,i4mag_zero,m24mag_zero,p70mag_zero])
 
 # Total Error On Flux (Relative) add in quadrature
-infra_rel_errs = np.sqrt( mag_rel_errs**2 + zeroflux_rel_errs**2)
+guter_rel_errs = np.sqrt( mag_rel_errs**2 + zeroflux_rel_errs**2)
 
 
 ########################################################################################
@@ -243,8 +243,8 @@ ir_fitted = np.array([6,10,12,15,16])
 # infrared pointings
 for i in range(source_num):
 	if (i in ir_fitted) == True:
-		ir_spix.append( infr_spix(guter_fluxes[i][7],guter_fluxes[i][6],ir_upper_lam,ir_lower_lam,infra_rel_errs[7],infra_rel_errs[6])[0] )
-		ir_spix_err.append( infr_spix(guter_fluxes[i][7],guter_fluxes[i][6],ir_upper_lam,ir_lower_lam,infra_rel_errs[7],infra_rel_errs[6])[1] )
+		ir_spix.append( infr_spix(guter_fluxes[i][7],guter_fluxes[i][6],ir_upper_lam,ir_lower_lam,guter_rel_errs[7],guter_rel_errs[6])[0] )
+		ir_spix_err.append( infr_spix(guter_fluxes[i][7],guter_fluxes[i][6],ir_upper_lam,ir_lower_lam,guter_rel_errs[7],guter_rel_errs[6])[1] )
 	else:
 		ir_spix.append(np.nan)
 		ir_spix_err.append(np.nan)	
@@ -266,6 +266,29 @@ def cross_match(array1,array2):
 		else: array1_temp.append(array1[array2[i]])
 	return np.array(array1_temp)
 
+def sigfigs(array,cut_str):
+	''' iterates a float manipulation command
+	try using "'%.3f'" as cut_str '''
[…]

### 2014-12-12 git_add.sh

@@ -58,6 +58,9 @@ git add Paper/paper.tex
 git add Paper/paper.pdf
 git add Paper/references.bib
 git add Paper/apj.bst
+git add Paper/emulateapj.cls
+git add Paper/deluxetable.sty
+git add Paper/mn2e.cls
 git add Paper/figures/SerpSouth_FOV-eps-converted-to.pdf
 git add Paper/figures/SerpSouth_fov_contour-eps-converted-to.pdf
 git add Paper/figures/SerpSouth_zoom_color_contour-eps-converted-to.pdf

### 2014-12-17 Paper/paper.tex
new file:   IRAM_sources.reg 	modified:   Make_Figs.py 	modified:   Paper/figures/SerpSouth_zoom_color_contour-eps-converted-to.pdf 	modified:   Paper/figures/SerpSouth_zoom_contour-eps-converted-to.pdf 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib 	new file:   Radio_Correlations.py 	modified:   SERPS_SED.py 	modified:   git_add.sh

@@
 %\submitted{Submitted: \today}
-\title{Radio Sources in the Serpens South Protocluster}
+\title{Radio Sources in the Central Filament of the Serpens South Protocluster}
 \author{Authors}
@@
 	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature.
-It lies south of the Serpens Main cloud, and is just West of the bright W40 HII region.
-Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars, suggesting it is in a very early phase of cluster formation.
+It lies south of the Serpens Main cloud and is just West of the bright W40 HII region.
+Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation.
 Since its discovery, it has become the center of a wide range of scholarship.
@@
 in prep).
-Beyond this study, further radio studies of Serpens South will be important in understanding the star formation process across the electromagnetic spectrum.
+
+	Because of its isolated formation, Serpens South presents a unique opportunity to study the environmental influences on protostars in a young stellar cluster.
+A multi-wavelength approach will be key to fully understanding to non-normative behaviors of protostars in a high-density environment such as Serpens South.
 
@@
 Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star.
-Theory and observations have best explained protostellar radio emission as having two components: thermal and non-thermal.
+Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal.
 Thermal radio emission is generally assumed to be free-free emission created from an HII region.
@@
 
-%	  Centimeter continuum emission is largely associated with free-free emission created from ionized regions within the dense envelope surrounding the star \citep{Anglada95}.
-High-mass protostars are strong enough to create this region from stellar winds, while low-mass protostars likely create these regions from compact, collimated thermal outflows, however photoionization and stellar winds from low-mass protostars may also help sustain HII regions around the protostar \citep{Scaife12}.
-Because radio observations probe deep into the stellar envelope, centimeter observations of this nature have been a proven tool in the detection of outflow sources \citep{Rodriguez97} and in the exploration of the physical dynamics of the youngest protostellar objects \citep{Anglada98,Shirley07}.
-In this respect, centimeter observations of protostars are a crucial asset in our understanding of regions of active star formation.
+	Towards the two goals of 1) locating new embedded protostars in the Serpens South protocluster and 2) better understanding the mechanisms of protostellar radio emission on a global scale, we carried out EVLA observations of Serpens South's central filament at 4.1 and 6.3 centimeters.
+In $\S 2$ we present our observations.
+In $\S 3$ we present our results.
+In $\S 4$ we discuss the implications of our study and in $\S 5$ we summarize our results.
 
@@
 The distances to Serpens South, W40 and the Serpens Main cloud are not agreed upon in the literature.
-When Serpens South was discovered in 2008, a distance of 260 pc $\pm$ 37 pc was adopted based on evidence that its LSR velocities matched LSR velocities of the Serpens Main cloud, which was then thought to be a part of the larger Aquila Rift extinction feature whose distance was estimated at 260 pc by \citet{Straizys03}.
-However, VLBA parallax measurements done in 2010 have established the distance to the Serpens Main cloud as 429 $\pm$ 2 pc \citep{Dzib11}, meaning that Serpens Main is distinct from the the Aquila Rift if the latter is to have a distance of 260 pc.
+When Serpens South was discovered in 2008, a distance of 260 pc $\pm$ 37 pc was adopted based on evidence that its LSR velocities matched LSR velocities of the Serpens Main cloud, which was then thought to be a part of the larger Aquila Rift extinction feature estimated to lie at 260 pc \citep{Straizys03}.
+However, VLBA parallax measurements conducted in 2010 have established the distance to the Serpens Main cloud as 429 $\pm$ 2 pc \citep{Dzib11}, meaning that Serpens Main is distinct from the the Aquila Rift if Aquila is to have a distance of 260 pc.
 
 \citet{Gutermuth08} also argued that Serpens South lies in front of W40, claiming that it is seen in absorption against emission from W40.
-Therefore, we know Serpens Main is at 429 pc, and we know that Serpens South lies in front of W40.
-What we don't know are the absolute distances to both W40 or Serpens South.
 If we are to follow the initial LSR velocity analysis by \citet{Gutermuth08}, we would equate Serpens South to Serpens Main and say Serpens South lies at approximately 429 pc, while W40 lies further away.
@@
 \enddata
-\tablenotetext{a}{Images deconvolved with robust (Briggs) weighting, \emph{robust}=0.5 \citep{Briggs95}.}
+\tablenotetext{a}{Deconvolved with robust weighting, \emph{robust}=0.5 \citep{Briggs95}.}
 \label{tab:image_pars}
@@
 \capstartfalse
-\begin{deluxetable*}{lcccccccc}
+\begin{deluxetable*}{lccccccccc}
 \label{tab:flux_table}
@@
 	\multicolumn{1}{c}{$\alpha^{\text{int}}_{\text{radio}}$}			&
-	\multicolumn{1}{c}{$\alpha^{\text{peak}}_{\text{radio}}$}				\\ [.25ex]		
+	\multicolumn{1}{c}{$\alpha^{\text{peak}}_{\text{radio}}$}			&	
+	\multicolumn{1}{c}{Class$^{e}$}							\\ [.25ex]	
 %	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
@@
 	\colhead{}										&
+	\colhead{}										&
 	\colhead{}	
@@
 
-VLA\_1	&	18:30:09.68	&	-02:00:32.8	&	844 $\pm$ 8	&	794	&	749 $\pm$ 6	&	718	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02\\[1ex]
+VLA\_1	&	18 30 09.68	&	-02 00 32.8	&	749 $\pm$ 6	&	718	&	844 $\pm$ 8	&	794	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02	&	Extragal.?\\[1ex]
 
-VLA\_2	&	18:30:04.79	&	-02:00:34.1	&	87 $\pm$ 7	&	72	&	177 $\pm$ 7	&	138	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14\\[1ex]
+VLA\_2	&	18 30 04.79	&	-02 00 34.1	&	177 $\pm$ 7	&	138	&	87 $\pm$ 7	&	72	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14	&	Extragal.\\[1ex]
 
-VLA\_3	&	18:30:02.55	&	-02:00:48.5	&	116 $\pm$ 10	&	87	&	140 $\pm$ 2	&	99	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15\\[1ex]
+VLA\_3	&	18 30 02.55	&	-02 00 48.5	&	140 $\pm$ 2	&	99	&	116 $\pm$ 10	&	87	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15	&	Extragal.\\[1ex]
 
-VLA\_4	&	18:30:01.53	&	-02:00:51.6	&	946 $\pm$ 28	&	515	&	1663 $\pm$ 32	&	1178	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02\\[1ex]
+VLA\_4	&	18 30 01.53	&	-02 00 51.6	&	1663 $\pm$ 32	&	1178	&	946 $\pm$ 28	&	515	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02	&	Extragal.\\[1ex]
 
-VLA\_5	&	18:30:14.79	&	-02:01:27.3	&	167 $\pm$ 10	&	173	&	106 $\pm$ 5	&	95	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13\\[1ex]
+VLA\_5	&	18 30 14.79	&	-02 01 27.3	&	106 $\pm$ 5	&	95	&	167 $\pm$ 10	&	173	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13	&	Extragal.?\\[1ex]
 
-VLA\_6	&	18:30:06.62	&	-02:01:28.9	&	33 $\pm$ 4	&	56	&	79 $\pm$ 7	&	61	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23\\[1ex]
+VLA\_6	&	18 30 06.62	&	-02 01 28.9	&	79 $\pm$ 7	&	61	&	33 $\pm$ 4	&	56	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23	&	Extragal.\\[1ex]
 
-VLA\_7	&	18:30:05.81	&	-02:01:44.9	&	84 $\pm$ 7	&	63	&	48 $\pm$ 4	&	40	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31\\[1ex]
+VLA\_7	&	18 30 05.81	&	-02 01 44.9	&	48 $\pm$ 4	&	40	&	84 $\pm$ 7	&	63	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31	&	Class I\\[1ex]
 
-VLA\_8	&	18:30:06.89	&	-02:02:11.5	&	50 $\pm$ 6	&	50	&	39 $\pm$ 3	&	46	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29\\[1ex]
+VLA\_8	&	18 30 06.89	&	-02 02 11.5	&	39 $\pm$ 3	&	46	&	50 $\pm$ 6	&	50	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29	&	Extragal.?\\[1ex]
 
-VLA\_9	&	18:30:02.80	&	-02:02:25.3	&	60 $\pm$ 1	&	44	&	66 $\pm$ 1	&	50	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29\\[1ex]
+VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 1	&	50	&	60 $\pm$ 1	&	44	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29	&	Class 0?\\[1ex]
 
-VLA\_10	&	18:30:02.95	&	-02:02:32.2	&	260 $\pm$ 17	&	73	&	287 $\pm$ 6	&	119	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15\\[1ex]
+VLA\_10	&	18 30 02.95	&	-02 02 32.2	&	287 $\pm$ 6	&	119	&	260 $\pm$ 17	&	73	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15	&	Unknown\\[1ex]
 
-VLA\_11	&	18:30:03.36	&	-02:02:45.8	&	73 $\pm$ 4	&	58	&	38 $\pm$ 2	&	36	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34\\[1ex]
+VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 2	&	36	&	73 $\pm$ 4	&	58	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]
 
-VLA\_12	&	18:30:04.11	&	-02:03:02.1	&	79 $\pm$ 2	&	58	&	30 $\pm$ 2	&	24	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48\\[1ex]
+VLA\_12	&	18 30 04.11	&	-02 03 02.1	&	30 $\pm$ 2	&	24	&	79 $\pm$ 2	&	58	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48	&	Class 0$^{*}$\\[1ex]
 
-VLA\_13	&	18:30:03.54	&	-02:03:08.4	&	231 $\pm$ 3	&	227	&	186 $\pm$ 1	&	178	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07\\[1ex]
+VLA\_13	&	18 30 03.54	&	-02 03 08.4	&	186 $\pm$ 1	&	178	&	231 $\pm$ 3	&	227	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07	&	Class 0$^{*}$\\[1ex]
 
-VLA\_14	&	18:30:03.84	&	-02:03:12.2	&	83 $\pm$ 2	&	61	&	31 $\pm$ 0	&	37	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33\\[1ex]
+VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 0	&	37	&	83 $\pm$ 2	&	61	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]
 
-VLA\_15	&	18:30:04.60	&	-02:03:14.1	&	49 $\pm$ 4	&	51	&	68 $\pm$ 1	&	52	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27\\[1ex]
+VLA\_15	&	18 30 04.60	&	-02 03 14.1	&	68 $\pm$ 1	&	52	&	49 $\pm$ 4	&	51	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27	&	Extragal.\\[1ex]
 
-VLA\_16	&	18:30:03.25	&	-02:03:26.6	&	55 $\pm$ 1	&	65	&	63 $\pm$ 2	&	58	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23\\[1ex]
+VLA\_16	&	18 30 03.25	&	-02 03 26.6	&	63 $\pm$ 2	&	58	&	55 $\pm$ 1	&	65	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23	&	Class II\\[1ex]
 
-VLA\_17	&	18:30:01.32	&	-02:03:42.9	&	161 $\pm$ 4	&	167	&	146 $\pm$ 3	&	135	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1\\[1ex]
+VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 3	&	135	&	161 $\pm$ 4	&	167	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1	&	Class I\\[1ex]
 
-VLA\_18	&	18:30:09.40	&	-02:04:08.8	&	167 $\pm$ 10	&	134	&	170 $\pm$ 3	&	182	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09
+VLA\_18	&	18 30 09.40	&	-02 04 08.8	&	170 $\pm$ 3	&	182	&	167 $\pm$ 10	&	134	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09	&	Extragal.?
 
@@
 \tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
-\tablenotetext{e}{}
+\tablenotetext{e}{Classification of source.
+Unless otherwise noted, Class 0 classifications come from Herschel \citep{Bontemps10} and Class I \& II  from Spitzer \citep{Gutermuth08}.
+(?) denotes uncertaintity.
+($^{*}$) denotes classified by this work.}
 
@@
 
-In choosing our sources, we restrict ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength.
-We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}.
-We were left with a total of 18 radio sources.
-We then ran source extractions on these spatial positions over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
-We used a 2 arcsecond maximum matching tolerance for these extractions.
-Apertures and adopted corrections are consistent with the HOPS survey.
+In choosing our sources, we restricted ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength.
+We chose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}.
+We took only sources that had at least a $4\sigma$ strength in the 4.1 cm image, and were left with a total of 18 radio sources.
+We note that we found $\sim$6 sources at the $2\sigma$ level that aligned within 2 arcsecond of an infrared association, however, we do not consider them strong detections and do not include them in our final source list.
+As stated in \autoref{sec:observations}, further observations with longer integration will likely be able to confidently detect these protostellar radio sources.
 
@@
 \begin{figure*}
+\label{fig:zoom}
 \epsscale{1.15}
+
 \plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
-\caption{{\bfseries Left}: Radio continuum of central filament at 6.3 cm, focused in on red box from \autoref{fig:serpsouth_fov_contour}.
-Blue and red crosses correspond to Class I and II protostars identified by Spitzer \citep{Gutermuth08}.
-Green crosses correspond to 1.2 mm dust peaks identified by IRAM \citep{Maury11}.
-{\bfseries Right}: Identical image as figure on the left, but the background color is PACS 70 $\mu$m image.}
+\caption{{\bfseries Left}: Radio continuum at 6.3 cm focused in on red box from \autoref{fig:serpsouth_fov_contour}.
+Blue and red crosses correspond to Spitzer identified Class I and II protostars.
+Green crosses correspond to 1.2 mm dust peaks identified by IRAM.
+{\bfseries Right}: Identical contours on the left but with a background PACS 70 $\mu$m image.
+The radio contour beam size is shown to the lower-left.}
 \end{figure*}
+
+We ran source extractions on the spatial positions of our final source list over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
+We used a 2 arcsecond maximum matching tolerance for these extractions.
+Apertures and adopted corrections were consistent with the HOPS survey.
 
@@
 A total of ten out of our 18 sources have signs that indicate they are protostellar in nature.
-One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as starless.
-Here, we confirm compact radio emission with a rising spectral index indicative of mixed optically thin and thick free-free emission, which suggests the presence of a compact core.
+One of our radio sources, VLA 12, matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they quote as starless.
 
@@
 Therefore, the total number of sources with flux $S$ greater than 50 $\mu$Jy at 6 cm is 0.229 arcmin$^{-2}$.
-This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact star, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest.
+This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact radio source, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest.
 This agrees with our analysis, as we find roughly 8 sources that are likely background sources.
@@
 
-\subsection{Radio Source Properties}
-\label{sec:radio source properties}
+\subsection{Radio Source Classifications}
+\label{sec:radio source classifications}
 
@@
 
-\sourcenote{VLA 1 - 5}
-VLA 1 is relatively isolated from the cluster, has very strong radio emission and has no known protostellar matches in the infrared.
-These alone would suggest an extragalactic classification, however, it has a slightly rising radio spectral index of 0.28 indicative of optically thin free-free emission.
-While galaxies are capable of producing  free-free emission from large HII regions, non-thermal synchrotron emission with a steep negative spectral index generally dominates a galaxies' radio emission output.
-However, because VLA 1 does not spatially match any near or far infrared emission structures, we conclude it is extragalactic in nature.
+\sourcenote{Extragalactic Sources}
+VLA 2, 3, 4, 6, and 15 are very likely extragalactic in nature.
+They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission.
 
-Sources 2 through 4 seem to be extragalactic. They have no infrared or far-infrared matches and have steep negative radio spectral indices that suggests their emission is non-thermal synchrotron.
+\sourcenote{Unclear Sources}
+While VLA 1 and 5 have no infrared, far-infrared or millimeter associations and are isolated from the filament, they have a flat and rising radio spectral indices suggesting optically thin and thick free-free emission respectively.
+Although galaxies can produce free-free emission from large HII clouds, the dominant component of a galaxy's radio emission output comes from non-thermal synchrotron emission with a declining spectrum.
+Nonetheless, we tentatively classify these sources as extragalactic due to their lack of associations.
 
-VLA 5 is isolated from the cluster and has no infrared or far-infrared matches, but has a strongly rising radio spectral index of 1.41 suggesting that it comes from optically thick free-free emission.
-Similar to VLA 1, we conclude that it is extragalactic.
+VLA 18 is spatially distinct from the filament but has a flat radio spectral index and actually has three very weak infrared associations at 3.6, 4.5 and 5.8 $\mu$m.
+However, we speculate that these associations are coincidental and tentatively classify VLA 18 as extragalactic.
+
+\begin{figure}
+\label{fig:serpsouth_vla10_contour}
+\centering
+\includegraphics[keepaspectratio=True,scale=.3]{figures/SerpSouth_VLA10_contour.eps}
+\caption{\small{Zoom in of the elongated VLA 10 source.
+Blue solid and red dashed contours correspond to 4.1 and 6.3 cm images respectively.
+The lower-left beam is the 4.1 cm beam size.
+Blue crosses represent Spitzer identified Class I sources.
+}}
+\end{figure}
+
+We are unsure as to the nature of VLA 10.
+We treat the whole elongated structure as one source.
+At our higher resolution 4.1 cm image, we can resolve two distinct emission components that are blended at our lower resolution 6.3 cm image (\autoref{fig:serpsouth_vla10_contour}).
+We cannot confidently rely on our gaussian fitted fluxes or spectral index due to the morphology of the source.
+For VLA 10's peak flux, we used the Northern structure in the 4.1 cm map.
+Although our measured peak fluxes are highly uncertain due to confusion at 6.3 cm, VLA 10's peak flux derived spectral index is strongly negative suggesting non-thermal emission and an extragalactic classification.
+However, VLA 10's Southern structure is also within 2 arcseconds of a Spitzer identified Class I source.
+This raises the possibility that the Northern structure is a background source while the Southern structure is a Class I protostellar radio source.
+
+Another possibility is that VLA 10 is representative of an outflow shock emanating from either the Southern VLA 10 structure or from sources VLA 11 or 9.
+An H$_{2}$ study conducted by \citet{Teixeira12}, however, labeled VLA 11 as an outflow source with a jet running from North-East to South-West, almost perpendicular to the direction necessary for it to be an outflow source powering VLA 10's emission.
+Further evidence that would support a non-extragalactic classification of both the South and North structures of VLA 10 is the fact that the cold dust seen at and longward of 70 $\mu$m neatly fits around VLA 10's elongated morphology, as seen in \autoref{fig:zoom}.
+
+\sourcenote{Protostellar Sources}
+The remainder of our 18 sources, VLA 7, 9, 11, 12, 13, 14, 16 and 17 are likely protostellar in nature.
+With the exception of VLA 9, all of these sources have either flat or rising radio spectral indices indicative of optically thin or thick free-free emission.
+We classify VLA 12, 13 and 14 as three newly identified embedded Class 0 protostars, separated form each other by less than 15 arcseconds.
 
@@
 
-The Serpens South embedded cluster occupies a region in projected proximity to the larger Aquila Rift complex, the W40 HII region and the Serpens Main molecular cloud.
-The Aquila Rift, as previously noted, is a local complex of dark molecular clouds extending several degrees, encompassing the Serpens Main molecular cloud, Serpens South and the W40 HII region (see Figure 1), which are the three main regions of star formation in the direction of the Aquila Rift \citep{Eiroa08}.
-
 %% Conclusions
@@
 \appendix
-{\large These are my edit notes for the paper.} \\[.25in]
+
+{\large To Include in Paper:} \\[.1in]
+
+-- Discussion on radio spectral indices and their implications to emission \\
+
+-- Does optically thick radio emission from Spitzer Class I/II source mean anything particularly interesting?
+B/c it is Spitzer identified, does it mean that it comes not from an ultra-compact region but from some other mechanism?
+\\
+
+-- Discussion on VeLLOs in sample. \\
+
+-- L\_int correlations? \\ \\
+
+-- Make radio\_alpha vs. L\_bol or L\_int graph?\\
+
+-- Fit Spitzer end of SED to get more accurate L\_MIR ? \\
+
+{\large Questions:} \\[.1in]
 
@@
 
+-- What can we say about optically thick radio sources that match Spitzer sources? Embedded Class I source? \\
+
+-- Is it even physically possible for VLA 10 to be a radio galaxy outflow source? In other words, is a 10 arcsecond angular extent on the size scale of typical radio galaxy outflows? \\
+
+-- Can we get a table of Herschel protostars from Bontemps et al.
+2010?
+Other papers, Teixeira12, Nakamura14 and more, quote protostellar classifications of individual protostars from Herschel data as if they had access to a Bontemps2010 catalogue.
+Perhaps they just asked the authors and got access to it.
+Ideally, we would want a catalogue of Class 0 protostars identified by Herschel with their flux values from 250 - 500 $\mu$m, the adopted FWHM apertures in the source extraction and Lbol and Menv properties they subsequently derived.\\
+
 %% End Document

### 2014-12-17 Make_Figs.py

@@ -18,8 +18,8 @@ from matplotlib.widgets import Slider
 savefig = False
 
 plot1 = False
-plot2 = False
-plot3 = True
+plot2 = True
+plot3 = False
 
 
 def sexig_to_deg(ra,dec):
@@ -128,6 +128,12 @@ if plot1 == True:
 ### Radio Contours
 if plot2 == True:
 
+	zoom = False
+	vla10 = True
+
+	figname = 'Paper/figures/SerpSouth_VLA10_contour.eps'
+	#figname = 'Paper/figures/SerpSouth_zoom_contour.eps'
+
 	# Choose Image
 	color_im = 'FITS/PACS_100_micron_cropped.fits'
 	contour_im = 'FITS/SERPS_2.upper.briggs05.deeper.fits'
@@ -144,10 +150,17 @@ if plot2 == True:
 	# Initialize Upper Subband Plot
 	fig = aplpy.FITSFigure(color_im, subplot=(1,1,1), figsize=(11,9))
 
-
 	fig.show_colorscale(cmap='CMRmap',stretch='power',exponent=.30,pmin=0,pmax=100.005)
 	fig.hide_colorscale()
 	fig.show_contour('FITS/SERPS_2.upper.briggs05.deeper.fits',alpha=1,cmap='Greys_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
+
+	if vla10 == True:
+		fig.hide_layer('contour_set_1')
+		fig.show_contour('FITS/SERPS_2.upper.briggs05.deeper.fits',alpha=0.8,cmap='Blues_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
+		contour_im = 'FITS/SERPS_2.lower.briggs05.deeper.fits'
+		contour_data = fits.open(contour_im)[0].data
+		rms = np.std(contour_data[~np.isnan(contour_data)])
+		fig.show_contour('FITS/SERPS_2.lower.briggs05.deeper.fits',alpha=0.8,cmap='Reds_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50],linestyles='dashed')
 
 	# Draw Beam
 	beam_dict = {'bmaj':contour_head['bmaj'],'bmin':contour_head['bmin'],'bpa':contour_head['bpa']}
[…]

### 2014-12-17 Radio_Correlations.py

@@ -1,0 +1,183 @@
+## This file loads in Scaling Relationship Data, like L_radio vs. L_bolometric
+## It does Chi Square fitting and makes plots
+
+## Import Modules ##
+import numpy as np
+import matplotlib.pyplot as mp
+import astropy.io.fits as fits
+from scipy.optimize import leastsq
+from AttrDict import AttrDict
+from scipy import stats
+import pickle as pkl
+
+## Flags ##
+
+
+## Constants ##
+dist1 = 0.429	# kpc
+dist2 = 0.260	# kpc
+c = 2.99e8	# m/s
+
+## Load In Data ##
+
+# Load Shirley07 Data
+shirley = AttrDict({})
+shirley.Lbol_36, shirley.flux_36 = np.loadtxt('Shirley07Data/3.6cmcont.dat',unpack=True)
+shirley.Lbol_60, shirley.flux_60 = np.loadtxt('Shirley07Data/6cmcont.dat',unpack=True)
+
+# Load Scaife11a Data
+scaifea = AttrDict({})
+data = np.loadtxt('Scaife11a_Data.tab',dtype='str',delimiter='\t',usecols=(0,1,2,3,4,5,6,7,8,9))
+match = np.where(data.T[4]=='y')[0]
+match = np.delete(match,[1,11,15,27])
+scaifea.classes = data.T[2][match]
+scaifea.flux_18 = np.array(data.T[5][match],float)
+scaifea.Menv = data.T[6][match]
+scaifea.Tbol = data.T[7][match]
+scaifea.Lbol = np.array(data.T[8][match],float)
+scaifea.Fout = data.T[9][match]
+
+data2 = np.loadtxt('Scaife11a_Data2.tab',dtype='str',delimiter='\t',usecols=(0,1,2,3,4,5,6,7))
+change_dist = np.array(['093','106','104','107','105','063','071',
+			'065','064','088','084','060','068','080','090','092','109'])
+dist_fix = np.array(map(lambda x:np.where(data2.T[0]==x)[0][0],change_dist))
+dist_fix = dist_fix[np.argsort(dist_fix)]
+new_dist = np.array(data2.T[5][dist_fix],float)*1e3
+scaifea.dist = 0.25	#kpc
+
+# Load Scaife11b Data
+scaifeb = AttrDict({})
[…]

### 2014-12-17 SERPS_SED.py

@@ -322,8 +322,8 @@ ir_spitz_class = cross_match(spitz_class,spitz_source_id)
 
 
 ### Dunham08 70micron vs. Linternal ###
-L_int_dunham08 = 3.3e8 * guter_fluxes.T[-1]*c/70e-6 * 1e-23	# Lsun
-L_int_dunham08_err = 3.3e8 * guter_fluxes.T[-1]*guter_rel_errs[-1]*c/70e-6 * 1e-23	# Lsun
+Lint_dunham = 3.3e8 * guter_fluxes.T[-1]*c/70e-6 * 1e-23	# Lsun
+Lint_dunham_err = 3.3e8 * guter_fluxes.T[-1]*guter_rel_errs[-1]*c/70e-6 * 1e-23	# Lsun
 
 ### Kryukova12 Lmir vs. Lbol ###
 dist1 = 429	# pc
@@ -338,22 +338,25 @@ Lmir2 = (19.79*guter_fluxes.T[0] + 16.96*guter_fluxes.T[1] + 10.49*guter_fluxes.
 Lmir2_err = (19.79*guter_fluxes.T[0]*guter_rel_errs[0] + 16.96*guter_fluxes.T[1]*guter_rel_errs[1] + 10.49*guter_fluxes.T[2]*guter_rel_errs[2] + 5.50*guter_fluxes.T[3]**guter_rel_errs[3] + 4.68*guter_fluxes.T[4]*guter_rel_errs[4] + 4.01*guter_fluxes.T[5]*guter_rel_errs[5] + 4.31*guter_fluxes.T[6]*guter_rel_errs[6] + 0.81*guter_fluxes.T[7]*guter_rel_errs[7]) * 1e-6 * dist2**2
 
 # For alpha > 0.3
-Lbol_kryukova_rising1 = Lmir1 / (-0.466 * np.log(ir_spix) + 0.337)**2
-Lbol_kryukova_rising2 = Lmir2 / (-0.466 * np.log(ir_spix) + 0.337)**2
+Lbol_kryukova_rising1 = Lmir1 / (-0.466 * np.log10(ir_spix) + 0.337)**2
+Lbol_kryukova_rising2 = Lmir2 / (-0.466 * np.log10(ir_spix) + 0.337)**2
 
-Lbol_kryukova_rising1_err = Lmir1 / ( np.sqrt( (0.014 * np.log(ir_spix))**2 + 0.053**2)/(-0.466 * np.log(ir_spix) + 0.337)**2 * np.sqrt(2))
[…]

### 2014-12-17 git_add.sh

@@ -35,7 +35,8 @@ git add gutermuth2008_serps_ysos1.txt
 git add notes_serpsouth_reduction.txt
 git add serps_yso1.reg
 git add vla_serps_merger_gutermuth_try1.csv
-
+git add IRAM_sources.reg
+git add Radio_Correlations.py
 git add AAS_2015/225th_AAS_Abstract.rtf
 
 git add Data/reduction_notes.txt

### 2014-12-17 Paper/paper.tex
modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   git_add.sh 	new file:   uv_space.png

@@
 Jansky Very Large Array in its C configuration.
-Our focus is a 4' x 4' area around the central filament ($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0).
+Our focus is a 3.5' x 3.5' area around the central filament.
 We detect roughly 18 sources, 10 of which are probably protostellar in nature.
 We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region.
-We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously labeled starless cores.
+We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously identified starless cores.
 We compare our radio sources to the known centimeter vs.
 bolometric luminosity relationship.
-With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more radio protostars.
+With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more protostars at centimeter wavelengths.
 
@@
 X-ray studies of Serpens South have yet to be published.
-Presently only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al.
+Presently only one radio study of Serpens South has been conducted, which used the Karl G.
+Jansky Very Large Array (VLA) in its A configuration in 2011 (Ortiz-Leon et al.
 in prep).
@@
 High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not.
-HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar.
-Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.
+Free-free emission around low-mass protostars arises from shocks at the base of protostellar jets that shock the surrounding envelope material.
+Non-thermal emission around young (Class 0 and I), low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission created by stellar magnetic fields.
+(The gyrosynchrotron can also be magnetic reconnection events in their coronae I believe, check some of the recent Goulds Belt distance papers for their explanations.) %or possibly from jets that produce synchrotron emission in their tails.
 
@@
 \tabletypesize{\footnotesize}
-\tablecaption{EVLA Image Properties}
+\tablecaption{VLA Image Properties}
 \tablehead{
@@
 The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband.
-We focused on a 3.5 arcsec x 3.5 arcsec region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$.
+We focused on a 3.5 arcmin x 3.5 arcmin region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$.
+The 6.31 and 4.14 cm images had primary beam diameters of 9.5 and 6.2 arcminutes respectively.
 Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation.
@@
 The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}.
-We also deconvolved the Stokes $V$ images, but did not find any significant signal.
 

### 2014-12-17 git_add.sh

@@ -38,6 +38,7 @@ git add vla_serps_merger_gutermuth_try1.csv
 git add IRAM_sources.reg
 git add Radio_Correlations.py
 git add AAS_2015/225th_AAS_Abstract.rtf
+git add uv_space.png
 
 git add Data/reduction_notes.txt
 

### 2014-12-24 Paper/paper.tex
modified:   Data/reduction_notes.txt 	new file:   Dzib13_Classes.tab 	new file:   Dzib13_Classes_Corr.tab 	new file:   Dzib13_Data.tab 	new file:   Dzib13_Data_Corr.tab 	modified:   Make_Figs.py 	new file:   Mallick13_Data.tab 	new file:   Paper/figures/Infra_SEDs_OnePlot-eps-converted-to.pdf 	new file:   Paper/figures/SPIRE_350_Figure-eps-converted-to.pdf 	new file:   Paper/figures/SerpSouth_Lower_GaussFits-eps-converted-to.pdf 	new file:   Paper/figures/SerpSouth_PACS70_Contour-eps-converted-to.pdf 	new file:   Paper/figures/SerpSouth_SPIRE250_Contour-eps-converted-to.pdf 	new file:   Paper/

@@
 %\submitted{Submitted: \today}
-\title{Radio Sources in the Central Filament of the Serpens South Protocluster}
+\title{Radio Properties of Young Protostars in the Central Filament of the Serpens South Infrared Dark Cloud}
 \author{Authors}
@@
 We characterize the radio emission and put it in context with 2MASS, Spitzer and Herschel data from the region.
-We find new embedded protostars that have yet to be resolved at shorter wavelengths, and in some cases confirm compact centimeter emission in previously identified starless cores.
 We compare our radio sources to the known centimeter vs.
@@
 With our relatively short integration time and weak detection of many more possible radio sources, we speculate that longer, higher resolution radio measurements of the region would yield confident detections of many more protostars at centimeter wavelengths.
+[Not finished...]
 
@@
 It lies south of the Serpens Main cloud and is just West of the bright W40 HII region.
-Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation.
+Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy Survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars suggesting it is in a very early phase of cluster formation.
+
 	Since its discovery, it has become the center of a wide range of scholarship.
-This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}.
+This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14, Nakamura14a}.
 X-ray studies of Serpens South have yet to be published.
@@
 
-	Because of its isolated formation, Serpens South presents a unique opportunity to study the environmental influences on protostars in a young stellar cluster.
+%	Because of its isolated formation, Serpens South presents a unique opportunity to study the environmental influences on protostars in a young stellar cluster.
 A multi-wavelength approach will be key to fully understanding to non-normative behaviors of protostars in a high-density environment such as Serpens South.
 
-	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}.
-Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star.
+	Early radio studies of protostars found an excess of radio emission compared to the Lyman-Alpha continuum drop off expected from a normal ZAMS star.
 Theory and observations have best explained protostellar radio emission as having two components, thermal and non-thermal.
@@
 
-	Towards the two goals of 1) locating new embedded protostars in the Serpens South protocluster and 2) better understanding the mechanisms of protostellar radio emission on a global scale, we carried out EVLA observations of Serpens South's central filament at 4.1 and 6.3 centimeters.
+	The VLA has been a proven tool for detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10,Dzib13}.
+With the goal of locating embedded protostars in the Serpens South protocluster, we carried out VLA observations of Serpens South's central filament at 4.1 and 6.3 centimeters.
 In $\S 2$ we present our observations.
@@
 
-We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration.
-The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband.
-We focused on a 3.5 arcmin x 3.5 arcmin region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$.
-The 6.31 and 4.14 cm images had primary beam diameters of 9.5 and 6.2 arcminutes respectively.
-Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation.
-\autoref{fig:serpsouth_fov} shows Serpens South at 350 micron and outlines our field of view.
+We observed Serpens South on July 2, 2013, for 1 hour with the VLA in its C array configuration.
+In order to derive a spectral index, we split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm) with a bandwidths of 1.024 GHz.
+At 4.75 and 7.25 GHz, our images had primary beam diameters of 9.5 and 6.2 arcminutes respectively.
+Our observation focused on a 3.5 arcmin x 3.5 arcmin region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$ (\autoref{fig:serpsouth_fov}).
+During our hour-long observation, we switched from Serpens South to J1804 + 0101 every 10 minutes for gain calibrations.
 
@@
 \includegraphics[keepaspectratio=True,scale=.55]{figures/SerpSouth_FOV.eps}
-\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South.
+\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South outlining its filamentary structure.
 Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively.
-The green box indicates our region of interest with the EVLA.}}
+The green box indicates our region of interest with the VLA.
+The black contour intensity level is set at 365 mJy/sr.}}
 \end{figure}
@@
 We deconvolved the Stokes $I$ images with the Cotton-Schwab algorithm \citep{Schwab84} using the CLEAN method \citep{Hogbom74,Clark80}.
-We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution with robust weighting, also known as Briggs weighting \citep{Briggs95}, with a \emph{robust} parameter set to 0.5.
+We experimented with natural, robust and uniform weighting, and found the best compromise between noise level and source resolution using robust weighting \citep{Briggs95}, with the \emph{robust} parameter set to 0.5.
 The synthesized beam sizes and RMS values for our two images are detailed in \autoref{tab:image_pars}.
+We performed a primary beam correction on our images by convolving the CLEANed images with the array's modeled flux response.
 
-Observing Serpens South at radio wavelengths is difficult because of the extended and bright HII region W40 directly to the East, which adds to over-resolved flux and increases the RMS noise level in our images.
+%Observing Serpens South at radio wavelengths is difficult because of the extended and bright HII region W40 directly to the East, which adds to over-resolved flux and increases the RMS noise level in our images.
 In addition, our short integration time--45 minutes on source--left us with a less than desirable UV coverage at long UV distances.
 Long UV distance coverage is particularly important because we are trying to resolve point source emission.
-Further EVLA studies of Serpens South would benefit from extended array configurations and longer integration times.
+Further VLA studies of Serpens South would benefit from extended array configurations and longer integration times.
 
@@
 
-VLA\_1	&	18 30 09.68	&	-02 00 32.8	&	749 $\pm$ 6	&	718	&	844 $\pm$ 8	&	794	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02	&	Extragal.?\\[1ex]
+VLA\_1	&	18 30 09.68	&	-02 00 32.8	&	749 $\pm$ 42	&	718	&	844 $\pm$ 43	&	794	&	0.28 $\pm$ 0.08	&	0.24 $\pm$ 0.07	&	Extragal.?\\[1ex]
 
-VLA\_2	&	18 30 04.79	&	-02 00 34.1	&	177 $\pm$ 7	&	138	&	87 $\pm$ 7	&	72	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14	&	Extragal.\\[1ex]
+VLA\_2	&	18 30 04.79	&	-02 00 34.1	&	177 $\pm$ 5	&	138	&	87 $\pm$ 8	&	72	&	-1.67 $\pm$ 0.1	&	-1.55 $\pm$ 0.16	&	Extragal.\\[1ex]
 
-VLA\_3	&	18 30 02.55	&	-02 00 48.5	&	140 $\pm$ 2	&	99	&	116 $\pm$ 10	&	87	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15	&	Extragal.\\[1ex]
+VLA\_3	&	18 30 02.55	&	-02 00 48.5	&	140 $\pm$ 6	&	99	&	116 $\pm$ 12	&	87	&	-0.46 $\pm$ 0.11	&	-0.3 $\pm$ 0.16	&	Extragal.\\[1ex]
 
-VLA\_4	&	18 30 01.53	&	-02 00 51.6	&	1663 $\pm$ 32	&	1178	&	946 $\pm$ 28	&	515	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02	&	Extragal.\\[1ex]
+VLA\_4	&	18 30 01.53	&	-02 00 51.6	&	1663 $\pm$ 50	&	1178	&	946 $\pm$ 55	&	515	&	-1.33 $\pm$ 0.07	&	-1.96 $\pm$ 0.07	&	Extragal.\\[1ex]
 
-VLA\_5	&	18 30 14.79	&	-02 01 27.3	&	106 $\pm$ 5	&	95	&	167 $\pm$ 10	&	173	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13	&	Extragal.?\\[1ex]
+VLA\_5	&	18 30 14.79	&	-02 01 27.3	&	106 $\pm$ 12	&	95	&	167 $\pm$ 13	&	173	&	1.07 $\pm$ 0.14	&	1.41 $\pm$ 0.14	&	Extragal.?\\[1ex]
 
-VLA\_6	&	18 30 06.62	&	-02 01 28.9	&	79 $\pm$ 7	&	61	&	33 $\pm$ 4	&	56	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23	&	Extragal.\\[1ex]
+VLA\_6	&	18 30 06.62	&	-02 01 28.9	&	79 $\pm$ 3	&	61	&	33 $\pm$ 4	&	56	&	-2.04 $\pm$ 0.15	&	-0.22 $\pm$ 0.24	&	Extragal.\\[1ex]
 
-VLA\_7	&	18 30 05.81	&	-02 01 44.9	&	48 $\pm$ 4	&	40	&	84 $\pm$ 7	&	63	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31	&	Class I\\[1ex]
+VLA\_7	&	18 30 05.81	&	-02 01 44.9	&	48 $\pm$ 8	&	40	&	84 $\pm$ 8	&	63	&	1.29 $\pm$ 0.2	&	1.08 $\pm$ 0.31	&	Class I\\[1ex]
 
-VLA\_8	&	18 30 06.89	&	-02 02 11.5	&	39 $\pm$ 3	&	46	&	50 $\pm$ 6	&	50	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29	&	Extragal.?\\[1ex]
+VLA\_8	&	18 30 06.89	&	-02 02 11.5	&	39 $\pm$ 5	&	46	&	50 $\pm$ 6	&	50	&	0.55 $\pm$ 0.19	&	0.18 $\pm$ 0.3	&	Extragal.?\\[1ex]
 
-VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 1	&	50	&	60 $\pm$ 1	&	44	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29	&	Class 0?\\[1ex]
+VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 3	&	50	&	60 $\pm$ 3	&	44	&	-0.22 $\pm$ 0.07	&	-0.31 $\pm$ 0.3	&	Class 0$^{*}$?\\[1ex]
 
-VLA\_10	&	18 30 02.95	&	-02 02 32.2	&	287 $\pm$ 6	&	119	&	260 $\pm$ 17	&	73	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15	&	Unknown\\[1ex]
+VLA\_10	&	18 30 02.95	&	-02 02 32.2	&	287 $\pm$ 14	&	119	&	260 $\pm$ 21	&	73	&	-0.23 $\pm$ 0.1	&	-1.15 $\pm$ 0.16	&	Unknown\\[1ex]
 
-VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 2	&	36	&	73 $\pm$ 4	&	58	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]
+VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 6	&	36	&	73 $\pm$ 5	&	58	&	1.5 $\pm$ 0.17	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]
 
-VLA\_12	&	18 30 04.11	&	-02 03 02.1	&	30 $\pm$ 2	&	24	&	79 $\pm$ 2	&	58	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48	&	Class 0$^{*}$\\[1ex]
+VLA\_12	&	18 30 04.11	&	-02 03 02.1	&	30 $\pm$ 8	&	24	&	79 $\pm$ 4	&	58	&	2.31 $\pm$ 0.27	&	2.06 $\pm$ 0.48	&	Class 0\\[1ex]
 
-VLA\_13	&	18 30 03.54	&	-02 03 08.4	&	186 $\pm$ 1	&	178	&	231 $\pm$ 3	&	227	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07	&	Class 0$^{*}$\\[1ex]
+VLA\_13	&	18 30 03.54	&	-02 03 08.4	&	186 $\pm$ 11	&	178	&	231 $\pm$ 12	&	227	&	0.51 $\pm$ 0.08	&	0.58 $\pm$ 0.1	&	Class 0\\[1ex]
 
-VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 0	&	37	&	83 $\pm$ 2	&	61	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]
+VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 4	&	37	&	83 $\pm$ 4	&	61	&	2.29 $\pm$ 0.15	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]
 
-VLA\_15	&	18 30 04.60	&	-02 03 14.1	&	68 $\pm$ 1	&	52	&	49 $\pm$ 4	&	51	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27	&	Extragal.\\[1ex]
+VLA\_15	&	18 30 04.60	&	-02 03 14.1	&	68 $\pm$ 2	&	52	&	49 $\pm$ 4	&	51	&	-0.74 $\pm$ 0.1	&	-0.08 $\pm$ 0.28	&	Extragal.\\[1ex]
 
-VLA\_16	&	18 30 03.25	&	-02 03 26.6	&	63 $\pm$ 2	&	58	&	55 $\pm$ 1	&	65	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23	&	Class II\\[1ex]
+VLA\_16	&	18 30 03.25	&	-02 03 26.6	&	63 $\pm$ 3	&	58	&	55 $\pm$ 3	&	65	&	-0.28 $\pm$ 0.08	&	0.27 $\pm$ 0.24	&	Class II\\[1ex]
 
-VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 3	&	135	&	161 $\pm$ 4	&	167	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1	&	Class I\\[1ex]
+VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 8	&	135	&	161 $\pm$ 9	&	167	&	0.22 $\pm$ 0.08	&	0.5 $\pm$ 0.12	&	Class I\\[1ex]
 
-VLA\_18	&	18 30 09.40	&	-02 04 08.8	&	170 $\pm$ 3	&	182	&	167 $\pm$ 10	&	134	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09	&	Extragal.?
+VLA\_18	&	18 30 09.40	&	-02 04 08.8	&	170 $\pm$ 9	&	182	&	167 $\pm$ 13	&	134	&	-0.04 $\pm$ 0.1	&	-0.71 $\pm$ 0.11	&	Extragal.?
 
@@
 Unless otherwise noted, Class 0 classifications come from Herschel \citep{Bontemps10} and Class I \& II  from Spitzer \citep{Gutermuth08}.
-(?) denotes uncertaintity.
+(?) denotes uncertainty.
 ($^{*}$) denotes classified by this work.}
@@
 
-In choosing our sources, we restricted ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength.
-We chose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}.
-We took only sources that had at least a $4\sigma$ strength in the 4.1 cm image, and were left with a total of 18 radio sources.
-We note that we found $\sim$6 sources at the $2\sigma$ level that aligned within 2 arcsecond of an infrared association, however, we do not consider them strong detections and do not include them in our final source list.
-As stated in \autoref{sec:observations}, further observations with longer integration will likely be able to confidently detect these protostellar radio sources.
+Out of the 50+ Spitzer identified Class I and II YSOs located in and around Serpens South's central filament, we detect 18 radio sources at our sensitivity level.
+In choosing our sources, we restricted ourselves to a circular region centered on our phase center extending out to 50\% of the primary beam response.
+We chose our sources based on their appearance and strength in both our 4.1 and 6.3 cm images, their spatial proximity to infrared associations, and by referencing a source extracted sample using Sextractor \citep{Bertin96}.
+We only took sources that had at least a $4\sigma$ detection in the 4.1 cm image.
+We note that we found $\sim$6 sources at the $2\sigma$ level that aligned within 2 arcsecond of infrared associations, however, we do not consider them strong detections and do not include them in our final source list.
+Further observations with higher sensitivity will likely be able to confidently detect these protostellar radio sources.
 
-\begin{figure}[h!]
+\begin{figure}
 \label{fig:serpsouth_fov_contour}
@@
 \includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
-\caption{\small{Serpens South radio continuum at 6.3 cm, focused in on green box from \autoref{fig:serpsouth_fov}.
+\caption{\small{Serpens South's central filament at 4.1 cm, focused in on the green box from \autoref{fig:serpsouth_fov}.
 Radio contours start at 4$\sigma$ and end at 50$\sigma$.
@@
 \epsscale{1.15}
-
 \plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
-\caption{{\bfseries Left}: Radio continuum at 6.3 cm focused in on red box from \autoref{fig:serpsouth_fov_contour}.
-Blue and red crosses correspond to Spitzer identified Class I and II protostars.
+\caption{{\bfseries Left}: Radio continuum of our sources VLA 6 to VLA 17 at 4.1 cm.
+Blue and red crosses correspond to Class I and II protostars, respectively, identified by Spitzer.
 Green crosses correspond to 1.2 mm dust peaks identified by IRAM.
 {\bfseries Right}: Identical contours on the left but with a background PACS 70 $\mu$m image.
-The radio contour beam size is shown to the lower-left.}
+The radio image beam size is shown to the lower-left.}
 \end{figure*}
 
-We ran source extractions on the spatial positions of our final source list over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
+We used CASA's IMFIT function to fit 2D gaussians to our chosen radio sources.
+For strong and relatively isolated sources, we can reasonably rely on the 2D gaussian integrated flux densities.
+For somewhat blended sources, such as VLA 9 and 14, manually-calculated peak fluxes are likely more reliable for spectral index calculations.
+Integrated flux errors were calculated by adding in quadrature the flux error output from IMFIT with an assumed 5\% systematic flux calibration error.
+Peak flux errors were calculated by adding in quadrature the relative error of the image RMS with an assumed 5\% systematic flux calibration error.
+
+We cross-referenced our radio source positions with the 2MASS catalogue, and ran source extractions over the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel.
 We used a 2 arcsecond maximum matching tolerance for these extractions.
-Apertures and adopted corrections were consistent with the HOPS survey.
+Apertures and adopted corrections were consistent with the HOPS survey (Gutermuth et al.
+in prep).
 
-Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond.
+Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match a Spitzer identified Class I or II protostar within 1 arcsecond.
 A total of ten out of our 18 sources have signs that indicate they are protostellar in nature.
-One of our radio sources, VLA 12, matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they quote as starless.
+One of our radio sources, VLA 12, matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they identify as Class 0.
 
 We can calculate the number of random background sources we would expect to find in our images.
-We use the formulation found in \citet{Shirley07}, who draw from radio studies done by \citet{Fomalont91}.
-The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by $N(>S) = 0.42\cdot(S/30\ \mu \text{Jy})^{-1.18}$ arcmin$^{-2}$.
-Therefore, the total number of sources with flux $S$ greater than 50 $\mu$Jy at 6 cm is 0.229 arcmin$^{-2}$.
-This leads to a 0.4\% chance that a background source falls inside any one synthesized beam centered on a compact radio source, and gives us on average $\sim$9 background sources above 50 $\mu$Jy within our 3.5' x 3.5' region of interest.
-This agrees with our analysis, as we find roughly 8 sources that are likely background sources.
+We use the formulation found in \citet{Shirley07} and \citet{Dzib13}, who draw from radio studies done by \citet{Fomalont91}.
+The density of random background radio sources above a flux limit of $S\ \mu$Jy at 6 cm is given by
+\begin{equation*}
+n(>S) = 0.42\pm0.05\left(\frac{S}{30\ \mu \text{Jy}}\right)^{-1.18\pm0.19} \text{arcmin}^{-2}
+\end{equation*}
+Therefore, the total number of sources with flux $S$ greater than 30 $\mu$Jy at 6 cm is 0.42 arcmin$^{-2}$.
+This leads to a 0.7\% chance that a background source falls inside a 4.8 x 3.9 arcsec synthesized beam centered on a compact radio source.
+It also gives us on average $\sim6\pm1$ background sources within our 3.5' x 3.5' region of interest above a 3$\sigma$ level.
+We find roughly 5 to 8 sources that we identify as extragalactic, which is at worst within 2 standard deviations from the expectation.
 
-%\subsection{Spectral Indices}
-%\label{sec:spix}
-%A spectral index is the slope of the flux density in log space between two wavelengths. At radio wavelengths, the spectral index is defined as
-%
-%\begin{equation}
-%\label{eq:radio_spix}
-%\alpha_{\text{radio}} = \frac{\ln({S_{\lambda_{1}}/S_{\lambda_{2}})}}{\ln({\lambda_{2}/\lambda_{1}})}
-%\end{equation}
-%where $\lambda_{2} > \lambda_{1}$ \citep{Shirley07}.
+\subsection{Spectral Indices}
+\label{sec:spix}
+At radio wavelengths, the spectral index is defined as
+\begin{equation}
+\label{eq:radio_spix}
+\alpha_{\text{radio}} = \frac{\ln({S_{\lambda_{1}}/S_{\lambda_{2}})}}{\ln({\lambda_{2}/\lambda_{1}})}
+\end{equation}
+where $\lambda_{2} > \lambda_{1}$ \citep{Shirley07}.
 Note that we have defined $S_{\lambda}$ in terms of a flux density (e.g.
-Jansky) not a flux (e.g.
+Jansky) and not a flux (e.g.
 $\lambda S_{\lambda}$ or $\nu S_{\nu}$).
-Theoretical studies have shown that
-%
+Flat radio spectral indices ($\alpha > -0.1$) are generally indicative of optically thin free-free emission, while rising indices ($\alpha \sim 2.0$) are representative of optically thick free-free emission \citep{Anglada98}.
 
@@
 VLA 2, 3, 4, 6, and 15 are very likely extragalactic in nature.
-They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission.
+They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission typical of a galaxy's radio spectrum.
 
 \sourcenote{Unclear Sources}
-While VLA 1 and 5 have no infrared, far-infrared or millimeter associations and are isolated from the filament, they have a flat and rising radio spectral indices suggesting optically thin and thick free-free emission respectively.
+While VLA 1 and 5 have no infrared, far-infrared or millimeter associations and are isolated from the filament, they have a flat or rising radio spectral indices suggesting optically thin or thick free-free emission respectively.
 Although galaxies can produce free-free emission from large HII clouds, the dominant component of a galaxy's radio emission output comes from non-thermal synchrotron emission with a declining spectrum.
-Nonetheless, we tentatively classify these sources as extragalactic due to their lack of associations.
+Moreover, in \citet{Dzib13}'s study of 190 radio sources in the Ophiuchus star forming cloud, they didn't find a single extragalactic source with a radio spectral index larger than $\sim$0.
+Nonetheless, we tentatively classify these sources as extragalactic due to their lack of any association at shorter wavelengths.
 
 VLA 18 is spatially distinct from the filament but has a flat radio spectral index and actually has three very weak infrared associations at 3.6, 4.5 and 5.8 $\mu$m.
-However, we speculate that these associations are coincidental and tentatively classify VLA 18 as extragalactic.
-
-\begin{figure}
-\label{fig:serpsouth_vla10_contour}
-\centering
-\includegraphics[keepaspectratio=True,scale=.3]{figures/SerpSouth_VLA10_contour.eps}
-\caption{\small{Zoom in of the elongated VLA 10 source.
-Blue solid and red dashed contours correspond to 4.1 and 6.3 cm images respectively.
-The lower-left beam is the 4.1 cm beam size.
-Blue crosses represent Spitzer identified Class I sources.
-}}
-\end{figure}
+However, we speculate that these associations are coincidental due to their odd linear behavior, and tentatively classify VLA 18 as extragalactic.
 
@@
 We treat the whole elongated structure as one source.
-At our higher resolution 4.1 cm image, we can resolve two distinct emission components that are blended at our lower resolution 6.3 cm image (\autoref{fig:serpsouth_vla10_contour}).
-We cannot confidently rely on our gaussian fitted fluxes or spectral index due to the morphology of the source.
+At our higher resolution 4.1 cm image, we can resolve two distinct emission components that are blended at our lower resolution 6.3 cm image (\autoref{fig:vla10 and vla12}).
+We cannot confidently rely on our gaussian fitted fluxes due to the morphology of the source.
 For VLA 10's peak flux, we used the Northern structure in the 4.1 cm map.
@@
 An H$_{2}$ study conducted by \citet{Teixeira12}, however, labeled VLA 11 as an outflow source with a jet running from North-East to South-West, almost perpendicular to the direction necessary for it to be an outflow source powering VLA 10's emission.
-Further evidence that would support a non-extragalactic classification of both the South and North structures of VLA 10 is the fact that the cold dust seen at and longward of 70 $\mu$m neatly fits around VLA 10's elongated morphology, as seen in \autoref{fig:zoom}.
+Further evidence that would support a non-extragalactic classification of both the South and North structures of VLA 10 is the fact that the dust seen at and longward of 70 $\mu$m neatly fits around VLA 10's elongated morphology, as seen in \autoref{fig:zoom}.
+
+Lastly, the fact that VLA 10 is elongated anti-parallel to the synthesized beam's natural eccentricity emphasizes the fact that the morphology is true source structure and not artificial.
+Higher resolution observations should be able to spatially separate and resolve the individual emission components and better determine the nature behind its radio signal.
 
 \sourcenote{Protostellar Sources}
-The remainder of our 18 sources, VLA 7, 9, 11, 12, 13, 14, 16 and 17 are likely protostellar in nature.
-With the exception of VLA 9, all of these sources have either flat or rising radio spectral indices indicative of optically thin or thick free-free emission.
-We classify VLA 12, 13 and 14 as three newly identified embedded Class 0 protostars, separated form each other by less than 15 arcseconds.
+The remainder of our sources, VLA 7, 9, 11, 12, 13, 14, 16 and 17, are likely protostellar in nature.
+VLA 7, 11, 12, 13, 16, and 17 are associated with Spitzer and Herschel identified Class 0, I and II protostars.
+All sources have either flat or rising radio spectral indices indicative of optically thin or thick free-free emission expected from an ionized plasma created by protostellar processes.
+
+\begin{figure*}
+\label{fig:vla10 and vla12}
+\epsscale{1.17}
+\plottwo{figures/SerpSouth_VLA10_contour.eps}{figures/SerpSouth_VLA12_contour.eps}
+\caption{
+{\bfseries Left}: Zoom-in of the elongated VLA 10 source.
+Blue solid and red dashed contours correspond to 4.1 and 6.3 cm images, respectively, and start at the 4$\sigma$ level.
+The lower-left beam is the 4.1 cm beam size.
+Blue crosses represent Spitzer identified Class I sources.
+{\bfseries Right}: Zoom-in of VLA 12 and surrounding sources.
+Blue solid contour is 4.1 cm data and red dashed contour is 6.3 cm data.
+Both radio contours start at their respective 3$\sigma$ level.
+Blue crosses are Spitzer identified Class I sources.
+Green cross is IRAM 1.2 mm identified Class 0 source.
+}
+\end{figure*}
+
+VLA 7 and 17 correspond to Spitzer Class I sources and have an average radio spectral index of $0.8 \pm 0.2$.
+VLA 16 is our only radio source associated with a Spitzer Class II protostar.
+Its peak flux-derived spectral index is likely more reliable than its integrated flux-derived spectral index due to weak spurious signal in close proximity at 6.3 cm.
+
+While the infrared source associated with VLA 11 was initially classified as Class I with Spitzer data, it was later classified as Class 0 with Herschel images \citep{Bontemps10}.
+We report a confident detection  of compact radio emission at both 6.3 and 4.1 cm with a rising spectrum suggesting optically thick free-free emission, which agrees with the notion that it is perhaps more embedded than previously thought.
+
+VLA 12 is not visible short-ward of 24 microns.
+It is, however, the peak structure of diffuse 1.2 mm emission tracing cold dust and was therefore classified as a Class 0 source \citep{Maury11}.
+This classification used a 25 arcsecond FWHM fit, which encompassed the infrared sources associated with VLA 13 and 14.
+Here, we confirm VLA 12's Class 0 classification with the detection of compact radio emission, which \citet{Andre00} list as one of the qualifications for a Class 0 protostar.
+
+For VLA 13, we find infrared associations on the IRAC 2, 3 and 4 bands but not on the IRAC 1 band at 3.6 $\mu$m.
+We report an infrared spectral index from 8 to 24 $\mu$m of $\sim$2.4, which, according to \citet{Lada87}'s classification scheme, would make it a Class I protostar.
+Herschel studies, however, classify it as a Class 0 source \citep{Bontemps10}.
+While we classify it as Class 0, it may in fact be in a late Class 0 phase transitioning to a Class I protostar.
+
+In far-infrared images from 24 to 250 $\mu$m, it is clear that VLA 14 lies within or around a gaseous envelope (\autoref{fig:infrared_associations}).
+However, because of the low resolution of the PACS and SPIRE images, we do not retrieve any source extractions within 2 arcseconds of its radio peak.
+Even in the MIPS 24 $\mu$m image, it is not seen as an individual source but rather an extension of the emission structure from VLA 13 (\autoref{fig:infrared_associations}).
+This is likely why previous studies missed this source, and implies that if a compact source exists it is likely extremely young or extremely embedded.
+Here, we show that VLA 14 is a distinct radio source with a steeply rising radio spectral index of $\sim 1.2$, revealing the presence of an embedded Class 0 protostar.
+The 5 arcsecond separation between VLA 13 and 14 corresponds to an angular separation of only 0.01 pc ($\sim$2,000 AU) if Serpens South lies at a distance of 429 pc away.
+However, VLA 13 could lie much further away from VLA 14 in 3D coordinates.
+
+We also tentatively classify VLA 9 as another Class 0 source, although this is somewhat speculative.
+Like VLA 14, it has no strong infrared associations--although it does lie within 5 arcseconds of a weak infrared source.
+Also similar to VLA 14, VLA 9 is placed in a region of high protostellar density and falls in front of diffuse far-infrared emission.
+Its 6.3 cm emission does, however, begin to blend with VLA 10 at the 3$\sigma$ level, raising the possibility that it is tied to the structure powering VLA 10's radio emission (\autoref{fig:vla10 and vla12}).
 
@@
 \section{Discussion}
+\label{sec:discussion}
 
 \subsection{Protostars in the Central Filament}
-Spitzer observations revealed dozens of Class I and II protostars spatially correlated to the central filament \citep{Gutermuth08}.
-Herschel observations revealed colder clumps of dust corresponding to younger Class 0 protostars \citep{Bontemps10}, however, with their poor spatial resolution they cannot reasonably resolve individual compact cores.
+\label{sec:central filament}
 
-\subsection{$L_{\text{infrared}}$ and $L_{\text{bol}}$ Relationship}
+[Comment on how out of 50+ Spitzer identified Class I and II protostars and half a dozen Class 0 protostars identified by Herschel in our field of view, we only confidently detect $\sim6$, and weakly detect $\sim11$.
+Anything to be said about the clustering of the three Class 0 protostars in the center of our field of view?
+VLA 13 and 14 have an angular separation of only 0.01 pc, anything interesting we can say?]
 
+\subsection{Sources of Outflow}
+\label{sec:outflows}
+Radio continuum images have shown elongation with respect to radio jets etc etc...
+
+H$_{2}$ $\nu$ = 1--0 S(1) 2.122 $\mu$m line imaging conducted by \citet{Teixeira12} showed that the infrared sources associated with VLA 11, 13 and 17 are sources driving large scale outflows.
+VLA 11 and 13's radio emission structures at 4.1 cm mildly reflect this, as they are slightly elongated in the proposed direction of outflow (\autoref{fig:vla10 and vla12}).
+VLA 17's morphology does not exceed the natural eccentricity of the beam.
+Future sub-arcsecond resolution observations will likely be able to resolve the radio-loud jets at the center of VLA 11 and 13.
+
+\citet{Nakamura11} carried out CO (J = 3--2) and HCO$^{+}$ (J = 4--3) observations towards Serpens South to map the broad-scale outflow from the central filament.
+
+We can't directly correlate outflow and envelope mass properties due to blending of dust sources etc etc.
+
+\subsection{The $S_{\text{radio}}$ and $L_{\text{bol}}$ Relationship}
+\label{sec:correlations}
+
+-- talk about anglada, beltran, shirley, scaife and others who have plotted Sradio vs. Lbol
+
+-- mention that we cannot easily derive Lbol estimates due to source blending
+
+-- talk about Kryukova and Dunham relationship, mention errors etc.
+
+-- present plots
+
+\subsection{VeLLOs}
+\label{sec:vellos}
 The internal luminosity $L_{\text{int}}$ of a protostar is defined as the total luminosity from the protostar and its circumstellar disk if present.
@@
 
-\subsection{The $S_{\text{radio}}$ and $L_{\text{bol}}$ Relationship}
-
-\subsection{Sources of Molecular Outflow}
-
 %% Conclusions
 \section{Conclusions}
+\label{sec:conclusions}
+
+present major conclusions
+
+-- new protostars, better estimates of protostellar positions
+
+-- weak detection of a few more protostars, no evident detection of many protostars
+
+-- highly clustered and fragmentation of gas/dust evident
+
+-- outflow elongation for two sources
+
+-- Sradio and Lbol relationship
+
+-- VeLLO
+
+-- point to future studies
 
@@
 
-{\large To Include in Paper:} \\[.1in]
+{\large Questions I Still Need Answers To:} \\[.1in]
 
--- Discussion on radio spectral indices and their implications to emission \\
+-- Does optically thick thermal radio emission ($\alpha_{radio} > 1.0$) mean that the source is ``embedded''?
+In other words, can a protostellar source still be considered ``embedded'' in the sense that it is invisible at IRAC wavelengths, but have a radio spectral index indicative of optically thin thermal emission ($\alpha_{radio} \sim0$)?\\
 
--- Does optically thick radio emission from Spitzer Class I/II source mean anything particularly interesting?
-B/c it is Spitzer identified, does it mean that it comes not from an ultra-compact region but from some other mechanism?
-\\
+-- Is it even physically possible for VLA 10 to be a radio galaxy outflow source? In other words, is a 10 arcsecond angular extent on the size scale of typical radio galaxy jets? \\
 
--- Discussion on VeLLOs in sample. \\
+-- Can we get a table of Herschel protostars from Bontemps et al. 2010? Reason being is because I want to say if protostars have previously been detected or not.\\
 
--- L\_int correlations? \\ \\
+-- Are my classifications okay? Specifically, VLA 1, 5, 8, 9, 10 and 18? \\
 
--- Make radio\_alpha vs. L\_bol or L\_int graph?\\
+-- What does MIPS 24 $\mu$m emission trace around protostars, heated dust from disk?\\
 
--- Fit Spitzer end of SED to get more accurate L\_MIR ? \\
+-- Can we say anything about the fact that out of 50+ Spitzer identified Class I and II protostars, only $\sim$6 show strong radio emission?
+What is up with that?
+Does this say anything about relative masses of these protostars (perhaps all mid-low mass?) \\
 
-{\large Questions:} \\[.1in]
+-- Are the images to a high enough sensitivity to which I can say they are ``deep'' ? \\
 
--- What does Rob say about SS distance?\\
+\newpage
+\section{Additional Figures}
 
--- What paper should I quote for infrared source extraction photometry analysis?\\
+\begin{figure}[h!]
+\label{fig:serpsouth_upper_gaussfits}
+\centering
+\includegraphics[keepaspectratio=True,scale=.5]{figures/SerpSouth_Upper_GaussFits.eps}
+\caption{\small{4.1 cm map with 2D gaussian fits from CASA's IMFIT routine. Radio contours start at 3$\sigma$ level.
+}}
+\end{figure}
 
--- Do we have to worry about vibrational dust emission in our 4.1 cm data?\\
+\begin{figure}[h!]
+\label{fig:serpsouth_lower_gaussfits}
+\centering
+\includegraphics[keepaspectratio=True,scale=.5]{figures/SerpSouth_Lower_GaussFits.eps}
+\caption{\small{6.3 cm map with 2D gaussian fits from CASA's IMFIT routine. Radio contours start at 3$\sigma$ level.
+}}
+\end{figure}
 
--- What can we say about optically thick radio sources that match Spitzer sources? Embedded Class I source? \\
+\begin{figure}
+\label{fig:infra_SEDs}
+\centering
+\includegraphics[keepaspectratio=True,scale=.6]{figures/Infra_SEDs_OnePlot.eps}
+\caption{\small{All VLA sources that have any catalogued infrared associations.
+Infrared bands are 2MASS H and K from 1.1 - 2.2 $\mu$m, IRAC 1, 2, 3 and 4 from 3.6 - 8.0 $\mu$m, MIPS 24$\mu$m and PACS 70$\mu$m.
+}}
+\end{figure}
 
--- Is it even physically possible for VLA 10 to be a radio galaxy outflow source? In other words, is a 10 arcsecond angular extent on the size scale of typical radio galaxy outflows? \\
+\begin{figure}
+\label{fig:infrared_associations}
+\epsscale{1.1}
+\plottwo{figures/SerpSouth_Spitz36_Contour.eps}{figures/SerpSouth_Spitz58_Contour.eps}
+\plottwo{figures/SerpSouth_Spitz80_Contour.eps}{figures/SerpSouth_Spitz24_Contour.eps}
+\plottwo{figures/SerpSouth_PACS70_Contour.eps}{figures/SerpSouth_SPIRE250_Contour.eps}
+\caption{\small{ 4.1 cm radio contours plotted over infrared and far-infrared images ranging from 3.6 to 250 $\mu$m.
+Radio contours start at the 4$\sigma$ level, with the deconvolved beam size shown at lower-left.
+{\bfseries (a)} Spitzer IRAC 3.6 $\mu$m image.
+{\bfseries (b)} Spitzer IRAC 5.8 $\mu$m image.
+{\bfseries (c)} Spitzer IRAC 8.0 $\mu$m image.
+{\bfseries (d)} Spitzer MIPS 24 $\mu$m image.
+{\bfseries (e)} Herschel PACS 70 $\mu$m image.
+{\bfseries (a)} Herschel SPIRE 250 $\mu$m image.
+}}
+\end{figure}
 
--- Can we get a table of Herschel protostars from Bontemps et al.
-2010?
-Other papers, Teixeira12, Nakamura14 and more, quote protostellar classifications of individual protostars from Herschel data as if they had access to a Bontemps2010 catalogue.
-Perhaps they just asked the authors and got access to it.
-Ideally, we would want a catalogue of Class 0 protostars identified by Herschel with their flux values from 250 - 500 $\mu$m, the adopted FWHM apertures in the source extraction and Lbol and Menv properties they subsequently derived.\\
+\begin{figure}
+\label{fig:spix_class}
+\centering
+\includegraphics[keepaspectratio=True,scale=.6]{figures/Spix_Class.eps}
+\caption{\small{Radio spectral index of sources as a function of classification.
+}}
+\end{figure}
+
+\begin{figure}
+\label{fig:shirley36_corr}
+\centering
+\includegraphics[keepaspectratio=True,scale=.6]{figures/Shirley36_Correlation.eps}
+\caption{\small{Figure 2 from \citet{Shirley07} showing the 3.6 cm vs.
+Bolometric Luminosity correlation for protostars.
+Five of our protostellar sources are overlaid with a bolometric luminosities derived from a correlation that utilizes the protostars' mid-infrared luminosity \citep{Kryukova12}.
+Figure reproduced from \citet{Shirley07} with permission.
+}}
+\end{figure}
+
+\begin{figure}
+\label{fig:shirley60_corr}
+\centering
+\includegraphics[keepaspectratio=True,scale=.6]{figures/Shirley60_Correlation.eps}
+\caption{\small{Figure 2 from \citet{Shirley07} showing the 6.0 cm vs.
+Bolometric Luminosity correlation for protostars.
+Five of our protostellar sources are overlaid with a bolometric luminosities derived from a correlation that utilizes the protostars' mid-infrared luminosity \citep{Kryukova12}.
+Figure reproduced from \citet{Shirley07} with permission.
+}}
+\end{figure}
 

### 2014-12-24 Make_Figs.py

@@ -12,15 +12,22 @@ import matplotlib
 from astropy import coordinates as coord
 from astropy import units as u
 from matplotlib.widgets import Slider
+from AttrDict import AttrDict
+import re
+
+
+## Constants
+c = 2.99e8		# m / s
+au_per_pc = 206264.806	# au
 
 
 ## Flags
 savefig = False
 
 plot1 = False
-plot2 = True
-plot3 = False
-
+plot2 = False
+plot3 = True
+plot4 = False
 
 def sexig_to_deg(ra,dec):
 	length = len(ra)
@@ -129,10 +136,13 @@ if plot1 == True:
 if plot2 == True:
 
 	zoom = False
-	vla10 = True
+	vla10 = False
+	vla12 = True
 
-	figname = 'Paper/figures/SerpSouth_VLA10_contour.eps'
+	figname = 'Paper/figures/SerpSouth_VLA12_contour.eps'
 	#figname = 'Paper/figures/SerpSouth_zoom_contour.eps'
+
+	savefig = False
 
 	# Choose Image
 	color_im = 'FITS/PACS_100_micron_cropped.fits'
@@ -152,15 +162,15 @@ if plot2 == True:
 
 	fig.show_colorscale(cmap='CMRmap',stretch='power',exponent=.30,pmin=0,pmax=100.005)
 	fig.hide_colorscale()
-	fig.show_contour('FITS/SERPS_2.upper.briggs05.deeper.fits',alpha=1,cmap='Greys_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
+	fig.show_contour(contour_im,alpha=1,cmap='Greys_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
 
-	if vla10 == True:
+	if vla10 == True or vla12 == True:
 		fig.hide_layer('contour_set_1')
-		fig.show_contour('FITS/SERPS_2.upper.briggs05.deeper.fits',alpha=0.8,cmap='Blues_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
+		fig.show_contour(contour_im,alpha=0.6,cmap='Blues_r',levels=[rms*3,rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
 		contour_im = 'FITS/SERPS_2.lower.briggs05.deeper.fits'
[…]

### 2014-12-24 Radio_Correlations.py

@@ -50,7 +50,7 @@ scaifeb = AttrDict({})
 data = np.loadtxt('Scaife11b_Data.tab',dtype='str',delimiter='\t',usecols=(0,1,2,3,4,5,6,7,8,9))
 match = np.where(data.T[3]!='-')[0]
 scaifeb.classes = data.T[9][match]
-scaifeb.distances = np.array(map(lambda x: x[0:3],data.T[1]),float)/1e3
+scaifeb.distances = np.array(map(lambda x: x[0:3],data.T[1]),float)[match]/1e3
 scaifeb.flux_18 = np.array(data.T[8][match],float)
 scaifeb.Lbol = np.array(data.T[3][match],float)
 
@@ -58,6 +58,7 @@ scaifeb.Lbol = np.array(data.T[3][match],float)
 scaife = AttrDict({})
 scaife.Lbol = np.concatenate([scaifea.Lbol,scaifeb.Lbol])
 scaife.flux_18 = np.concatenate([np.log10(scaifea.flux_18/1e3*scaifea.dist**2),scaifeb.flux_18])
+scaife.distances = np.concatenate([[scaifea.dist]*scaifea.Lbol.shape[0], scaifeb.distances])
 
 # Load Centimeter Data
 data = pkl.Unpickler(open('Radio_Data.pkl','rb')).load()
@@ -67,22 +68,50 @@ for i in data:
 	except ValueError:
 		pass
 kern = AttrDict(data)
+kern.Lbol_sources = np.array(kern.Lbol_sources,int)
+
+# Load Mallick Data
+mallick_data = np.loadtxt("Mallick13_Data.tab",dtype='str',unpack=True,delimiter='\t')
+mallick = AttrDict({})
+mallick.ra = np.array(map(lambda x: x[0:10], mallick_data))
+mallick.dec = np.array(map(lambda x: x[11:20], mallick_data))
+mallick.jmag = np.array(map(lambda x: x[21:27], mallick_data))
+mallick.jmag_err = np.array(map(lambda x: x[28:33], mallick_data)) 
+mallick.hmag = np.array(map(lambda x: x[34:40], mallick_data)) 
+mallick.hmag_err = np.array(map(lambda x: x[41:46], mallick_data)) 
+mallick.kmag = np.array(map(lambda x: x[47:53], mallick_data)) 
[…]

### 2014-12-24 SERPS_SED.py

@@ -160,7 +160,9 @@ def radio_spix(flux1,flux2,lam1,lam2):
 	return np.log(flux1/flux2)/np.log(lam2/lam1)
 
 def radio_spix_err(flux1,flux1_err,flux2,flux2_err):
-	return np.sqrt( (flux1_err/flux1)**2 + (flux2_err/flux2)**2 )
+	# Add 5% errors to flux errors for calibration error
+	return np.sqrt(  (flux1_err/flux1)**2 + (flux2_err/flux2)**2 )
+
 
 
 # Load cm Peak Flux Data
@@ -174,15 +176,22 @@ upper_rms = 8.5e-6		# Jy
 lower_rms = 11.1e-6		# Jy
 for i in range(Source_Num):
 		cm_int_spix.append(	radio_spix(upper_data[i][0],lower_data[i][0],upper_lam,lower_lam) )
+		upper_data[i][1] = upper_data[i][0] * np.sqrt( (upper_data[i][1]/upper_data[i][0])**2 + 0.05**2 )
+		lower_data[i][1] = upper_data[i][0] * np.sqrt( (lower_data[i][1]/lower_data[i][0])**2 + 0.05**2 )
 		cm_int_spix_err.append(	radio_spix_err(upper_data[i][0],upper_data[i][1],lower_data[i][0],lower_data[i][1]) )
 		cm_peak_spix.append(	radio_spix(upper_peak_flux[1][i],lower_peak_flux[1][i],upper_lam,lower_lam) )
-		cm_peak_spix_err.append(radio_spix_err(upper_peak_flux[1][i],upper_rms,lower_peak_flux[1][i],lower_rms) )
+		upper_err = upper_peak_flux[1][i] * np.sqrt( (upper_rms/upper_peak_flux[1][i])**2 + 0.05**2 )
+		lower_err = lower_peak_flux[1][i] * np.sqrt( (lower_rms/lower_peak_flux[1][i])**2 + 0.05**2 )
+		cm_peak_spix_err.append(radio_spix_err(upper_peak_flux[1][i],upper_err,lower_peak_flux[1][i],lower_err) )
 
 cm_int_spix = np.array(cm_int_spix)
 cm_int_spix_err = np.array(cm_int_spix_err)
 cm_peak_spix = np.array(cm_peak_spix)
 cm_peak_spix_err = np.array(cm_peak_spix_err)
[…]

### 2014-12-24 git_add.sh

@@ -39,6 +39,15 @@ git add IRAM_sources.reg
 git add Radio_Correlations.py
 git add AAS_2015/225th_AAS_Abstract.rtf
 git add uv_space.png
+git add Teixeira12_Sources.reg
+git add Teixeira12_Sources.tab
+git add Tanaka13_Data.tab
+git add Mallick13_Data.tab
+git add Radio_Data.pkl
+git add Dzib13_Data_Corr.tab
+git add Dzib13_Data.tab
+git add Dzib13_Classes_Corr.tab
+git add Dzib13_Classes.tab
 
 git add Data/reduction_notes.txt
 
@@ -67,6 +76,22 @@ git add Paper/figures/SerpSouth_FOV-eps-converted-to.pdf
 git add Paper/figures/SerpSouth_fov_contour-eps-converted-to.pdf
 git add Paper/figures/SerpSouth_zoom_color_contour-eps-converted-to.pdf
 git add Paper/figures/SerpSouth_zoom_contour-eps-converted-to.pdf
+git add Paper/figures/Infra_SEDs_OnePlot-eps-converted-to.pdf
+git add Paper/figures/SPIRE_350_Figure-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_Lower_GaussFits-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_PACS70_Contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_SPIRE250_Contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_Spitz24_Contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_Spitz36_Contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_Spitz58_Contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_Spitz80_Contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_Upper_GaussFits-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_VLA10_contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_VLA12_contour-eps-converted-to.pdf
+git add Paper/figures/SerpSouth_uppercont_herschelcolor-eps-converted-to.pdf
+git add Paper/figures/Shirley36_Correlation-eps-converted-to.pdf
+git add Paper/figures/Shirley60_Correlation-eps-converted-to.pdf
[…]

### 2014-12-24 Paper/paper.tex
modified:   Make_Figs.py 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib

@@
 
+\begin{figure*}
+\label{fig:vla4}
+\centering
+\includegraphics[keepaspectratio=True,scale=.7]{figures/SerpSouth_VLA4_contour.eps}
+\caption{\small{ 
+}}
+\end{figure*}
+
 \sourcenote{Unclear Sources}
@@
 \label{sec:outflows}
-Radio continuum images have shown elongation with respect to radio jets etc etc...
+Early radio studies found that radio jet candidates are elongated in approximately the same direction as the large-scale outflow \citep{Anglada95}.
 
@@
 
+-- Is it possible that VLA 2, 3 and 4 are all apart of a radio-loud extragalactic jet? \\
+
+-- Given the size of the beam and the size of VLA 1 and 4, should they be considered ``resolved'' ? \\
+
 -- Does optically thick thermal radio emission ($\alpha_{radio} > 1.0$) mean that the source is ``embedded''?
@@
 
--- Are the images to a high enough sensitivity to which I can say they are ``deep'' ? \\
+-- Are the images to a high enough sensitivity to which we can say they are ``deep'' ? \\
+
+-- Title? \\
 

### 2014-12-24 Make_Figs.py

@@ -66,83 +66,92 @@ def get_zorder(layers):
 		zorder_paths[a] = path
 	return zorder_values, zorder_paths
 
+
 ### Herschel map w/ Spitzer sources and VLA primary beam
 if plot1 == True:
-	# Load and Configure Images
-	file1 = fits.open("FITS/SPIRE_250_micron.fits")
-	file2 = fits.open("FITS/SPIRE_350_micron.fits")
-	file3 = fits.open("FITS/SPIRE_500_micron.fits")
 
-	data1 = file1[1].data
-	wcs1 = WCS(file1[1].header)
+	figname = 'AAS_2015/SerpSouth_FOV.eps'
 
-	data2 = file2[1].data
-	wcs2 = WCS(file2[1].header)
+	savefig = False
 
-	data3 = file3[1].data
-	wcs3 = WCS(file3[1].header)
+	# Choose Image
+	color_im = 'FITS/SPIRE_350_micron.fits'
+	contour_im = 'FITS/SPIRE_350_micron.fits'
 
-	# Load Regions
-	spitzer = np.loadtxt('gutermuth2008_serps_ysos1.txt',unpack=True,dtype='str')
-	spitz_radec = np.array([np.array(spitzer[1],float),np.array(spitzer[2],float)])
+	# Load Header and FITS Data for Contour
+	contour_head = fits.open(contour_im)[0].header
+	contour_data = fits.open(contour_im)[1].data
+	
+	# Get RMS
+	rms = np.std(contour_data[~np.isnan(contour_data)])
 
-	# Plot Image
-	fig = mp.figure()
-	ax = WCSAxes(fig,[0.1,0.1,0.8,0.8],wcs=wcs2)
-	fig.add_axes(ax)
+	# Initialize Upper Subband Plot
+	fig = aplpy.FITSFigure(color_im, subplot=(1,1,1), figsize=(11,9))
 
-	ax.imshow(np.log(data2), origin='lower', cmap='Greys', interpolation='nearest',
-		alpha=1.0)
-
-	ax.contour(np.log(data2), levels=[5.9], colors='black', alpha=.8)
-
-	#	ax.imshow(data2, origin='lower', cmap='Greens', extent=extent2,
-	#		vmax=np.max(data2[~np.isnan(data2)])/4, alpha=.7 )
-	#	ax.imshow(data1, origin='lower', cmap='Greys', extent=extent1, alpha=1,
[…]

### 2014-12-27 Paper/paper.tex
new file:   AAS_2015/SS_AAS_Poster.ai 	new file:   AAS_2015/SS_AAS_Poster.pdf 	modified:   Make_Figs.py 	modified:   Paper/figures/Shirley36_Correlation-eps-converted-to.pdf 	modified:   Paper/figures/Shirley60_Correlation-eps-converted-to.pdf 	modified:   Paper/figures/Spix_Class-eps-converted-to.pdf 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib 	modified:   Radio_Correlations.py 	modified:   SERPS_SED.py 	modified:   git_add.sh

@@
 
-VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 3	&	50	&	60 $\pm$ 3	&	44	&	-0.22 $\pm$ 0.07	&	-0.31 $\pm$ 0.3	&	Class 0$^{*}$?\\[1ex]
+VLA\_9	&	18 30 02.80	&	-02 02 25.3	&	66 $\pm$ 3	&	50	&	60 $\pm$ 3	&	44	&	-0.22 $\pm$ 0.07	&	-0.31 $\pm$ 0.3	&	Class 0?\\[1ex]
 
@@
 
-VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 6	&	36	&	73 $\pm$ 5	&	58	&	1.5 $\pm$ 0.17	&	1.14 $\pm$ 0.34	&	Class 0\\[1ex]
+VLA\_11	&	18 30 03.36	&	-02 02 45.8	&	38 $\pm$ 6	&	36	&	73 $\pm$ 5	&	58	&	1.5 $\pm$ 0.17	&	1.14 $\pm$ 0.34	&	Class 0,VeLLO\\[1ex]
 
@@
 
-VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 4	&	37	&	83 $\pm$ 4	&	61	&	2.29 $\pm$ 0.15	&	1.19 $\pm$ 0.33	&	Class 0$^{*}$\\[1ex]
+VLA\_14	&	18 30 03.84	&	-02 03 12.2	&	31 $\pm$ 4	&	37	&	83 $\pm$ 4	&	61	&	2.29 $\pm$ 0.15	&	1.19 $\pm$ 0.33	&	Class 0\\[1ex]
 
@@
 
-VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 8	&	135	&	161 $\pm$ 9	&	167	&	0.22 $\pm$ 0.08	&	0.5 $\pm$ 0.12	&	Class I\\[1ex]
+VLA\_17	&	18 30 01.32	&	-02 03 42.9	&	146 $\pm$ 8	&	135	&	161 $\pm$ 9	&	167	&	0.22 $\pm$ 0.08	&	0.5 $\pm$ 0.12	&	Class I,VeLLO\\[1ex]
 
@@
 They have no visible associations from 1$\mu$m to 70$\mu$m and have negative radio spectral indices indicative of non-thermal synchrotron emission typical of a galaxy's radio spectrum.
-
-\begin{figure*}
-\label{fig:vla4}
-\centering
-\includegraphics[keepaspectratio=True,scale=.7]{figures/SerpSouth_VLA4_contour.eps}
-\caption{\small{ 
-}}
-\end{figure*}
 
@@
 
+\citep{Dunham13}
+
 %% Conclusions
@@
 
--- Given the size of the beam and the size of VLA 1 and 4, should they be considered ``resolved'' ? \\
+-- Given the size of the beam size compared to the size of VLA 1 and 4, should they be considered ``resolved'' ? \\
 
@@
 
+\begin{figure}
+\label{fig:vla4}
+\centering
+\includegraphics[keepaspectratio=True,scale=.6]{figures/SerpSouth_VLA4_contour.eps}
+\caption{\small{ Zoom-in on sources VLA 2, 3 and 4. Blue solid and red dashed contours correspond to 4.1 and 6.3 cm images respectively. Radio contours start at their respective 3$\sigma$ levels.
+}}
+\end{figure}
+
 %% End Document

### 2014-12-27 Make_Figs.py

@@ -26,8 +26,8 @@ savefig = False
 
 plot1 = False
 plot2 = False
-plot3 = True
-plot4 = False
+plot3 = False
+plot4 = True
 
 def sexig_to_deg(ra,dec):
 	length = len(ra)
@@ -148,8 +148,8 @@ if plot2 == True:
 	vla10 = False
 	vla12 = False
 
+	#figname = 'AAS_2015/SerpSouth_VLA12_contour.eps'
 	figname = 'Paper/figures/SerpSouth_VLA4_contour.eps'
-	#figname = 'Paper/figures/SerpSouth_zoom_contour.eps'
 
 	savefig = True
 
@@ -195,8 +195,8 @@ if plot2 == True:
 	fig.ticks.show_y()
 	fig.axis_labels.set_xtext('Right Ascension (J2000)')
 	fig.axis_labels.set_ytext('Declination (J2000)')
-	fig.axis_labels.set_xtext('')
-	fig.axis_labels.set_ytext('')
+#	fig.axis_labels.set_xtext('')
+#	fig.axis_labels.set_ytext('')
 	fig.axis_labels.set_font(size=18)
 	fig.axis_labels.set_xpad(15)
 	fig.axis_labels.set_ypad(10)
@@ -443,6 +443,11 @@ if plot3 == True:
 if plot4 == True:
 	import pickle as pkl
 
+	figname = 'Paper/figures/Spix_Class.eps'
+	figname = 'AAS_2015/Spix_Class.eps'
+
+	savefig = True
+
 	# Load Radio Data
 	data = pkl.Unpickler(open('Radio_Data.pkl','rb')).load()
 	for i in data:
@@ -472,29 +477,29 @@ if plot4 == True:
 	for i in range(18):
 		if i in class0:
 			if i in trust_int_spix:
-				ax.errorbar([0],kern.cm_int_spix[i],yerr=kern.cm_int_spix_err[i],fmt='s',color='green',alpha=.7)
+				ax.errorbar([0],kern.cm_int_spix[i],yerr=kern.cm_int_spix_err[i],fmt='s',markersize=10,color='green',alpha=.7)
 			elif i in trust_peak_spix:
-				ax.errorbar([0],kern.cm_peak_spix[i],yerr=kern.cm_peak_spix_err[i],fmt='s',color='green',alpha=.7)
[…]

### 2014-12-27 Radio_Correlations.py

@@ -9,6 +9,7 @@ from scipy.optimize import leastsq
 from AttrDict import AttrDict
 from scipy import stats
 import pickle as pkl
+from matplotlib import rc
 
 ## Flags ##
 
@@ -247,13 +248,19 @@ kern63_model = kern63_a*kern63_xrange + kern63_b
 
 
 ## Flags
-plot1 = True
+plot1 = False
 plot2 = False
-
-savefig = True
 
 ## Plot 4.1 cm over Shirley 3.6 cm data and 6.3 cm over Shirley 6.0 cm data
 if plot1 == True:
+
+	figname1 = 'Paper/figures/Shirley36_Correlation.eps'
+	figname2 = 'Paper/figures/Shirley60_Correlation.eps'
+	figname1 = 'AAS_2015/Shirley36_Correlation.eps'
+	figname2 = 'AAS_2015/Shirley60_Correlation.eps'
+
+	savefig = False
+
 	# Extrapolate 4.1 cm to 3.6 cm and 6.3 cm to 6.0 cm w/ spectral indices	
 	trust_int_spix = np.where(kern.cm_spix_trust == 'int')[0]
 	trust_peak_spix = np.where(kern.cm_spix_trust == 'peak')[0]
@@ -295,33 +302,37 @@ if plot1 == True:
 	fig1,ax1 = mp.subplots()
 
 	p1, = ax1.plot(shirley36_x,shirley36_y,'ko',alpha=.8)
-	p2 = ax1.errorbar(kern_x_kryukova1,kern36_flux1,xerr=0.5,yerr=kern36_flux_err1,fmt='o',color='b',alpha=.9)
-	p3 = ax1.errorbar(kern_x_kryukova2,kern36_flux2,xerr=0.5,yerr=kern36_flux_err2,fmt='o',color='r',alpha=.9)
-#	p4 = ax1.errorbar(kern_x_dunham1,kern36_flux1,yerr=kern36_flux_err1,fmt='o',color='c',alpha=.7)
-#	p5 = ax1.errorbar(kern_x_dunham2,kern36_flux2,yerr=kern36_flux_err2,fmt='o',color='m',alpha=.7)
-	mp.legend([p1,p2,p3],["Shirley+07","This work, d=429pc","This work, d=260pc"],loc=2)
[…]

### 2014-12-27 SERPS_SED.py

@@ -164,7 +164,6 @@ def radio_spix_err(flux1,flux1_err,flux2,flux2_err):
 	return np.sqrt(  (flux1_err/flux1)**2 + (flux2_err/flux2)**2 )
 
 
-
 # Load cm Peak Flux Data
 lower_peak_flux = np.loadtxt('Lower_Peak_Fluxes_try2.csv',delimiter=',',unpack=True)
 upper_peak_flux = np.loadtxt('Upper_Peak_Fluxes_try2.csv',delimiter=',',unpack=True)
@@ -331,8 +330,8 @@ ir_spitz_class = cross_match(spitz_class,spitz_source_id)
 
 
 ### Dunham08 70micron vs. Linternal ###
-Lint_dunham = 3.3e8 * guter_fluxes.T[-1]*c/70e-6 * 1e-23	# Lsun
-Lint_dunham_err = 3.3e8 * guter_fluxes.T[-1]*guter_rel_errs[-1]*c/70e-6 * 1e-23	# Lsun
+Lint_dunham = 3.3e8 * guter_fluxes.T[-1]*c/70e-6 * 1e-23				# Lsun
+Lint_dunham_err = 3.3e8 * guter_fluxes.T[-1]*guter_rel_errs[-1]*c/70e-6 * 1e-23		# Lsun
 
 ### Kryukova12 Lmir vs. Lbol ###
 dist1 = 429	# pc
@@ -361,7 +360,7 @@ Lbol_dunham1 = np.concatenate( [Lmir1[flat] / (-0.298 * np.log10(0.3) + 0.270)**
 Lbol_dunham2 = np.concatenate( [Lmir2[flat] / (-0.298 * np.log10(0.3) + 0.270)**2, Lmir2[rising] / (-0.298 * np.log10(ir_spix[rising]) + 0.270)**2] )
 
 # Classification
-classes = ['Extragal.?','Extragal.','Extragal.','Extragal.','Extragal.?','Extragal.','Class I','Extragal.?','Class 0?','Unknown','Class 0','Class 0','Class 0','Class 0','Extragal.','Class II','Class I','Extragal.?']
+classes = ['Extragal.?','Extragal.','Extragal.','Extragal.','Extragal.?','Extragal.','Class I','Extragal.?','Class 0?','Unknown','Class 0,VeLLO','Class 0','Class 0','Class 0','Extragal.','Class II','Class I,VeLLO','Extragal.?']
 
 # Convert RA and DEC to J2000
 ra = upper_ra

### 2014-12-27 git_add.sh

@@ -37,7 +37,6 @@ git add serps_yso1.reg
 git add vla_serps_merger_gutermuth_try1.csv
 git add IRAM_sources.reg
 git add Radio_Correlations.py
-git add AAS_2015/225th_AAS_Abstract.rtf
 git add uv_space.png
 git add Teixeira12_Sources.reg
 git add Teixeira12_Sources.tab
@@ -48,6 +47,11 @@ git add Dzib13_Data_Corr.tab
 git add Dzib13_Data.tab
 git add Dzib13_Classes_Corr.tab
 git add Dzib13_Classes.tab
+
+git add AAS_2015/225th_AAS_Abstract.rtf
+git add AAS_2015/SS_AAS_Poster.ai
+git add AAS_2015/SS_AAS_Poster.pdf
+
 
 git add Data/reduction_notes.txt
 

### 2015-01-02 Make_Figs.py
modified:   AAS_2015/SS_AAS_Poster.ai 	modified:   AAS_2015/SS_AAS_Poster.pdf 	modified:   Make_Figs.py 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Radio_Correlations.py 	modified:   Radio_Data.pkl 	modified:   SERPS_SED.py

@@ -26,8 +26,8 @@ savefig = False
 
 plot1 = False
 plot2 = False
-plot3 = False
-plot4 = True
+plot3 = True
+plot4 = False
 
 def sexig_to_deg(ra,dec):
 	length = len(ra)
@@ -144,12 +144,13 @@ if plot1 == True:
 if plot2 == True:
 
 	zoom = False
-	vla4 = True
+	vla4 = False
 	vla10 = False
 	vla12 = False
+	vla10and12 = True
 
-	#figname = 'AAS_2015/SerpSouth_VLA12_contour.eps'
-	figname = 'Paper/figures/SerpSouth_VLA4_contour.eps'
+	figname = 'AAS_2015/SerpSouth_VLA10and12_contour.eps'
+	#figname = 'Paper/figures/SerpSouth_VLA4_contour.eps'
 
 	savefig = True
 
@@ -173,7 +174,7 @@ if plot2 == True:
 	fig.hide_colorscale()
 	fig.show_contour(contour_im,alpha=1,cmap='Greys_r',levels=[rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
 
-	if vla4 == True or vla10 == True or vla12 == True:
+	if vla4 == True or vla10 == True or vla12 == True or vla10and12 == True:
 		fig.hide_layer('contour_set_1')
 		fig.show_contour(contour_im,alpha=0.6,cmap='Blues_r',levels=[rms*3,rms*4,rms*5,rms*6,rms*8,rms*10,rms*15,rms*20,rms*30,rms*50])
 		contour_im = 'FITS/SERPS_2.lower.briggs05.deeper.fits'
@@ -265,6 +266,16 @@ if plot2 == True:
 		fig.show_arrows(277.5205,-2.0550,-0.00075,0.00075,width=.15,head_width=.5,head_length=.4,facecolor='k')
 		fig.show_arrows(277.5115,-2.0585,0.00125,0.0005,width=.15,head_width=.5,head_length=.4,facecolor='k')
 
+	elif vla10and12 == True:
+		fig.show_arrows(277.5098,-2.0421,0.0010,0,width=.15,head_width=.5,head_length=.4,facecolor='k')
+		fig.show_arrows(277.5125,-2.0467,0.00075,0.0004,width=.15,head_width=.5,head_length=.4,facecolor='k')
[…]

### 2015-01-02 Radio_Correlations.py

@@ -248,7 +248,7 @@ kern63_model = kern63_a*kern63_xrange + kern63_b
 
 
 ## Flags
-plot1 = False
+plot1 = True
 plot2 = False
 
 ## Plot 4.1 cm over Shirley 3.6 cm data and 6.3 cm over Shirley 6.0 cm data
@@ -259,7 +259,7 @@ if plot1 == True:
 	figname1 = 'AAS_2015/Shirley36_Correlation.eps'
 	figname2 = 'AAS_2015/Shirley60_Correlation.eps'
 
-	savefig = False
+	savefig = True
 
 	# Extrapolate 4.1 cm to 3.6 cm and 6.3 cm to 6.0 cm w/ spectral indices	
 	trust_int_spix = np.where(kern.cm_spix_trust == 'int')[0]
@@ -302,16 +302,16 @@ if plot1 == True:
 	fig1,ax1 = mp.subplots()
 
 	p1, = ax1.plot(shirley36_x,shirley36_y,'ko',alpha=.8)
-	p2 = ax1.errorbar(kern_x_kryukova1,kern36_flux1,xerr=0.5,yerr=kern36_flux_err1,fmt='o',color='b',alpha=.6)
+	p2 = ax1.errorbar(kern_x_kryukova1,kern36_flux1,xerr=kern.Lbol_kryukova1_err/kern.Lbol_kryukova1,yerr=kern36_flux_err1,fmt='o',color='b',alpha=.6)
 #	p3 = ax1.errorbar(kern_x_kryukova2,kern36_flux2,xerr=0.5,yerr=kern36_flux_err2,fmt='o',color='r',alpha=.9)
-	p4 = ax1.errorbar(kern_x_dunham1,kern36_flux1,xerr=0.5,yerr=kern36_flux_err1,fmt='o',color='r',alpha=.6)
+#	p4 = ax1.errorbar(kern_x_dunham1,kern36_flux1,xerr=0.5,yerr=kern36_flux_err1,fmt='o',color='r',alpha=.6)
 #	p5 = ax1.errorbar(kern_x_dunham2,kern36_flux2,xerr=0.5,yerr=kern36_flux_err2,fmt='o',color='m',alpha=.7)
-	mp.legend([p1,p2,p4],["Shirley+07","This work and Kryukova+ 2012","This work and Dunham+ 2013"],loc=2)
[…]

### 2015-01-02 SERPS_SED.py

@@ -192,6 +192,19 @@ cm_peak_spix_err = np.array(cm_peak_spix_err)
 # Which spectral index to trust based on observational properties
 cm_spix_trust = ['int','int','int','int','int','peak','int','peak','peak','peak','peak','peak','peak','peak','int','peak','int','peak']
 
+cm_spix = []
+cm_spix_err = []
+for i in range(source_num):
+	if cm_spix_trust[i] == 'int':
+		cm_spix.append(cm_int_spix[i])
+		cm_spix_err.append(cm_int_spix_err[i])
+	elif cm_spix_trust[i] == 'peak':
+		cm_spix.append(cm_peak_spix[i])
+		cm_spix_err.append(cm_peak_spix_err[i])
+
+cm_spix = np.array(cm_spix)
+cm_spix_err = np.array(cm_spix_err)	
+
 cm_lower_snr = lower_peak_flux[1] / lower_rms
 cm_upper_snr = upper_peak_flux[1] / upper_rms
 
@@ -295,8 +308,6 @@ def replace_nan(array,sub,round_num=2,flt=True):
 				new_array.append(array[i])
 	return np.array(new_array)
 
-
-
 ## Create data dictionary for arrays with ordering identical to SS_Final_Sources
 data = {}
 
@@ -330,7 +341,7 @@ ir_spitz_class = cross_match(spitz_class,spitz_source_id)
 
 
 ### Dunham08 70micron vs. Linternal ###
-Lint_dunham = 3.3e8 * guter_fluxes.T[-1]*c/70e-6 * 1e-23				# Lsun
+Lint_dunham = (guter_fluxes.T[-1] * c / 70e-6 * 1e-23) ** (0.94) * 3.3e8
 Lint_dunham_err = 3.3e8 * guter_fluxes.T[-1]*guter_rel_errs[-1]*c/70e-6 * 1e-23		# Lsun
 
 ### Kryukova12 Lmir vs. Lbol ###
@@ -345,22 +356,28 @@ Lmir2 = (19.79*guter_fluxes.T[0] + 16.96*guter_fluxes.T[1] + 10.49*guter_fluxes.
 
[…]
